### 2018-01-27 MScFigures.Rmd
Add files via upload

---
title: "MSc Statistical overview"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    highlight: tango
    theme: cerulean
    toc: yes
  word_document:
    toc: yes
---
# Housekeeping
### Preamble

By Katherine Duchesneau

We are working with the roots Lesion and Mycorrhiza dataset for now.

### R details

This section contains all the necessary details about the R version and package version used to run this Notebook.

  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `tidyverse` package version: `r packageVersion("tidyverse")`
  * `lme4` package version `r packageVersion("lme4")`
  * `MASS` package version `r packageVersion("MASS")`
  * `MuMIn` package version `r packageVersion("MuMIn")`
  * `emmeans` package version `r packageVersion("emmeans")`
  * `boot` package version `r packageVersion("boot")`
  * `brms` package version `r packageVersion("brms")`
  * `loo` package version `r packageVersion("loo")`
  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`

### Load Packages and Functions

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)

# theme_simple() a homemade function from the Colautti lab (2017) to standardize figures
theme_simple <- function (base_size = 16, base_family = "") {
  theme_classic(base_size = base_size, base_family = base_family) %+replace%
    theme(
      axis.text = element_text(colour = "black"),
      axis.title.x = element_text(size=18),
      axis.text.x = element_text(size=16, face= "italic"),
      axis.title.y = element_text(size=18, angle=90), 
      axis.text.y = element_text(size=16),
      axis.ticks = element_blank(),
      panel.background = element_rect(fill="white"),
      panel.border = element_blank(),
      plot.title=element_text(face="bold", size=24)
      #      legend.position="none"
    )
}

overdisp_fun <- function(model) {
  ## number of variance parameters in an n-by-n variance-covariance matrix
  vpars <- function(m) {
    nrow(m) * (nrow(m) + 1)/2
  }
  # The next two lines calculate the residual degrees of freedom
  model.df <- sum(sapply(VarCorr(model), vpars)) + length(fixef(model))
  rdf <- nrow(model.frame(model)) - model.df
  # extracts the Pearson residuals
  rp <- residuals(model, type = "pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  # Generates a p-value. If less than 0.05, the data are overdispersed.
  pval <- pchisq(Pearson.chisq, df = rdf, lower.tail = FALSE)
  c(chisq = Pearson.chisq, ratio = prat, rdf = rdf, p = pval)
}
```

# Introducing the Data

### Load/ Modify data: Co-occurence
```{r Introduce co-occurence dataset, message=FALSE, warning=FALSE}
mdata <- read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
indiv <- mdata$CODE[!mdata$CODE==""]
tdata <- mdata[grep("[0-9]+",mdata$Cross),]
nrow(tdata)/length(indiv)
# This is not the same because some individuals just had the totals not the cooccurence data
indiv2 <- tdata$CODE[!tdata$CODE==""]
nrow(tdata)/length(indiv2)
indiv2 <- data.frame(indiv2)
indiv2 <- mefa:::rep.data.frame(indiv2,each=100)
fdata <- cbind(indiv2,tdata)
fdata <- fdata[,-c(2,3,4,9,14,17,18)]

# Cleaning up the occurence data
fdata[is.na(fdata)] <- 0
fdata$Lesion<-rowSums(fdata[,2:4])
fdata[fdata$Lesion>1,]
fdata$Mycorrhiza<-rowSums(fdata[,6:8])
fdata[fdata$Mycorrhiza>1,]
fdata <- fdata[,-c(2:4,6:8)]

#### Checking data for problems ####

summary(fdata)
fdata$None.Path <- as.integer(fdata$None.Path)
fdata$None.Myc <- as.integer(fdata$None.Myc)
fdata[is.na(fdata)] <- 0

sherb <- fdata$Herbivory+fdata$None.Herb
fdata[sherb!=1,]
fdata[sherb!=1,"None.Herb"]<-1

# Are all the sums equal to 100 for herb? 
dframeHerb <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeHerb[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeHerb$counter[c] <- c
  dframeHerb$Indiv2[c] <- i
  dframeHerb$Sum[c] <- sum(subdata[,"Herbivory"]+subdata[,"None.Herb"])
  subdata <- NA
  c <- c + 1
}
dframeHerb[dframeHerb$Sum!=100,]

# Are all the sums equal to 100 for Mycorrhiza? 
dframeMyc <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeMyc[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeMyc$counter[c] <- c
  dframeMyc$Indiv2[c] <- i
  dframeMyc$Sum[c] <- sum(subdata[,"Mycorrhiza"]+subdata[,"None.Myc"])
  subdata <- NA
  c <- c + 1
}
dframeMyc[dframeMyc$Sum!=100,]

# Are all the sums equal to 100 for Lesions? 
dframeLesion <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeLesion[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeLesion$counter[c] <- c
  dframeLesion$Indiv2[c] <- i
  dframeLesion$Sum[c] <- sum(subdata[,"Lesion"]+subdata[,"None.Path"])
  subdata <- NA
  c <- c + 1
}
dframeLesion[dframeLesion$Sum!=100,]

# Separating "Individual" into: pop,location,species columns 
fdata$pop <- gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",fdata$indiv)
fdata$location <- gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",fdata$indiv)
fdata$species <- sub("^[0-9]+[I,O]([A-Z]+).*","\\1",fdata$indiv)
fdata$location <- as.factor(fdata$location)
fdata$species <- as.factor(fdata$species)
fdata$pop <- as.factor(fdata$pop)
fdata$indiv2 <- as.character(fdata$indiv2)
summary(fdata)
fdata %>% drop_na()->fdata

fdata$None.Myc <- as.factor(fdata$None.Myc)
fdata$Herbivory <- as.factor(fdata$Herbivory)
fdata$Mycorrhiza <- as.factor(fdata$Mycorrhiza)
fdata$Lesion <- as.factor(fdata$Lesion)
fdata$None.Herb <- as.factor(fdata$None.Herb)
fdata$None.Path <- as.factor(fdata$None.Path)
summary(fdata)

#### Gather ####
length(unique(fdata$indiv2))
Cross<- data.frame(c(rep(1:100, times=225)))
fdatac <- cbind(fdata,Cross)
colnames(fdatac)[11]<-"cross"
fdatac %>% gather(Trait, Value, c(4,6,7)) -> fdata_gather # The warning is an inconsequential bug from tidyverse (https://github.com/tidyverse/tidyr/issues/386)
fdata_gather$Value<-as.numeric(fdata_gather$Value)
fdata_gather$Trait<-as.factor(fdata_gather$Trait)
fdata_gather <- fdata_gather[,-c(2:4)]
```

### Load/ Modify data: Totals
```{r Introduce total dataset, message=FALSE, warning=FALSE}
mdata<-read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
indiv<-mdata$CODE[!mdata$CODE==""]
tdata<-mdata[mdata$Slide=="TOTAL",]
length(indiv)
nrow(tdata)

ndata<-cbind(indiv,tdata)
ndata<-ndata[,-c(2,3,4,9,14,17:37)]
ndata$None.Path<-as.integer(ndata$None.Path)
ndata$None.Myc<-as.integer(ndata$None.Myc)

# Checking data for problems
problemsPath<-ndata[!rowSums(ndata[,c(2:5)])==100,]
problemsHyph<-ndata[!rowSums(ndata[,c(6:9)])==100,]
problemsHerb<-ndata[!rowSums(ndata[,c(10:11)])==100,]

# Separating "Individual" into: pop,location,species columns 
ndata$pop<-gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",ndata$indiv)
ndata$location<-gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",ndata$indiv)
ndata$species<-gsub("^[0-9]+[I,O]([A-Z]+).*","\\1",ndata$indiv)
ndata$location<-as.factor(ndata$location)
ndata$species<-as.factor(ndata$species)
ndata$pop<-as.factor(ndata$pop)

#### Totalling the scores####
binlesion<-cbind(ndata$None.Path,100-ndata$None.Path)
binmycorr<-cbind(ndata$None.Myc,100-ndata$None.Myc)
binherbivory<-cbind(ndata$None.Herb,100-ndata$None.Herb)
summary(ndata)

# scale data (only need to scale the numerical variables!)
numcols <- grep("^None.",names(ndata))
ndatas <- ndata
ndatas[,numcols] <- scale(ndatas[,numcols])
```

### Variable descriptions

The variables are:

Co-occurence:

  * **indiv2:** The unique code given to a sample. In this dataset the unique sample code repeats 100 times for each cross where an observation was taken on the root sample.

  * **None.Path:** A binary representation of whether a sign of pathogen activity was recorded (0) or not (1).

  * **Lesion:** The counterpart to the previous variable (None.Path). A binary representation of whether a sign of pathogen activity was recorded (1) or not (0).

  * **None.Myc:** A binary representation of whether a sign of myccorhizal activity was recorded (0) or not (1).

  * **Mycorrhiza:** The counterpart to the previous variable (None.Myc). A binary representation of whether a sign of mycorrhizal activity was recorded (1) or not (0).

  * **None.Herb:** A binary representation of whether herbivory was recorded (0) or not (1).

  * **Herbivory:** The counterpart to the previous variable (None.Herb). A binary representation of whether Herbivoryn was recorded (1) or not (0).

  * **Population (pop):** The coding number representing the population at which the sample was collected.

  * **location:** A code representing the whether the sample was collected inside a Alliaria petiolata population (I) or whther it was collected at least 7 m outside of he furthest individual in the A. petiolata population (O).

  * **species:** The particular species to which the sample belongs.

  * **Cross:** The particular cross number where the data was recorded on the individual sample.

Total scores:

  * **indiv:** The unique code given to a sample.

  * **Decay:** The total number of crosses where decay was recorded an individual sample when doing a total of 100 crosses/ sample.

  * **Pathogen:** The total number of crosses where pathogen was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **Hyphae:** The total number of crosses where non-myccorhizal hyphae was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **None.Path:** The total number of crosses where no signs of pathogen activities were recorded on an individual sample when doing a total of 100 crosses/ sample. Note that the total of Decay, Pathogen, Hyphae, and None.Path must come to 100 per individual to account for all 100 crosses.

  * **Arbuscule:** The total number of crosses where an arbuscule was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **Vesicules:** The total number of crosses where a vesicule was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **M_Hyphae:** The total number of crosses where myccorhizal hyphae was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **None.Myc:** The total number of crosses where no signs of mycorrhizal activities were recorded on an individual sample when doing a total of 100 crosses/ sample. Note that the total of Arbuscules, Vesicules, M_Hyphae, and None.Myc must come to 100 per individual to account for all 100 crosses.

  * **Herbivory:** The total number of crosses where herbivory was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **None.Herb:** The total number of crosses where no signs of herbivory was recorded on an individual sample when doing a total of 100 crosses/ sample. Note that the total of Herbivory, and None.Herb must come to 100 per individual to account for all 100 crosses.

  * **Population (pop):** The coding number representing the population at which the sample was collected.

  * **location:** A code representing the whether the sample was collected inside a Alliaria petiolata population (I) or whther it was collected at least 7 m outside of he furthest individual in the A. petiolata population (O).

  * **species:** The particular species to which the sample belongs.

# Reviewing the hypothesis

## Histology data Hypothesis
### Hypothesis 1

Mycorrhizal colonization protects roots from lesions and herbivory.
```{r echo=FALSE}
y<-data.frame(c(rnorm(50, mean=5, sd=8),rnorm(50, mean=50, sd=8)))
colnames(y)<-c("y")
y$y<-sort(y$y, decreasing = T)
x<-data.frame(c(rnorm(50, mean=5, sd=8),rnorm(50, mean=50, sd=8)))
colnames(x)<-c("x")
x$x<-sort(x$x, decreasing = F)
df <- cbind(x,y)
colnames(df)<-c("x","y")

ggplot(df, aes(x,y))+geom_smooth(method="lm", se=F)+geom_point()+
  theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
  theme(axis.text.x = element_blank(),axis.text.y = element_blank())
```

### Hypothesis 2

A. petiolata invasion reduces mycorrhizal colonization and increases pathogen colonization and herbivory
```{r echo=FALSE}
InOut<- data.frame(c(rep("I", times=50),rep("O", times=50)))
colnames(InOut)<-c("Location")
df <- cbind(df,InOut)

ggplot(df, aes(x,y, colour=Location))+geom_smooth(method="lm", se=F)+geom_jitter()+
  theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
  theme(axis.text.x = element_blank(),axis.text.y = element_blank())
```
### Hypothesis 3

Efficiency of mycorrhizal protection is reduced in the presence of A. petiolata
```{r echo=FALSE}
y<-data.frame(c(rnorm(50, mean=5, sd=8),rep(40, times=10),rep(41, times=10),rep(42, times=10),rep(40.5, times=10),rep(39, times=10)))
colnames(y)<-c("y")
y$y<-sort(y$y, decreasing = T)
x<-data.frame(c(rnorm(50, mean=5, sd=8),rnorm(50, mean=50, sd=8)))
colnames(x)<-c("x")
x$x<-sort(x$x, decreasing = F)
df <- cbind(x,y)
colnames(df)<-c("x","y")

InOut<- data.frame(c(rep("I", times=50),rep("O", times=50)))
colnames(InOut)<-c("Location")
df <- cbind(df,InOut)

ggplot(df, aes(x,y, colour=Location))+geom_smooth(method="lm", se=F)+geom_jitter()+
  theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
  theme(axis.text.x = element_blank(),axis.text.y = element_blank())
```

## Molecular data Hypothesis

### Hypothesis 1

A. petiolata invasion changes the diversity of mycorrhizal and other fungal species present in the soil.

I will find that the molecular data from the soil extraction supports this claim by having a reduced biodiversity and abundance of mycorrhiza in samples taken inside A. petiolata populations.

### Hypothesis 2

There will be a negative correlation between mycorrhizal and fungal pathogen diversity.

# Histology data Analysis

## Hypothesis 1: Lesion ~ Mycorriza

###Co-occurence data

```{r Co-occurence model using corr}
# calculating the r
indivCODE <- unique(fdata$indiv2)
dfcorr <-data.frame(indivCODE=c(0),r=c(0))
for (i in 1:length(indivCODE)){
  dat1<-NULL
  dat1<-filter(fdata, fdata$indiv2==indivCODE[i])
  dfcorr[i,1] <- indivCODE[i]
  dfcorr[i,2] <- cor(as.numeric(dat1$Mycorrhiza),as.numeric(dat1$Lesion))
}
dfcorr %>% drop_na()->dfcorr

#Normal?
car::qqp(dfcorr$r, "norm")
shapiro.test(dfcorr$r)
hist(dfcorr$r)
# Cannot be normal because it is only between -1 and 1 and our mean is at 0.
descdist(dfcorr$r, discrete = FALSE, boot = 500)

# weibull when transformed to be positive?
dfcorr$r.t <- dfcorr$r+1
fit.weibull <- fitdist(dfcorr$r.t, "weibull")
car::qqp(dfcorr$r.t, "weibull", shape = fit.weibull$estimate[[1]])

dfcorr$pop <- gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",dfcorr$indivCODE)
dfcorr$location <- gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",dfcorr$indivCODE)
dfcorr$species <- sub("^[0-9]+[I,O]([A-Z]+).*","\\1",dfcorr$indivCODE)
dfcorr$location <- as.factor(dfcorr$location)
dfcorr$species <- as.factor(dfcorr$species)
dfcorr$pop <- as.factor(dfcorr$pop)

meanR<-mean(dfcorr$r)
SEMR<-sd(dfcorr$r)/sqrt(length(dfcorr$r))
UCI<- meanR+SEMR*1.96
LCI<- meanR-SEMR*1.96
mean(filter(dfcorr, dfcorr$location=="I")$r)
mean(filter(dfcorr, dfcorr$location=="O")$r)

baysian_corrGLMM <- brm(r.t ~ location * species + (1|pop), data=dfcorr, family = weibull(link="log"), control = list(adapt_delta = 0.9))
baysian_corrGLMM2 <- brm(r.t ~ location + species + (1|pop), data=dfcorr, family = weibull(link="log"), control = list(adapt_delta = 0.9))
baysian_corrGLMM3 <- brm(r.t ~ location + (1|pop), data=dfcorr, family = weibull(link="log"), control = list(adapt_delta = 0.9))
baysian_corrGLMM_NULL <- brm(r.t ~ 1 + (1|pop), data=dfcorr, family = weibull(link="log"), control = list(adapt_delta = 0.9))

waic.BCG_1<-waic(baysian_corrGLMM)
waic.BCG_2<-waic(baysian_corrGLMM2)
waic.BCG_3<-waic(baysian_corrGLMM3)
waic.BCG_NULL<-waic(baysian_corrGLMM_NULL)
compare(waic.BCG_1,waic.BCG_2) #positive means second is better
compare(waic.BCG_2,waic.BCG_3) #negative means first is better
compare(waic.BCG_2,waic.BCG_NULL) #negative means first is better
summary(baysian_corrGLMM2)
bayes_R2(baysian_corrGLMM2)

ggplot(dfcorr, aes(y=r,x=location))+geom_boxplot()+theme_simple()
ggplot(dfcorr, aes(y=r,x=species))+geom_boxplot()+theme_simple()

```

Co-occurence with gather: what is the difference? 
Here I want to see that the traits are associating differently at every cross for each indiv

````{r Co-occurence model GATHER}

baysianGLMERmyc_lesion_GTHR <- brm(Value ~ Trait * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))

summary(baysianGLMERmyc_lesion_GTHR)
bayes_R2(baysianGLMERmyc_lesion_GTHR)

baysianGLMERmyc_lesion_GTHR_1 <- brm(Value ~ Trait * location * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))

baysianGLMERmyc_lesion_GTHR_2 <- brm(Value ~ Trait + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))

baysianGLMERmyc_lesion_GTHR_NULL <- brm(Value ~ 1 + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))

model.sel(baysianGLMERmyc_lesion_GTHR,baysianGLMERmyc_lesion_GTHR_1,baysianGLMERmyc_lesion_GTHR_2,baysianGLMERmyc_lesion_GTHR_NULL) #not sure if this function will work with brm model, if not ill just have to do a waic and then a compare like the previous... should test with a smaller model
```
**SUMMARY:**

What is significant with the correlation~location*sp model?

What does it change when we gather the model? What am I really testing?
Does it really test what I want it to test?

What is significant when we gather? Is this model even any good?

###Totals data

```{r Totals model}

# model 
GLMMmyc_lesion <- glmer(binlesion ~ None.Myc * species + (1 | pop) , data = ndatas,family = binomial(link = "logit"))
summary(GLMMmyc_lesion)

options(na.action="na.fail")
dredge(GLMMmyc_lesion)
r.squaredGLMM(GLMMmyc_lesion)
# will need to change this ASAP

ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path))+
  stat_summary(fun.y=mean, geom="point")+
  geom_smooth(method = "lm")+
  geom_point()+
  theme_simple()+
  facet_wrap("species")+
  labs(x = "Mycorrhizal colonization", y="Lesions")
```
**SUMMARY:**

Is the totals the same as the corr data?

if not what has change? what does it mean biologically: Same/less path=mycorrhiza defend NotSame/less path=mycorrhizal defence is not related to colonization. if theres not an effect then maybe it has more to do with the species composition than the actual mycorrhizal colonization, Thats why we will test pathogen colonization alone (without myc = H2)

## Hypothesis 2: Mycorrhiza & Lesion ~ invasion

### Does location impact the effect of myc on lesion?

```{r location interaction with mycorrhiza and lesion}
GLMMmyc_lesion_loc <- glmer(binlesion ~ None.Myc * location * species + (1 | pop), data = ndatas, family = binomial(link = "logit"))
summary(GLMMmyc_lesion_loc)

emm<-emmeans(GLMMmyc_lesion_loc, list(~None.Myc| species | location, ~None.Myc| location), type = "response" )
summary(emm)

ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path))+
  geom_smooth(method = "lm")+
  geom_point(aes(color=location))+
  theme_simple()+
  facet_wrap("species")+
  labs(x = "Mycorrhizal colonization", y="Lesions")

pca <- prcomp(ndata[,c(5,9)])
location <- ndata[,13]
library(ggbiplot)
g <- ggbiplot(pca, obs.scale = 1, var.scale = 1, 
                groups = location, ellipse = TRUE, 
                circle = TRUE)
g <- g + scale_color_discrete(name = '')
g <- g + theme(legend.direction = 'horizontal', 
                 legend.position = 'top')
print(g)
```

### Does location impact lesion alone?

```{r location on lesion}
glmerLESION_disp <- glmer (binlesion ~ location * species + (1|pop) + (1|indiv), data = ndatas, family = binomial(link="logit"))
summary(glmerLESION_disp)
options(na.action="na.fail")
dredge(glmerLESION_disp)
r.squaredGLMM(glmerLESION_disp)

ggplot(aes(x = location, y = 100-None.Path, color=location), data=ndata)+
  geom_boxplot()+
  geom_jitter(width=0.1)+
  facet_wrap("species")+
  theme_simple()
```

### Does location impact mycorrhiza alone?

```{r location on mycorrhiza}
glmerMYC_disp <- glmer (binmycorr ~ location * species + (1|pop) + (1|indiv), data = ndata, family = binomial(link="logit"))
summary(glmerMYC_disp)
options(na.action="na.fail")
dredge(glmerMYC_disp)
r.squaredGLMM(glmerMYC_disp)

ggplot(aes(x = location, y = 100-None.Myc, color=location), data=ndata)+
  geom_boxplot()+
  geom_jitter(width=0.1)+
  facet_wrap("species")+
  theme_simple()

```

## Hypothesis 3: Lesion ~ Mycorriza * invasion

```{r Hypothesis 3}

ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path, color=location))+
  geom_smooth(method = "lm")+
  geom_point()+
  theme_simple()+
  facet_wrap("species")+
  labs(x = "Mycorrhizal colonization", y="Lesions")

ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path, color=location))+
  geom_smooth(method = "lm")+
  geom_point()+
  theme_simple()+
  labs(x = "Mycorrhizal colonization", y="Lesions")
```

# Molecular data Analysis

## Hypothesis 1: Mycorrhiza_div ~ invasion

## Hypothesis 2: Mycorrhiza_div ~ Pathoge_div

### 2018-01-27 MScFigures.Rmd
Added missing libraries

@@
   * `fitdistrplus` package version `r packageVersion("fitdistrplus")`
+  * `mefa` package version `r packageVersion("mefa")`
+  * `library(devtools)` and `install_github("vqv/ggbiplot")` package version `r packageVersion("ggbiplot")`
+  * also requires [rtools](https://cran.r-project.org/bin/windows/Rtools/)
 
@@
 library(fitdistrplus)
+library(mefa)
+library(ggbiplot)
 

### 2018-01-27 MScFigures_noGather.Rmd
Add files via upload

--- 2018-01-27 MScFigures.Rmd
@@
 fdata_gather <- fdata_gather[,-c(2:4)]
+write.csv(fdata_gather, "fdata_gather.csv")
 ```
@@
 
-Co-occurence with gather: what is the difference? 
-Here I want to see that the traits are associating differently at every cross for each indiv
-
-````{r Co-occurence model GATHER}
-
-baysianGLMERmyc_lesion_GTHR <- brm(Value ~ Trait * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-summary(baysianGLMERmyc_lesion_GTHR)
-bayes_R2(baysianGLMERmyc_lesion_GTHR)
-
-baysianGLMERmyc_lesion_GTHR_1 <- brm(Value ~ Trait * location * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-baysianGLMERmyc_lesion_GTHR_2 <- brm(Value ~ Trait + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-baysianGLMERmyc_lesion_GTHR_NULL <- brm(Value ~ 1 + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-model.sel(baysianGLMERmyc_lesion_GTHR,baysianGLMERmyc_lesion_GTHR_1,baysianGLMERmyc_lesion_GTHR_2,baysianGLMERmyc_lesion_GTHR_NULL) #not sure if this function will work with brm model, if not ill just have to do a waic and then a compare like the previous...
-should test with a smaller model
-```
-**SUMMARY:**
-
-What is significant with the correlation~location*sp model?
-
-What does it change when we gather the model? What am I really testing?
-Does it really test what I want it to test?
-
-What is significant when we gather? Is this model even any good?
-
 ###Totals data

### 2018-01-29 MScFigures.Rmd
Added simplified analysis and data visualizations -- Rob

@@
 library(ggbiplot)
+```
 
+## KAT, PLEASE BREAK UP YOUR CODE INTO SMALL CHUNCKS AND EXPLAIN WHAT EACH IS DOING. 
+Load a custome theme for clean, readable graphs
+```{r echo=F}
 # theme_simple() a homemade function from the Colautti lab (2017) to standardize figures
@@
 }
+```
 
+## EXPLAIN WHAT THIS OVERDISPERSION FUNCTION IS FOR...
+```{r echo=F}
 overdisp_fun <- function(model) {
@@
 nrow(tdata)/length(indiv)
+
 # This is not the same because some individuals just had the totals not the cooccurence data
+## THE COMMENT IS NOT CLEAR, EXPLAIN...
 indiv2 <- tdata$CODE[!tdata$CODE==""]
@@
 # Cleaning up the occurence data
+## CLEANING UP HOW?
 fdata[is.na(fdata)] <- 0
@@
 
-# Reviewing the hypothesis
+# Reviewing of hypotheses:
 
-## Histology data Hypothesis
+## Question 1: Is there evidence that Mycorrhizal colonization provides protection against root pathogen damage?
+
+## Question 2: Do these effects vary among species?
+
 ### Hypothesis 1
+
+### VERY NICE PREDICTION FIGURES! PERSONALLY, I WOULD MAKE THE DOTS BIGGER AND BIVARIATE NORMAL (SEE CHANGES):
 
@@
 ```{r echo=FALSE}
-y<-data.frame(c(rnorm(50, mean=5, sd=8),rnorm(50, mean=50, sd=8)))
+set.seed(3242)
+y<-data.frame(rnorm(100,sd=7))
 colnames(y)<-c("y")
-y$y<-sort(y$y, decreasing = T)
-x<-data.frame(c(rnorm(50, mean=5, sd=8),rnorm(50, mean=50, sd=8)))
+y$y<-sort(y$y)
+x<-data.frame(-y+rnorm(100))
 colnames(x)<-c("x")
-x$x<-sort(x$x, decreasing = F)
 df <- cbind(x,y)
 colnames(df)<-c("x","y")
+df$Location <- c(rep("Out",nrow(df)/2),rep("In",nrow(df)/2))
 
-ggplot(df, aes(x,y))+geom_smooth(method="lm", se=F)+geom_point()+
+ggplot(data=df, aes(x,y))+geom_smooth(method="lm", se=F)+geom_point(size=4,alpha=0.3)+
   theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
@@
 ```{r echo=FALSE}
-InOut<- data.frame(c(rep("I", times=50),rep("O", times=50)))
-colnames(InOut)<-c("Location")
-df <- cbind(df,InOut)
-
-ggplot(df, aes(x,y, colour=Location))+geom_smooth(method="lm", se=F)+geom_jitter()+
-  theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
+ggplot(df, aes(x,y, colour=Location))+geom_smooth(method="lm", se=F)+
+  geom_point(size=4,alpha=0.3)+theme_simple()+
+  labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
   theme(axis.text.x = element_blank(),axis.text.y = element_blank())
@@
 
-Efficiency of mycorrhizal protection is reduced in the presence of A. petiolata
+Cycorrhizal colonization is reduced in the presence of A. petiolata
 ```{r echo=FALSE}
-y<-data.frame(c(rnorm(50, mean=5, sd=8),rep(40, times=10),rep(41, times=10),rep(42, times=10),rep(40.5, times=10),rep(39, times=10)))
-colnames(y)<-c("y")
-y$y<-sort(y$y, decreasing = T)
-x<-data.frame(c(rnorm(50, mean=5, sd=8),rnorm(50, mean=50, sd=8)))
-colnames(x)<-c("x")
-x$x<-sort(x$x, decreasing = F)
-df <- cbind(x,y)
-colnames(df)<-c("x","y")
+df$y2<-df$y
+df$y2[df$Location=="In"]<-df$y2[df$Location=="In"]+10
+ggplot(df, aes(x,y2, colour=Location))+geom_smooth(method="lm", se=F)+
+  geom_point(size=4,alpha=0.3)+
+  theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
+  theme(axis.text.x = element_blank(),axis.text.y = element_blank())
+```
 
-InOut<- data.frame(c(rep("I", times=50),rep("O", times=50)))
-colnames(InOut)<-c("Location")
-df <- cbind(df,InOut)
+### Hypothesis 4
 
-ggplot(df, aes(x,y, colour=Location))+geom_smooth(method="lm", se=F)+geom_jitter()+
+Mycorrhizal protection is completely lost in the presence of A. petiolata
+```{r echo=FALSE}
+df$y2<-df$y
+set.seed (238.4)
+df$y2[df$Location=="In"]<-rnorm(nrow(df)/2,mean=10)
+ggplot(df, aes(x,y2, colour=Location))+geom_smooth(method="lm", se=F)+
+  geom_point(size=4,alpha=0.3)+
   theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
@@
 
+## IMPORTANT: BEFORE RUNNING COMPLICATED MODELS: (1) TAKE A LOOK AT THE DATA, (2) RUN SIMPLE MODELS -- SEE IF IT IS EVEN WORTH YOUR TIME & EFFORT
+
 ### Hypothesis 2
@@
 
+### Data exploration:
+
+Calculate plant-level Mycchorizae, pathogens and herbivory:
+
+```{r}
+# Fix column characteristics for plotting and analysis
+fdata$indiv2<-as.factor(fdata$indiv2)
+fdata$Mycorrhiza<-as.numeric(paste(fdata$Mycorrhiza))
+fdata$Lesion<-as.numeric(paste(fdata$Lesion))
+fdata$Herbivory<-as.numeric(paste(fdata$Herbivory))
+pct<-function(x){
+  sum(x)/100
+}
+
+# Calculate plant-level averages
+fdat_ind<-aggregate(fdata[,c("Mycorrhiza","Lesion","Herbivory")],
+                    by=list(indiv2=fdata$indiv2,pop=fdata$pop,loc=fdata$loc,species=fdata$species),
+                    pct)
+
+```
+
+## SIMPLE LINEAR MODEL AND VISUALIZATION:
+
+### Mycorrhia model results
+
+  1. Mycorrhiza colonization is significantly higher outside patches of A. petiolata than inside
+  2a. Species vary in Mycorrhiza colonization, with highest colonization in SC and others relatively similar. 
+  2b. Effect of A. petiolata on Mycorrhiza colonization differs among species, with more pronounced effects for GR and MR, and will little effect for GA
+  3. Effect of A. petiolata on Mycorrhiza colonization varies by population, but not as strongly as among species
+
+```{r}
+## Mycorrhiza model (NOTE: No loc*species because not all species present in all populations)
+base.Myc<-lmer(Mycorrhiza~species+loc+species:loc+(1|pop)+(1|pop:loc),data=fdat_ind)
+noint.Myc<-lmer(Mycorrhiza~species+loc+(1|pop)+(1|pop:loc),data=fdat_ind)
+anova(base.Myc,noint.Myc)
+base.Myc ## Inspect coefficients
+
+ggplot(fdat_ind,aes(species,Mycorrhiza,colour=loc))+geom_boxplot()+theme_simple()
+ggplot(fdat_ind,aes(pop,Mycorrhiza,colour=loc))+geom_boxplot()+theme_simple()
+```
+
+### Lesions model results
+
+  1. Root lesions increase with mycorrhiza colonization, contrary to predictions
+  2. Effect of Mycorrhiza on Lesions depends strongly on species (Myc*species interactions)
+
+```{r}
+## Mycorrhiza model (NOTE: No loc*species because not all species present in all populations)
+base.Les<-lmer(Lesion~Mycorrhiza*species*loc+(1|pop/loc),data=fdat_ind)
+norint.Les<-lmer(Lesion~Mycorrhiza*species*loc+(1|pop),data=fdat_ind)
+anova(base.Les,norint.Les)
+norint.Les # inspect coefficients
+
+Les2<-lmer(Lesion~Mycorrhiza*species*loc-Mycorrhiza:species:loc+(1|pop),data=fdat_ind)
+anova(norint.Les,Les2)
+
+Les3a<-lmer(Lesion~Mycorrhiza*species+Mycorrhiza*loc+(1|pop),data=fdat_ind)
+Les3b<-lmer(Lesion~Mycorrhiza*species+species*loc+(1|pop),data=fdat_ind)
+Les3c<-lmer(Lesion~species*loc+Mycorrhiza*loc+(1|pop),data=fdat_ind)
+anova(norint.Les,Les3a) # TEST species*loc 
+anova(norint.Les,Les3b) # TEST Myc*loc 
+anova(norint.Les,Les3c) # TEST Myc*species
+
+ggplot(fdat_ind,aes(Mycorrhiza,Lesion))+facet_wrap(~species)+
+  geom_point(aes(col=loc))+theme_simple()+geom_smooth(method="lm")
+```
+
 ## Hypothesis 1: Lesion ~ Mycorriza
 
-###Co-occurence data
+### GIVEN THE NEW ANALYSIS ABOVE, THIS ISN'T WORTHWILE BECAUSE THERE IS NO SIGNIFICANT Myc:species:loc
 
-```{r Co-occurence model using corr}
+```{r}
 # calculating the r
@@
 dfcorr %>% drop_na()->dfcorr
+```
 
+###Co-occurence data
+
+```{r Co-occurence model using corr}
 #Normal?

### 2018-02-01 MSc_Statistical_Rob_correction_-Jan29.Rmd
making sure computer and github are synched

--- 2018-01-29 MScFigures.Rmd
@@
 ---
-title: "MSc Statistical overview"
+title: "MSc Statistical Rob correction -Jan29"
 output:

### 2018-02-01 Field_work_script.R

@@ -1,0 +1,293 @@
+library(readr)
+May_2017_FloristicSurvey_summer2016 <- read_delim("~/Documents/Queens/Thesis/Data/May_2017_FloristicSurvey_summer2016.csv", 
+                                                  +     "\t", escape_double = FALSE, trim_ws = TRUE)
+FloristicSurvey<-May_2017_FloristicSurvey_summer2016
+
+PlantLength <- read_delim("~/Documents/Queens/Thesis/Data/May_2017_PlantLength_summer2016.csv", 
+                          +     "\t", escape_double = FALSE, trim_ws = TRUE)
+
+####Restructuring####
+library("dplyr")
+head(PlantLength)
+str(PlantLength)
+colnames(PlantLength)[1] <- "Population"
+PlantLength$Population<-as.factor(PlantLength$Population)
+PlantLength$Location<-as.factor(PlantLength$Location)
+
+# Simplified, clean plotting theme
+theme_simple <- function (base_size = 12, base_family = "") {
+  theme_classic(base_size = base_size, base_family = base_family) %+replace%
+    theme(
+      axis.text = element_text(colour = "black"),
+      axis.title.x = element_text(size=18),
+      axis.text.x = element_text(size=12),
+      axis.title.y = element_text(size=18,angle=90),
+      axis.text.y = element_text(size=12),
+      axis.ticks = element_blank(),
+      panel.background = element_rect(fill="white"),
+      panel.border = element_blank(),
+      plot.title=element_text(face="bold", size=24),
+#      legend.position="none"
+    )
+}
+
+####Plant length and GM presence####
+library("lme4")
+mod1<-PlantLength$Length_plant~PlantLength$Location+(1|PlantLength$Species)+(1|PlantLength$Population)
+lmer(mod1) # Just made a model, it didnt work. Why? NAs!
+row.has.na <- apply(PlantLength, 1, function(x){any(is.na(x))})
+sum(row.has.na) 
+PlantLength.filtered <- PlantLength[!row.has.na,]# Removed all the rows with NAs
+
[…]

### 2018-02-01 MSc_Statistical_Rob_correction_-Jan29.Rmd
Formating and stuff

--- 2018-01-29 MScFigures.Rmd
@@
 ---
-title: "MSc Statistical overview"
+title: "MSc Statistical Rob correction -Jan29"
 output:
-  html_document:
-    df_print: paged
-    toc: yes
   html_notebook:
@@
     theme: cerulean
+    toc: yes
+  html_document:
+    df_print: paged
     toc: yes
@@
 
-## KAT, PLEASE BREAK UP YOUR CODE INTO SMALL CHUNCKS AND EXPLAIN WHAT EACH IS DOING. 
-Load a custome theme for clean, readable graphs
+Load a custome theme for clean, readable graphs:
+
 ```{r echo=F}
@@
 
-## EXPLAIN WHAT THIS OVERDISPERSION FUNCTION IS FOR...
+Overdispersion function, tests for overdispersion in GLMM:
+
 ```{r echo=F}
@@
 ### Load/ Modify data: Co-occurence
-```{r Introduce co-occurence dataset, message=FALSE, warning=FALSE}
+```{r Introduce co-occurence dataset, message=FALSE, warning=FALSE, echo=FALSE}
 mdata <- read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
@@
 ### Load/ Modify data: Totals
-```{r Introduce total dataset, message=FALSE, warning=FALSE}
+```{r Introduce total dataset, message=FALSE, warning=FALSE, echo=FALSE}
 mdata<-read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
@@
 
-### VERY NICE PREDICTION FIGURES! PERSONALLY, I WOULD MAKE THE DOTS BIGGER AND BIVARIATE NORMAL (SEE CHANGES):
-
 Mycorrhizal colonization protects roots from lesions and herbivory.
@@
   labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
-  theme(axis.text.x = element_blank(),axis.text.y = element_blank())
+  theme(axis.text.x = element_blank(),axis.text.y = element_blank())+
+  scale_color_brewer(palette="Dark2")
 ```
@@
   theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
-  theme(axis.text.x = element_blank(),axis.text.y = element_blank())
+  theme(axis.text.x = element_blank(),axis.text.y = element_blank())+
+  scale_color_brewer(palette="Dark2")
 ```
@@
 I will find that the molecular data from the soil extraction supports this claim by having a reduced biodiversity and abundance of mycorrhiza in samples taken inside A. petiolata populations.
-
-## IMPORTANT: BEFORE RUNNING COMPLICATED MODELS: (1) TAKE A LOOK AT THE DATA, (2) RUN SIMPLE MODELS -- SEE IF IT IS EVEN WORTH YOUR TIME & EFFORT
 
@@
 # Calculate plant-level averages
-fdat_ind<-aggregate(fdata[,c("Mycorrhiza","Lesion","Herbivory")],
-                    by=list(indiv2=fdata$indiv2,pop=fdata$pop,loc=fdata$loc,species=fdata$species),
-                    pct)
-
+fdat_ind<-aggregate(fdata[,c("Mycorrhiza","Lesion","Herbivory")],by=list(indiv2=fdata$indiv2,pop=fdata$pop,loc=fdata$loc,species=fdata$species, pct))
 ```
 
-## SIMPLE LINEAR MODEL AND VISUALIZATION:
-
-### Mycorrhia model results
-
-  1. Mycorrhiza colonization is significantly higher outside patches of A. petiolata than inside
-  2a. Species vary in Mycorrhiza colonization, with highest colonization in SC and others relatively similar. 
-  2b. Effect of A. petiolata on Mycorrhiza colonization differs among species, with more pronounced effects for GR and MR, and will little effect for GA
-  3. Effect of A. petiolata on Mycorrhiza colonization varies by population, but not as strongly as among species
+#### Simple linear model visualization:
 
@@
 
-### Lesions model results
+**Mycorrhia model results**
 
-  1. Root lesions increase with mycorrhiza colonization, contrary to predictions
-  2. Effect of Mycorrhiza on Lesions depends strongly on species (Myc*species interactions)
+1. Mycorrhiza colonization is significantly higher outside patches of A. petiolata than inside
+  2a. Species vary in Mycorrhiza colonization, with highest colonization in SC and others relatively similar. 
+  2b. Effect of A. petiolata on Mycorrhiza colonization differs among species, with more pronounced effects for GR and MR, and will little effect for GA
+  3. Effect of A. petiolata on Mycorrhiza colonization varies by population, but not as strongly as among species
 
@@
 
+** Lesions model results**
+
+  1. Root lesions increase with mycorrhiza colonization, contrary to predictions
+  2. Effect of Mycorrhiza on Lesions depends strongly on species (Myc*species interactions)
+
 ## Hypothesis 1: Lesion ~ Mycorriza
 
-### GIVEN THE NEW ANALYSIS ABOVE, THIS ISN'T WORTHWILE BECAUSE THERE IS NO SIGNIFICANT Myc:species:loc
+GIVEN THE NEW ANALYSIS ABOVE, THIS ISN'T WORTHWILE BECAUSE THERE IS NO SIGNIFICANT Myc:species:loc
 
@@
 ```
-
-Co-occurence with gather: what is the difference? 
-Here I want to see that the traits are associating differently at every cross for each indiv
-
-````{r Co-occurence model GATHER}
-
-baysianGLMERmyc_lesion_GTHR <- brm(Value ~ Trait * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-summary(baysianGLMERmyc_lesion_GTHR)
-bayes_R2(baysianGLMERmyc_lesion_GTHR)
-
-baysianGLMERmyc_lesion_GTHR_1 <- brm(Value ~ Trait * location * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-baysianGLMERmyc_lesion_GTHR_2 <- brm(Value ~ Trait + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-baysianGLMERmyc_lesion_GTHR_NULL <- brm(Value ~ 1 + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-model.sel(baysianGLMERmyc_lesion_GTHR,baysianGLMERmyc_lesion_GTHR_1,baysianGLMERmyc_lesion_GTHR_2,baysianGLMERmyc_lesion_GTHR_NULL) #not sure if this function will work with brm model, if not ill just have to do a waic and then a compare like the previous...
-should test with a smaller model
-```
-**SUMMARY:**
-
-What is significant with the correlation~location*sp model?
-
-What does it change when we gather the model? What am I really testing?
-Does it really test what I want it to test?
-
-What is significant when we gather? Is this model even any good?
-
-###Totals data
-
-```{r Totals model}
-
-# model 
-GLMMmyc_lesion <- glmer(binlesion ~ None.Myc * species + (1 | pop) , data = ndatas,family = binomial(link = "logit"))
-summary(GLMMmyc_lesion)
-
-options(na.action="na.fail")
-dredge(GLMMmyc_lesion)
-r.squaredGLMM(GLMMmyc_lesion)
-# will need to change this ASAP
-
-ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path))+
-  stat_summary(fun.y=mean, geom="point")+
-  geom_smooth(method = "lm")+
-  geom_point()+
-  theme_simple()+
-  facet_wrap("species")+
-  labs(x = "Mycorrhizal colonization", y="Lesions")
-```
-**SUMMARY:**
-
-Is the totals the same as the corr data?
-
-if not what has change?
-what does it mean biologically: Same/less path=mycorrhiza defend NotSame/less path=mycorrhizal defence is not related to colonization.
-if theres not an effect then maybe it has more to do with the species composition than the actual mycorrhizal colonization, Thats why we will test pathogen colonization alone (without myc = H2)
 

### 2018-02-05 MSc_Statistical_Rob_correction_-Jan29.Rmd
commit

@@
 output:
+  html_document:
+    df_print: paged
+    toc: yes
   html_notebook:
@@
     theme: cerulean
-    toc: yes
-  html_document:
-    df_print: paged
     toc: yes
@@
 library(mefa)
+library(ggbiplot)
+library(pvclust)
+library(vegan)
 library(ggbiplot)
@@
 ```{r Introduce co-occurence dataset, message=FALSE, warning=FALSE, echo=FALSE}
-mdata <- read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
+mdata <- read.csv("CSV/Assessing_Oct_20.csv",stringsAsFactors=F)
 indiv <- mdata$CODE[!mdata$CODE==""]
@@
 ```{r Introduce total dataset, message=FALSE, warning=FALSE, echo=FALSE}
-mdata<-read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
+mdata<-read.csv("CSV/Assessing_Oct_20.csv",stringsAsFactors=F)
 indiv<-mdata$CODE[!mdata$CODE==""]
@@
 ndatas[,numcols] <- scale(ndatas[,numcols])
+```
+
+### Field survey data
+
+```{r}
+FloristicSurvey <-read.csv("CSV/May_2017_FloristicSurvey_summer2016.csv", sep="\t")
+PlantLength <- read.csv("CSV/May_2017_PlantLength_summer2016.csv", sep="\t")
+Soil_characteristics <- read.csv("CSV/Soil_characteristics.txt", sep="\t")
+
+#Restructuring
+head(PlantLength)
+str(PlantLength)
+colnames(PlantLength)[1] <- "Population"
+PlantLength$Population<-as.factor(PlantLength$Population)
+PlantLength$Location<-as.factor(PlantLength$Location)
+
+```
+
+### Root size
+```{r}
+Root_size <-read.csv("CSV/Root_size.csv")
 ```
@@
 
+# Field Data Analysis
+
+## Plant length and GM presence
+
+```{r}
+mod1<-PlantLength$Length_plant~PlantLength$Location+(1|PlantLength$Species)+(1|PlantLength$Population)
+row.has.na <- apply(PlantLength, 1, function(x){any(is.na(x))})
+sum(row.has.na) 
+PlantLength.filtered <- PlantLength[!row.has.na,]# Removed all the rows with NAs
+
+mod1<-lmer(log(PlantLength.filtered$Length_plant)~PlantLength.filtered$Location+(1|PlantLength.filtered$Species)+(1|PlantLength.filtered$Population))
+mod2<-lmer(log(PlantLength.filtered$Length_plant)~PlantLength.filtered$Location+(1|PlantLength.filtered$Species))
+mod3<-lmer(log(PlantLength.filtered$Length_plant)~1+(1|PlantLength.filtered$Species)+(1|PlantLength.filtered$Population))
+# Made these three models, one is all of them, one no population, and one no in/ out
+summary(mod1)
+anova(mod1,mod2) # One ANOVA with model 1, one with model 2 to compare if they are statistically significantly different from each other
+qplot(predict(mod1),log(PlantLength.filtered$Length_plant)) #is this model normal? NO
+qplot(predict(mod1),log(PlantLength.filtered$Length_plant)-predict(mod1)) # Make this model normal by log() the y variable.
+cor(predict(mod1),PlantLength.filtered$Length_plant)^2 # Are the correlation coefficients meaningful?
+cor(predict(mod2),PlantLength.filtered$Length_plant)^2 # Are the correlation coefficients meaningful wihout pops?
+
+anova(mod1,mod3) # Repeat with a model without the in/ out component.
+cor(predict(mod3),PlantLength.filtered$Length_plant)^2 # how much different does it make when we consider GM?
+```
+
+## Floristic composition and GM presence
+
+```{r}
+colnames(FloristicSurvey)[1] <- "Population" # population loads in weirdly, I am just arranging it to not have quotes around. so odd
+FloristicSurvey$Population<-as.factor(FloristicSurvey$Population) # Make the population a factor and not an interger
+FloristicSurvey[is.na(FloristicSurvey)] <- 0
+sum(row.has.na <- apply(FloristicSurvey, 1, function(x){any(is.na(x))}))
+
+# Start the PCA
+PC <- prcomp(FloristicSurvey[,4:ncol(FloristicSurvey)], center=T)
+summary(PC)
+screeplot(PC)
+
+# Variation explaination
+100*sum(summary(PC)[[1]][1])/sum(summary(PC)[[1]]) #explained by just PC1
+100*sum(summary(PC)[[1]][1:2])/sum(summary(PC)[[1]])#explained by PC1 and PC2
+n=25
+100*sum(summary(PC)[[1]][1:n])/sum(summary(PC)[[1]])
+```
+
+### Linear discriminate analysis
+```{r}
+# Discriminant function analysis is used (general LDA format) because i have a cat. dependent and a binary independent. (it needs binary or continuous!)
+# you might have to bin covers because it only works with categorical, so 0-5% none, 6-40 low etc.
+FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,20,50,80,100), labels = c("None", "Med_Low", "Med_High", "Overtaken"))
+table(FloristicSurvey$GM_Coverage_category)
+# [0-20] None
+# ]20-50] Medium low
+# ]50-80] Medium high
+# ]80-100] Overtaken
+```
+
+### LDA
+```{r}
+#LDA
+FloristicSurveysmall<-data.frame(FloristicSurvey[,4:56])
+# Linear discriminant function analysis
+
+FloristicSurveysmall <- FloristicSurveysmall[,-c(42,45)] 
+FloristicSurveyLDA <- lda(GM_Coverage_category ~., data=FloristicSurveysmall)
+# Extract scaling vectors
+scalvec<-data.frame(FloristicSurveyLDA$scaling)
+# Extract predictions
+FloristicSurveyLDAval <- data.frame(predict(FloristicSurveyLDA)$x)
+
+# Plot results
+ggplot(data=FloristicSurveyLDAval,aes(x=LD1, y=LD2, group=FloristicSurveysmall$GM_Coverage_category))+
+  stat_ellipse(geom="polygon",aes(colour=FloristicSurveysmall$GM_Coverage_category),fill=NA,size=1.2,alpha=0.3)+
+  stat_ellipse(geom="polygon",aes(fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=1.2,alpha=0.3)+
+  geom_point(aes(shape=FloristicSurveysmall$GM_Coverage_category,fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=I(4),alpha=I(0.8))+
+  xlab("LD Axis 1")+ylab("LD Axis 2")+theme_simple() +
+  theme(legend.title=element_blank())
+
+#test significance of axis
+anova(lm(FloristicSurveyLDAval$LD1~FloristicSurveysmall$GM_Coverage_category))
+anova(lm(FloristicSurveyLDAval$LD2~FloristicSurveysmall$GM_Coverage_category))
+
+#LDA WITHOUT A. PETIOLATA
+FloristicSurveysmall<-data.frame(FloristicSurvey[,4:56])
+# Linear discriminant function analysis
+FloristicSurveysmall[10]<-NULL
+FloristicSurveysmall[c(41,44)] <- NULL 
+FloristicSurveyLDA<-lda(GM_Coverage_category ~ ., data=FloristicSurveysmall)
+# Extract scaling vectors
+scalvec<-data.frame(FloristicSurveyLDA$scaling)
+# Extract predictions
+FloristicSurveyLDAval <- data.frame(predict(FloristicSurveyLDA)$x)
+
+# Plot results
+ggplot(data=FloristicSurveyLDAval,aes(x=LD1,y=LD2,group=FloristicSurveysmall$GM_Coverage_category))+
+  stat_ellipse(geom="polygon",aes(colour=FloristicSurveysmall$GM_Coverage_category),fill=NA,size=1.2,alpha=0.3)+
+  stat_ellipse(geom="polygon",aes(fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=1.2,alpha=0.3)+
+  geom_point(aes(shape=FloristicSurveysmall$GM_Coverage_category,fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=I(4),alpha=I(0.8))+
+  xlab("LD Axis 1")+ylab("LD Axis 2")+theme_simple() +
+  theme(legend.title=element_blank())
+
+#test significance of axis
+anova(lm(FloristicSurveyLDAval$LD1~FloristicSurveysmall$GM_Coverage_category))
+anova(lm(FloristicSurveyLDAval$LD2~FloristicSurveysmall$GM_Coverage_category))
+```
+
+### Cluster analysis
+```{r}
+# Ward Hierarchical Clustering with Bootstrapped p values
+#do they cluster by population?
+FloristicSurvey[is.na(FloristicSurvey)] <- 0
+mydata<-t(data.frame(FloristicSurvey[,1],FloristicSurvey[,4:55]))
+my.names <- mydata[1,]
+colnames(mydata) <- my.names
+mydata <- mydata[-1,]
+d <- dist(t(mydata), method = "euclidean") # distance matrix
+fit <- hclust(d, method = "ward.D")
+plot(fit)
+
+#do they cluster by GM coverage?
+FloristicSurvey[is.na(FloristicSurvey)] <- 0
+#this will just make the dendogram easier to see
+FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,5,30,50,70,95,100), labels = c("N", "L", "ML", "MH", "H", "F"))
+mydata<-t(data.frame(FloristicSurvey[,56],FloristicSurvey[,4:55]))
+my.names <- mydata[1,]
+colnames(mydata) <- my.names
+mydata <- mydata[-1,]
+d <- dist(t(mydata), method = "euclidean") # distance matrix
+fit <- hclust(d, method = "ward.D")
+plot(fit) 
+FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,5,30,50,70,95,100), labels = c("None", "Low", "Med_Low", "Med_High", "High", "Overtaken"))
+
+```
+
+### NMDS 
+```{r}
+# https://jonlefcheck.net/2012/10/24/nmds-tutorial-in-r/
+# https://oliviarata.wordpress.com/2014/04/17/ordinations-in-ggplot2/
+#Make a matrix with no row or column equal to 0 (do not enclude the env variable (GM COVERAGE))
+M <- as.matrix(FloristicSurvey[1:198,4:55])
+M[is.na(M)] <- 0
+rownames(M) <- FloristicSurvey$Population
+which( colSums(M)==0 )
+which( rowSums(M)==0 )
+#Now that you know which column must be taken out, redo the matrix but with the last column, then remove the rows and columns =0
+#I did this because the previous method doesnt work with the characters in the GM_COVERAGE column.
+M <- as.matrix(FloristicSurvey[1:198,4:56])
+M[is.na(M)] <- 0
+rownames(M) <- FloristicSurvey$Population
+M<-M[,-45]
+M<-M[-130,]
+M<-M[-133,]
+M<-M[-132,]
+# Now I'll make the env column a vector on its own, but the previous colde now allows it to be in the same order as the matrix im using for distances.
+GM_coverage_df <- data.frame(M[,52])
+M<-M[,-52]
+class(M) <- "numeric"
+# with vegdist from Bray to seroeson: add binary = T 
+dist_FloristicSurvey <- vegdist(M, method = "bray", binary = T)
+#The metaMDS analysis could have done the distance matrix internally but i would rather control it since i have presence/abscence
+meta.nmds.FloristicSurvey <- metaMDS(dist_FloristicSurvey)
+# Non convergence with only 20 tries. lets increase that then
+meta.nmds.FloristicSurvey2D <- metaMDS(dist_FloristicSurvey, k=2, trymax = 1000)
+str(meta.nmds.FloristicSurvey2D)
+stressplot(meta.nmds.FloristicSurvey2D)
+# Im getting a little above a stress of 0.2 (0.207), which isnt ideal, ill try it again with 3 dimension
+# A good rule of thumb: stress < 0.05 provides an excellent representation in reduced dimensions, < 0.1 is great, < 0.2 is good/ok, and stress < 0.3 provides a poor representation.
+meta.nmds.FloristicSurvey3D <- metaMDS(dist_FloristicSurvey, k=3, trymax = 1000)
+str(meta.nmds.FloristicSurvey3D)
+# stress is lower! 0.146
+stressplot(meta.nmds.FloristicSurvey3D)
+
+# envfit for the 2D
+FloristicSurvey_envfit <- envfit(meta.nmds.FloristicSurvey2D, env = GM_coverage_df, perm = 999) #standard envfit
+FloristicSurvey_envfit
+
+#data for plotting 
+##NMDS points
+FloristicSurvey.NMDS.data<-GM_coverage_df 
+FloristicSurvey.NMDS.data$NMDS1<-meta.nmds.FloristicSurvey2D$points[ ,1] 
+FloristicSurvey.NMDS.data$NMDS2<-meta.nmds.FloristicSurvey2D$points[ ,2] 
+colnames(FloristicSurvey.NMDS.data)[1] <- "GM_Coverage"
+
+# data for the envfit arrows
+env.scores.FloristicSurvey <- as.data.frame(scores(FloristicSurvey_envfit, display = "vectors")) #extracts relevant scores from envifit
+env.scores.FloristicSurvey <- cbind(env.scores.FloristicSurvey, env.variables = rownames(env.scores.FloristicSurvey)) #and then gives them their names
+
+# function for ellipsess - just run this, is used later
+#taken from the excellent stackoverflow Q+A: http://stackoverflow.com/questions/13794419/plotting-ordiellipse-function-from-vegan-package-onto-nmds-plot-created-in-ggplo
+veganCovEllipse <- function (cov, center = c(0, 0), scale = 1, npoints = 100) 
+{
+  theta <- (0:npoints) * 2 * pi/npoints
+  Circle <- cbind(cos(theta), sin(theta))
+  t(center + scale * t(Circle %*% chol(cov)))
+}
+
+#data for ellipse, use GM coverage
+df_ell.FSurvey.GM_coverage <- data.frame() #sets up a data frame before running the function.
+for(g in levels(FloristicSurvey.NMDS.data$GM_Coverage)){
+  df_ell.FSurvey.GM_coverage <- rbind(df_ell.FSurvey.GM_coverage, cbind(as.data.frame(with(FloristicSurvey.NMDS.data [FloristicSurvey.NMDS.data$GM_Coverage==g,],
+                                                                                   veganCovEllipse(cov.wt(cbind(NMDS1,NMDS2),wt=rep(1/length(NMDS1),length(NMDS1)))$cov,center=c(mean(NMDS1),mean(NMDS2)))))
+                                                                ,GM_coverage=g))
+}
+
+# data for labelling the ellipse
+NMDS.mean.FloristicSurvey=aggregate(FloristicSurvey.NMDS.data[ ,c("NMDS1", "NMDS2")], 
+                         list(group = FloristicSurvey.NMDS.data$GM_Coverage), mean)
+
+## finally plotting.
+mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
+FloristicSurvey.nmds.gg1 <- ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ #sets up the plot. brackets around the entire thing to make it draw automatically
+    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, alpha=df_ell.FSurvey.GM_coverage$GM_coverage))+ #this is the ellipse, seperate ones by Site.
+If you didn't change the "alpha" (the shade) then you need to keep the "group
+    scale_alpha_manual(guide = FALSE,values=c(0.3, 0.5, 0.6, 0.7, 0.8, 0.9))+ #sets the shade for the ellipse
+    geom_point( aes(shape = FloristicSurvey.NMDS.data$GM_Coverage), size = 1) + #puts the site points in from the ordination, shape determined by site, size refers to size of point
+    # geom_text(data=spps2, aes(x=spps2$NMDS1, y=spps2$NMDS2, label=species), size = 3.3, hjust=1.1)+ #labelling the species. hjust used to shift them slightly from their points
+    #annotate("text",x = NMDS.mean$NMDS1,y = NMDS.mean$NMDS2,label=NMDS.mean$group) + #labels for the centroids - I haven't used this since we have a legend.
+but you could also dithc the legend, but plot will get v messy
+    #geom_segment(data = env.scores.FloristicSurvey,
+    #             aes(x = 0, xend = mult*env.scores.FloristicSurvey$NMDS1, y = 0, yend = mult*env.scores.FloristicSurvey$NMDS2),
+    #             arrow = arrow(length = unit(0.25, "cm")), colour = "grey") + #arrows for envfit.
+doubled the length for similarity to the plot() function.
+NB check ?envfit regarding arrow length if not familiar with lengths
+    #geom_text(data = env.scores.FloristicSurvey, #labels the environmental variable arrows * "mult" as for the arrows
+    #          aes(x = mult*env.scores.FloristicSurvey$NMDS1, y = mult*env.scores.FloristicSurvey$NMDS2, label=env.variables),
+    #          size = 5,
+    #          hjust = -0.5)+
+    scale_shape_manual(values = c(1,8,19,5,6,7))+ #sets the shape of the plot points instead of using whatever ggplot2 automatically provides
+    coord_cartesian(xlim = c(-1,1.5))+  ## NB this changes the visible area of the plot only (this is a good thing, apparently). Can also specify ylim. Here in case you want to set xaxis manually.
+    theme_simple()
+```
+
+# Soil Characteristics
+
+```{r}
+Soil_characteristics$Location<-as.factor(Soil_characteristics$Location)
+GLmodel_soil <- glm(Location ~Agg_stability*C_percent*N_percent,family=binomial(link='logit'),data=Soil_characteristics)
+summary(GLmodel_soil)
+
+Soil_characteristics2 <- data.frame(Soil_characteristics$Population, Soil_characteristics$Location, log(Soil_characteristics$pH), log(Soil_characteristics$Agg_stability), log(Soil_characteristics$C_percent), log(Soil_characteristics$N_percent))
+Soil_characteristics2<-rename(Soil_characteristics2, c("Soil_characteristics.Population"="Population", "Soil_characteristics.Location"="Location", "log.Soil_characteristics.pH."="pH", "log.Soil_characteristics.Agg_stability."="Agg_stability", "log.Soil_characteristics.C_percent."="Percent","log.Soil_characteristics.N_percent."="Percent" ))
+df2 <- reshape2::melt(Soil_characteristics2, id.var=c("Population","Location"))
+df2 <- rename(df2, c("value"="Log_value"))
+
+p <- ggplot(Soil_characteristics, aes(Location,pH,fill=Location))
+p + geom_boxplot() +
+  theme_simple()
+```
 # Histology data Analysis
 
-### Data exploration:
+### Data exploration
 
@@
 # Calculate plant-level averages
-fdat_ind<-aggregate(fdata[,c("Mycorrhiza","Lesion","Herbivory")],by=list(indiv2=fdata$indiv2,pop=fdata$pop,loc=fdata$loc,species=fdata$species, pct))
+fdat_ind<-aggregate(fdata[,c("Mycorrhiza","Lesion","Herbivory")],by=list(indiv2=fdata$indiv2,pop=fdata$pop,loc=fdata$loc,species=fdata$species), FUN=pct)
+
 ```
@@
 
-```{r Co-occurence model using corr}
+```{r Co-occurence model using corr, eval=FALSE}
 #Normal?
@@
 
+###Totals data
+
+```{r Totals model}
+
+# model 
+GLMMmyc_lesion <- glmer(binlesion ~ None.Myc * species + (1 | pop) , data = ndatas,family = binomial(link = "logit"))
+summary(GLMMmyc_lesion)
+
+options(na.action="na.fail")
+dredge(GLMMmyc_lesion)
+r.squaredGLMM(GLMMmyc_lesion)
+# will need to change this ASAP
+
+ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path))+
+  stat_summary(fun.y=mean, geom="point")+
+  geom_smooth(method = "lm")+
+  geom_point()+
+  theme_simple()+
+  facet_wrap("species")+
+  labs(x = "Mycorrhizal colonization", y="Lesions")
+```
+
 ## Hypothesis 2: Mycorrhiza & Lesion ~ invasion
@@
 location <- ndata[,13]
-library(ggbiplot)
 g <- ggbiplot(pca, obs.scale = 1, var.scale = 1, 
@@
 
-## Hypothesis 3: Lesion ~ Mycorriza * invasion
+## Hypothesis 3 + 4: Lesion ~ Mycorriza * invasion
 
@@
 
+# Combining histology and field data
+
 # Molecular data Analysis

### 2018-02-07 MSc_Statistical_Rob_correction_-Jan29.Rmd
formating

@@
 ```
+
 ### Hypothesis 3
@@
 
-### Data exploration
+# Histology Data exploration
 

### 2018-02-08 MSc_Statistical_Rob_correction_-Jan29.Rmd
PCA and working on field data

@@
 ```{r}
-mod1<-PlantLength$Length_plant~PlantLength$Location+(1|PlantLength$Species)+(1|PlantLength$Population)
 row.has.na <- apply(PlantLength, 1, function(x){any(is.na(x))})
@@
 
-mod1<-lmer(log(PlantLength.filtered$Length_plant)~PlantLength.filtered$Location+(1|PlantLength.filtered$Species)+(1|PlantLength.filtered$Population))
-mod2<-lmer(log(PlantLength.filtered$Length_plant)~PlantLength.filtered$Location+(1|PlantLength.filtered$Species))
-mod3<-lmer(log(PlantLength.filtered$Length_plant)~1+(1|PlantLength.filtered$Species)+(1|PlantLength.filtered$Population))
-# Made these three models, one is all of them, one no population, and one no in/ out
+car::qqp(PlantLength$Length_plant, "norm")
+shapiro.test(PlantLength$Length_plant)
+
+par(mfrow = c(1,1))
+descdist(PlantLength.filtered$Length_plant, discrete = FALSE, boot = 1000)
+f1g <- fitdist(PlantLength.filtered$Length_plant, "lnorm") 
+f2g <- fitdist(PlantLength.filtered$Length_plant, "norm") 
+f3g <- fitdist(PlantLength.filtered$Length_plant, "gamma")
+f4g <- fitdist(PlantLength.filtered$Length_plant, "weibull")
+f1g$aic
+f2g$aic
+f3g$aic
+f4g$aic
+
+mod1<-lm(Length_plant~Location*Species, data=PlantLength.filtered)
+
+bc<-boxcox(mod1, lambda = seq(-2, 2, 0.1))
+lambda <- bc$x[which.max(bc$y)]
+PlantLength.filtered <- cbind(PlantLength.filtered, ((PlantLength.filtered$Length_plant^lambda)-1)/lambda)
+names(PlantLength.filtered)[5] <- "Yprime"
+mod1BC <- lm(Yprime~Location*Species, data=PlantLength.filtered)
+
+par(mfrow = c(2, 2))
+plot(mod1BC)
+# This is basically a log transformation.
+
+# Multicolinearity?
+car::vif(mod1BC)
+sqrt(car::vif(mod1BC)) > 2
+
+mod1<-lmer(log(Length_plant)~Location*Species+(1|Pop), data=PlantLength.filtered)
+
+mod2<-lmer(log(Length_plant)~Location+(1|Pop), data=PlantLength.filtered)
+
+mod3<-lmer(log(Length_plant)~1+(1|Pop), data=PlantLength.filtered)
+
+AICres <- model.sel(mod1,mod2,mod3)
+r.squaredLR(mod1)
 summary(mod1)
-anova(mod1,mod2) # One ANOVA with model 1, one with model 2 to compare if they are statistically significantly different from each other
-qplot(predict(mod1),log(PlantLength.filtered$Length_plant)) #is this model normal? NO
-qplot(predict(mod1),log(PlantLength.filtered$Length_plant)-predict(mod1)) # Make this model normal by log() the y variable.
-cor(predict(mod1),PlantLength.filtered$Length_plant)^2 # Are the correlation coefficients meaningful?
-cor(predict(mod2),PlantLength.filtered$Length_plant)^2 # Are the correlation coefficients meaningful wihout pops?
-
-anova(mod1,mod3) # Repeat with a model without the in/ out component.
-cor(predict(mod3),PlantLength.filtered$Length_plant)^2 # how much different does it make when we consider GM?
+confint(mod1)
 ```
@@
 
+### PCA
 ```{r}
@@
 # you might have to bin covers because it only works with categorical, so 0-5% none, 6-40 low etc.
-FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,20,50,80,100), labels = c("None", "Med_Low", "Med_High", "Overtaken"))
+FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("None", "Med_Low", "Med_High", "Overtaken"))
 table(FloristicSurvey$GM_Coverage_category)
@@
 
-### LDA
 ```{r}
@@
 fit <- hclust(d, method = "ward.D")
-plot(fit)
+fitd <- as.dendrogram(fit)
+
+par(mfrow=c(3,2))
+plot(fit,cex=0.4,main="Clustering with populations")
+plot(cut(fitd, h=10)$upper, main="Upper tree of cut at h=10")
+plot(cut(fitd, h=10)$lower[[1]], main="First branch of lower tree with cut at h=10")
+plot(cut(fitd, h=10)$lower[[2]], main="Second branch of lower tree with cut at h=10")
+plot(cut(fitd, h=10)$lower[[3]], main="Third branch of lower tree with cut at h=10")
+plot(cut(fitd, h=10)$lower[[4]], main="Fourth branch of lower tree with cut at h=10")
 
@@
 #this will just make the dendogram easier to see
-FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,5,30,50,70,95,100), labels = c("N", "L", "ML", "MH", "H", "F"))
+FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("None", "ML", "MH", "High"))
 mydata<-t(data.frame(FloristicSurvey[,56],FloristicSurvey[,4:55]))
@@
 fit <- hclust(d, method = "ward.D")
-plot(fit) 
+fitd <- as.dendrogram(fit)
 FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,5,30,50,70,95,100), labels = c("None", "Low", "Med_Low", "Med_High", "High", "Overtaken"))
 
+par(mfrow=c(3,2))
+plot(fit,cex=0.4,main="Clustering with populations")
+plot(cut(fitd, h=10)$upper, main="Upper tree of cut at h=10")
+plot(cut(fitd, h=10)$lower[[1]], main="First branch of lower tree with cut at h=10")
+plot(cut(fitd, h=10)$lower[[2]], main="Second branch of lower tree with cut at h=10")
+plot(cut(fitd, h=10)$lower[[3]], main="Third branch of lower tree with cut at h=10")
+plot(cut(fitd, h=10)$lower[[4]], main="Fourth branch of lower tree with cut at h=10")
 ```
@@
 #The metaMDS analysis could have done the distance matrix internally but i would rather control it since i have presence/abscence
-meta.nmds.FloristicSurvey <- metaMDS(dist_FloristicSurvey)
-# Non convergence with only 20 tries. lets increase that then
+
 meta.nmds.FloristicSurvey2D <- metaMDS(dist_FloristicSurvey, k=2, trymax = 1000)
+
 str(meta.nmds.FloristicSurvey2D)
 stressplot(meta.nmds.FloristicSurvey2D)
-# Im getting a little above a stress of 0.2 (0.207), which isnt ideal, ill try it again with 3 dimension
-# A good rule of thumb: stress < 0.05 provides an excellent representation in reduced dimensions, < 0.1 is great, < 0.2 is good/ok, and stress < 0.3 provides a poor representation.
-meta.nmds.FloristicSurvey3D <- metaMDS(dist_FloristicSurvey, k=3, trymax = 1000)
-str(meta.nmds.FloristicSurvey3D)
-# stress is lower! 0.146
-stressplot(meta.nmds.FloristicSurvey3D)
 
@@
 mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
-FloristicSurvey.nmds.gg1 <- ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ #sets up the plot. brackets around the entire thing to make it draw automatically
-    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, alpha=df_ell.FSurvey.GM_coverage$GM_coverage))+ #this is the ellipse, seperate ones by Site.
-If you didn't change the "alpha" (the shade) then you need to keep the "group
-    scale_alpha_manual(guide = FALSE,values=c(0.3, 0.5, 0.6, 0.7, 0.8, 0.9))+ #sets the shade for the ellipse
-    geom_point( aes(shape = FloristicSurvey.NMDS.data$GM_Coverage), size = 1) + #puts the site points in from the ordination, shape determined by site, size refers to size of point
-    # geom_text(data=spps2, aes(x=spps2$NMDS1, y=spps2$NMDS2, label=species), size = 3.3, hjust=1.1)+ #labelling the species. hjust used to shift them slightly from their points
-    #annotate("text",x = NMDS.mean$NMDS1,y = NMDS.mean$NMDS2,label=NMDS.mean$group) + #labels for the centroids - I haven't used this since we have a legend.
-but you could also dithc the legend, but plot will get v messy
-    #geom_segment(data = env.scores.FloristicSurvey,
-    #             aes(x = 0, xend = mult*env.scores.FloristicSurvey$NMDS1, y = 0, yend = mult*env.scores.FloristicSurvey$NMDS2),
-    #             arrow = arrow(length = unit(0.25, "cm")), colour = "grey") + #arrows for envfit.
-doubled the length for similarity to the plot() function.
-NB check ?envfit regarding arrow length if not familiar with lengths
-    #geom_text(data = env.scores.FloristicSurvey, #labels the environmental variable arrows * "mult" as for the arrows
-    #          aes(x = mult*env.scores.FloristicSurvey$NMDS1, y = mult*env.scores.FloristicSurvey$NMDS2, label=env.variables),
-    #          size = 5,
-    #          hjust = -0.5)+
-    scale_shape_manual(values = c(1,8,19,5,6,7))+ #sets the shape of the plot points instead of using whatever ggplot2 automatically provides
-    coord_cartesian(xlim = c(-1,1.5))+  ## NB this changes the visible area of the plot only (this is a good thing, apparently). Can also specify ylim. Here in case you want to set xaxis manually.
-    theme_simple()
+FloristicSurvey.nmds.gg1 <- ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
+    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, alpha=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
+    scale_alpha_manual(guide = FALSE,values=c(0.3, 0.5, 0.6, 0.7))+ 
+    geom_point( aes(shape = FloristicSurvey.NMDS.data$GM_Coverage), size = 1)+ 
+    annotate("text",x = NMDS.mean.FloristicSurvey$NMDS1,y = NMDS.mean.FloristicSurvey$NMDS2,label=NMDS.mean.FloristicSurvey$group)+ 
+    geom_segment(data = env.scores.FloristicSurvey,aes(x = 0, xend = mult*env.scores.FloristicSurvey$NMDS1, y = 0, yend = mult*env.scores.FloristicSurvey$NMDS2),arrow = arrow(length = unit(0.25, "cm")), colour = "grey")+
+    geom_text(data = env.scores.FloristicSurvey,aes(x = mult*env.scores.FloristicSurvey$NMDS1, y = mult*env.scores.FloristicSurvey$NMDS2, label=env.variables),size = 5, hjust = -0.5)+ 
+    scale_shape_manual(values = c(1,8,19,5))+ 
+    coord_cartesian(xlim = c(-1,1.5)) 
 ```
@@
 
-```{r}
+```{r, Soil Characteristics}
 Soil_characteristics$Location<-as.factor(Soil_characteristics$Location)
@@
 
-p <- ggplot(Soil_characteristics, aes(Location,pH,fill=Location))
-p + geom_boxplot() +
+par(mfrow=c(2,2))
+ggplot(Soil_characteristics, aes(Location,Agg_stability,fill=Location))+ geom_boxplot() +
   theme_simple()
+ggplot(Soil_characteristics, aes(Location,pH,fill=Location))+ geom_boxplot() +
+  theme_simple()
+ggplot(Soil_characteristics, aes(Location,C_percent,fill=Location))+ geom_boxplot() +
+  theme_simple()
+ggplot(Soil_characteristics, aes(Location,N_percent,fill=Location))+ geom_boxplot() +
+  theme_simple()
+
 ```

### 2018-02-09 MSc_Statistical_Rob_correction_-Jan29.Rmd
Models putting everything together!

@@
 library(ggbiplot)
+library(factoextra)
 ```
@@
 
+FloristicSurvey$Population<-as.factor(FloristicSurvey$Population) # Make the population a factor and not an interger
+FloristicSurvey[is.na(FloristicSurvey)] <- 0
+sum(row.has.na <- apply(FloristicSurvey, 1, function(x){any(is.na(x))}))
+
 ```
@@
 Root_size <-read.csv("CSV/Root_size.csv")
+Root_size$pop<-gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",Root_size$indiv)
+Root_size$location<-gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",Root_size$indiv)
+Root_size$species<-gsub("^[0-9]+[I,O]([A-Z]+).*","\\1",Root_size$indiv)
+Root_size$location<-as.factor(Root_size$location)
+Root_size$species<-as.factor(Root_size$species)
+Root_size$pop<-as.factor(Root_size$pop)
 ```
@@
 
-### PCA
-```{r}
-colnames(FloristicSurvey)[1] <- "Population" # population loads in weirdly, I am just arranging it to not have quotes around. so odd
-FloristicSurvey$Population<-as.factor(FloristicSurvey$Population) # Make the population a factor and not an interger
-FloristicSurvey[is.na(FloristicSurvey)] <- 0
-sum(row.has.na <- apply(FloristicSurvey, 1, function(x){any(is.na(x))}))
-
-# Start the PCA
-PC <- prcomp(FloristicSurvey[,4:ncol(FloristicSurvey)], center=T)
-summary(PC)
-screeplot(PC)
-
-# Variation explaination
-100*sum(summary(PC)[[1]][1])/sum(summary(PC)[[1]]) #explained by just PC1
-100*sum(summary(PC)[[1]][1:2])/sum(summary(PC)[[1]])#explained by PC1 and PC2
-n=25
-100*sum(summary(PC)[[1]][1:n])/sum(summary(PC)[[1]])
-```
-
 ### Linear discriminate analysis
@@
 mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
-FloristicSurvey.nmds.gg1 <- ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
-    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, alpha=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
-    scale_alpha_manual(guide = FALSE,values=c(0.3, 0.5, 0.6, 0.7))+ 
-    geom_point( aes(shape = FloristicSurvey.NMDS.data$GM_Coverage), size = 1)+ 
-    annotate("text",x = NMDS.mean.FloristicSurvey$NMDS1,y = NMDS.mean.FloristicSurvey$NMDS2,label=NMDS.mean.FloristicSurvey$group)+ 
-    geom_segment(data = env.scores.FloristicSurvey,aes(x = 0, xend = mult*env.scores.FloristicSurvey$NMDS1, y = 0, yend = mult*env.scores.FloristicSurvey$NMDS2),arrow = arrow(length = unit(0.25, "cm")), colour = "grey")+
-    geom_text(data = env.scores.FloristicSurvey,aes(x = mult*env.scores.FloristicSurvey$NMDS1, y = mult*env.scores.FloristicSurvey$NMDS2, label=env.variables),size = 5, hjust = -0.5)+ 
-    scale_shape_manual(values = c(1,8,19,5))+ 
-    coord_cartesian(xlim = c(-1,1.5)) 
+ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
+    geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, color=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
+    geom_point( aes(color = FloristicSurvey.NMDS.data$GM_Coverage), size = 1)+ 
+    scale_color_manual(values = c(14,5,19,2))+ 
+    coord_cartesian(xlim = c(-1,1.5))+
+  theme_simple()+ guides(color=guide_legend("Garlic Mustard Coverage"))
 ```
+### PCA
+```{r}
+FloristicSurvey<-FloristicSurvey[,-56]
+FloristicSurvey.pca <- prcomp(FloristicSurvey[,4:(ncol(FloristicSurvey))],center = TRUE) 
+summary(FloristicSurvey.pca)
+fviz_eig(FloristicSurvey.pca,addlabels=TRUE,hjust = -0.3)+theme_simple()
+
+round(FloristicSurvey.pca$sdev^2/sum(FloristicSurvey.pca$sdev^2)*100,2)
+# About 25% explained by my first 2 eigenvectors. 50% by the first 6.
+```
+### Modeling (redundancy analysis)
+species comp ~ GMcov * pop + soil characteristics inside and outside as covariates? 
+```{r}
+
+species<-names(FloristicSurvey[4:(length(FloristicSurvey))])
+SpeciesGMCorrelation <- data.frame(matrix(ncol = 3, nrow = 0))
+names(SpeciesGMCorrelation)<-c("Species", "PValue","signif")
+
+for(i in 4:(length(FloristicSurvey))){
+  SpeciesGMCorrelation[i-3,1]<-names(FloristicSurvey[i])
+  SpeciesGMCorrelation[i-3,2]<-summary(glm(FloristicSurvey[,i]~GM_Coverage, data=FloristicSurvey, family = binomial))$coefficients[8]
+}
+for(i in 1:length(species)) if( SpeciesGMCorrelation[i,2] <= 0.05){
+  SpeciesGMCorrelation[i,3]<-c("TRUE")
+}else{
+  SpeciesGMCorrelation[i,3]<-c("FALSE")
+  }
+length(SpeciesGMCorrelation$signif[SpeciesGMCorrelation[,3]==TRUE])/length(SpeciesGMCorrelation$signif)*100
+SpeciesGMCorrelation$Species[SpeciesGMCorrelation[,3]==TRUE]
+
+# Redundancy analysis
+sp.comp <- FloristicSurvey[,4:(length(FloristicSurvey))]
+var <- FloristicSurvey[,1:3]
+var$Quadrat <- as.character(var$Quadrat)
+for(i in 1:length(var$Quadrat))if(var$Population[i] == "7"){
+  var$Quadrat[i]<-paste("7",var$Quadrat[i],sep="")
+}else if(var$Population[i] == "3"){
+  var$Quadrat[i]<-paste("3",var$Quadrat[i],sep="")
+}else if(var$Population[i] == "14"){
+  var$Quadrat[i]<-paste("14",var$Quadrat[i],sep="")
+}else if(var$Population[i] == "13"){
+  var$Quadrat[i]<-paste("13",var$Quadrat[i],sep="")
+}else if(var$Population[i] == "1"){
+  var$Quadrat[i]<-paste("1",var$Quadrat[i],sep="")
+}
+
+var$Population <- as.factor(var$Population)
+
+formulaRDA <- rda(sp.comp ~ GM_Coverage + Condition(Population) , data=var)
+
+formulaRDA <- rda(sp.comp ~ GM_Coverage , data=var)
+head(summary(formulaRDA))
+RsquareAdj(formulaRDA)
+plot(formulaRDA, scaling = 2)
+anova.cca(formulaRDA,step=1000)
+anova.cca(formulaRDA,by="axis", step=1000)
+
+```
+*Note that I redid this with GM_coverage_catogory and i didnt find ANY significance!
 
@@
   theme_simple()
+Soil_characteristics$Population<-as.factor(Soil_characteristics$Population)
 
+GLMER_soil <- glmer(Location~scale(Agg_stability)*scale(C_percent)*scale(N_percent)+(1|Population),family=binomial(link='logit'),data=Soil_characteristics)
+summary(GLMER_soil)
+options(na.action = "na.fail")
+dredge(GLMER_soil) 
+# A model with nothing is best...
 ```
@@
 
-# Combining histology and field data
+## Bring things together
+
+```{r}
+Soil_characteristics$Location<-as.character(Soil_characteristics$Location)
+for(i in 1:length(Soil_characteristics$Location))if(Soil_characteristics[i,2]=="in"){
+   Soil_characteristics[i,2]<-"I"
+}else{
+  Soil_characteristics[i,2]<-"O"
+}
+Soil_characteristics$Location<-as.factor(Soil_characteristics$Location)  
+names(Soil_characteristics)[1:2]<-c("pop","location")
+
+fulldata <- merge(Soil_characteristics, ndata, by=c("pop","location"))
+# note i used the SCALED dataframe for the total histology
+fulldata <- merge(fulldata, Root_size, by=c("indiv","location","pop","species"))
+for(i in 1:length(fulldata$indiv)){
+fulldata$mean_rootsize[i]<-(sum(fulldata[i,20:29])/length(fulldata[,20:29]))
+}
+fulldata<-fulldata[,-c(20:29)]
+
+binlesionF<-cbind(fulldata$None.Path,100-fulldata$None.Path)
+binmycorrF<-cbind(fulldata$None.Myc,100-fulldata$None.Myc)
+binherbivoryF<-cbind(fulldata$None.Herb,100-fulldata$None.Herb)
+
+fulldata$pop<-as.factor(fulldata$pop)
+# model myc_lesion 
+mod1 <- glmmadmb(binlesionF ~ scale(None.Myc)  * scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop), data = fulldata,family = "binomial")
+summary(mod1)
+mod1.dredge <- dredge(mod1)
+
+# model myc 
+mod2 <- glmmadmb(binmycorrF ~ scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop) , data = fulldata,family = "binomial")
+summary(mod2)
+mod2.dredge <- dredge(mod2)
+```
 

### 2018-02-12 Katherine Analysis.Rmd
New clean notebook

--- 2018-02-09 MSc_Statistical_Rob_correction_-Jan29.Rmd
@@
 ---
-title: "MSc Statistical Rob correction -Jan29"
+title: "Katherine Analysis"
 output:
@@
     theme: cerulean
-    toc: yes
-  word_document:
     toc: yes
@@
   * `library(devtools)` and `install_github("vqv/ggbiplot")` package version `r packageVersion("ggbiplot")`
-  * also requires [rtools](https://cran.r-project.org/bin/windows/Rtools/)
+  * `vegan` package version `r packageVersion("vegan")`
+  * `glmmADMB` package version `r packageVersion("glmmADMB")`
+  * `car` package version `r packageVersion("car")`
+  * `factoextra` package version `r packageVersion("factoextra")`
+  * `pvclust` package version `r packageVersion("pvclust")`
 
@@
 library(factoextra)
+library(glmmADMB)
+library(car)
 ```
@@
 PlantLength.filtered <- PlantLength[!row.has.na,]# Removed all the rows with NAs
+PlantLength.filtered$Pop <- as.factor(PlantLength.filtered$Pop)
 
@@
 shapiro.test(PlantLength$Length_plant)
-
-par(mfrow = c(1,1))
-descdist(PlantLength.filtered$Length_plant, discrete = FALSE, boot = 1000)
-f1g <- fitdist(PlantLength.filtered$Length_plant, "lnorm") 
-f2g <- fitdist(PlantLength.filtered$Length_plant, "norm") 
-f3g <- fitdist(PlantLength.filtered$Length_plant, "gamma")
-f4g <- fitdist(PlantLength.filtered$Length_plant, "weibull")
-f1g$aic
-f2g$aic
-f3g$aic
-f4g$aic
 
@@
 PlantLength.filtered <- cbind(PlantLength.filtered, ((PlantLength.filtered$Length_plant^lambda)-1)/lambda)
-names(PlantLength.filtered)[5] <- "Yprime"
+names(PlantLength.filtered)[length(PlantLength.filtered)] <- "Yprime"
 mod1BC <- lm(Yprime~Location*Species, data=PlantLength.filtered)
@@
 #Make a matrix with no row or column equal to 0 (do not enclude the env variable (GM COVERAGE))
-M <- as.matrix(FloristicSurvey[1:198,4:55])
-M[is.na(M)] <- 0
-rownames(M) <- FloristicSurvey$Population
-which( colSums(M)==0 )
-which( rowSums(M)==0 )
-#Now that you know which column must be taken out, redo the matrix but with the last column, then remove the rows and columns =0
-#I did this because the previous method doesnt work with the characters in the GM_COVERAGE column.
+FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("Low", "Med_Low", "Med_High", "High"))
+table(FloristicSurvey$GM_Coverage_category)
 M <- as.matrix(FloristicSurvey[1:198,4:56])
@@
 rownames(M) <- FloristicSurvey$Population
+M<-M[-c(130,133),]
 M<-M[,-45]
-M<-M[-130,]
-M<-M[-133,]
-M<-M[-132,]
-# Now I'll make the env column a vector on its own, but the previous colde now allows it to be in the same order as the matrix im using for distances.
 GM_coverage_df <- data.frame(M[,52])
@@
 class(M) <- "numeric"
+
 # with vegdist from Bray to seroeson: add binary = T 
@@
 #The metaMDS analysis could have done the distance matrix internally but i would rather control it since i have presence/abscence
-
 meta.nmds.FloristicSurvey2D <- metaMDS(dist_FloristicSurvey, k=2, trymax = 1000)
@@
 
-# envfit for the 2D
 FloristicSurvey_envfit <- envfit(meta.nmds.FloristicSurvey2D, env = GM_coverage_df, perm = 999) #standard envfit
@@
 ```
+
 ### PCA
@@
 ```
+
 *Note that I redid this with GM_coverage_catogory and i didnt find ANY significance!
@@
 ```
+
 # Histology data Analysis
@@
 mod1.dredge <- dredge(mod1)
-
+mod1.dredgegood <- subset(mod1.dredge,mod1.dredge$delta<=7)
 # model myc 
@@
 mod2.dredge <- dredge(mod2)
+mod2.dredgegood <- subset(mod2.dredge,mod2.dredge$delta<=7)
 ```

### 2018-03-15 Colonize_Model.Rmd
Draft method for calculating correlation in root cross-sections

---
title: "Root Colonization Model"
author: "Robert I. Colautti"
date: "March 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Colonization of roots by _k_ taxa at each of _N_ root intersections can be modelled as the joint probability of _k_ Bernoulli variables. A simple example is the joint probability of mycorrhizal colonization (Cm) and pathogen colonization (Cp). The joint probabilities are:

$$ P(C_m=n_m, C_p=n_p) $$

$$= P(C_p=n_p | C_m=n_m) \cdot P(C_m=n_m)$$

$$= P(C_m=n_m | C_p=n_p) \cdot P(C_p=n_p)) $$

where n~m~ and n~p~ are 0 or 1.

Now consider the four possible outcomes:

$$A. \space Both := P(C_m = 1 , C_p = 1)$$

$$B. \space Mycorrhizae \space Only := P(C_m = 1 , C_p = 1)$$

$$C. \space Pathogens \space Only := P(C_m = 1 , C_p = 1)$$

$$D. \space Neither := P(C_m = 0, C_p = 0)$$

The variance-covariance matrix for mycorrhizae (m) and pathogens (p) species is:

$$V_m = (A + B)(1 - (A + B))$$

$$V_p = (A + C)(1 - (A + C))$$

$$Cov_{mp} = A - (A + B)(A + C)$$

The correlation coefficient between species is:

$$\frac {Cov_{mp}}{\sqrt{V_m \cdot V_p}} $$

$$= \frac {A - (A + B)(A + C)}{\sqrt {(A + B)(1 - (A + B))(A + C)(1 - (A + C))}}$$

### 2018-03-15 Corelato.R

@@ -1,0 +1,38 @@
+# This function scalculate the variances/covariance matrix or the correlation coefficient 
+# for the joint probability of two species occurring at N locations. 
+# For example, colonization by mycorrhizal fungi and pathogens at N = 100 root cross-sections
+# x is the dataset with rows representing each cross-section and the following columns:
+# ind -- the column with the labels for individuals; there should be > 1 location per individual
+# s1 -- the column of presence/absence (1:0) for the first species
+# s2 -- the column of presence/absence (1:0) for the second species
+# coef -- should be cor or cov, indicating which calculation to use. 
+# Cor returns a single value (correlation) 
+# Cov returns a vector of 3 values representing the variance of Sp1, variance of Sp2, and their covariance
+Bcor<-function(x=NA,ind=ind,s1=s1,s2=s2,coef=NA){
+  # Check if user wants covariance matrix or correlation coefficient
+  
+  # Calculate variances, covariance and correlation
+  V1<- 
+  V2<-
+  COV12<-
+  COR12<-
+    
+  if (coef == cov){
+    return(c(V1,V2,Cov))
+  }
+
+  if (coef == cor){
+    
+    return(COR)
+  }
+}
+
+# Example:
+rootdata<-data.frame(ID=c(rep("A1",100),rep("B1",100)),
+                     myc=sample(0:1,100,prob=c(0.8,0.2),replace=T),
+                     path=sample(0:1,100,prob=c(0.8,0.2),replace=T))
+head(rootdata)
+
+Bcor(rootdata,ind=ID,s1=myc,s2=path,coef=cor)
+Bcor(rootdata,ind=ID,s1=myc,s2=path,coef=cov)
+

### 2018-03-15 Corelato.R
minor change

@@ -11,6 +11,12 @@
 Bcor<-function(x=NA,ind=ind,s1=s1,s2=s2,coef=NA){
   # Check if user wants covariance matrix or correlation coefficient
   
+  # Calculate the frequency of each possible outcome
+  A<-
+  B<-
+  C<-
+  D<-
+  
   # Calculate variances, covariance and correlation
   V1<- 
   V2<-
@@ -29,10 +35,15 @@ Bcor<-function(x=NA,ind=ind,s1=s1,s2=s2,coef=NA){
 
 # Example:
 rootdata<-data.frame(ID=c(rep("A1",100),rep("B1",100)),
-                     myc=sample(0:1,100,prob=c(0.8,0.2),replace=T),
-                     path=sample(0:1,100,prob=c(0.8,0.2),replace=T))
+                     myc=sample(0:1,200,prob=c(0.8,0.2),replace=T),
+                     path=sample(0:1,200,prob=c(0.8,0.2),replace=T))
 head(rootdata)
 
-Bcor(rootdata,ind=ID,s1=myc,s2=path,coef=cor)
 Bcor(rootdata,ind=ID,s1=myc,s2=path,coef=cov)
+
+Bcor(rootdata,ind=ID,s1=myc,s2=path,coef=cor)
+
+for(i in levels(rootdata$ID)){
+  print(paste(i,round(cor(rootdata$myc[rootdata$ID==i],rootdata$path[rootdata$ID==i]),3)))
+}
 

### 2018-03-15 Katherine Analysis.Rmd

@@
 confint(mod1)
+
 ```
@@
 # you might have to bin covers because it only works with categorical, so 0-5% none, 6-40 low etc.
-FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("None", "Med_Low", "Med_High", "Overtaken"))
+FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("None to Low","Medium", "High", "Overtaken"))
 table(FloristicSurvey$GM_Coverage_category)
 # [0-20] None
-# ]20-50] Medium low
-# ]50-80] Medium high
+# ]20-40] low
+# ]40-60] Medium 
+# ]60-80] high
 # ]80-100] Overtaken
@@
 # Plot results
-ggplot(data=FloristicSurveyLDAval,aes(x=LD1,y=LD2,group=FloristicSurveysmall$GM_Coverage_category))+
+LDA_of_Floristic_Composition<-ggplot(data=FloristicSurveyLDAval,aes(x=LD1,y=LD2,group=FloristicSurveysmall$GM_Coverage_category))+
   stat_ellipse(geom="polygon",aes(colour=FloristicSurveysmall$GM_Coverage_category),fill=NA,size=1.2,alpha=0.3)+
@@
   geom_point(aes(shape=FloristicSurveysmall$GM_Coverage_category,fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=I(4),alpha=I(0.8))+
-  xlab("LD Axis 1")+ylab("LD Axis 2")+theme_simple() +
-  theme(legend.title=element_blank())
+  xlab("LD Axis 1")+ylab("LD Axis 2")+
+  ggtitle("LDA of Floristic Composition \n in a Garlic Mustard Population")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_color_manual(values=c("green3"," blue3","orange3","red3"))+ scale_fill_manual(values=c("green3","blue3","orange3","red3"))
+ggsave(file="LDA_of_Floristic_Composition.epx", plot=LDA_of_Floristic_Composition, width=10, height=8)
 
@@
 par(mfrow=c(3,2))
-plot(fit,cex=0.4,main="Clustering with populations")
+plot(fit,cex=0.4,main="Clustering with coverage")
 plot(cut(fitd, h=10)$upper, main="Upper tree of cut at h=10")
@@
 #Make a matrix with no row or column equal to 0 (do not enclude the env variable (GM COVERAGE))
-FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("Low", "Med_Low", "Med_High", "High"))
+FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("None to Low","Medium", "High", "Overtaken"))
 table(FloristicSurvey$GM_Coverage_category)
@@
 dist_FloristicSurvey <- vegdist(M, method = "bray", binary = T)
-#The metaMDS analysis could have done the distance matrix internally but i would rather control it since i have presence/abscence
 meta.nmds.FloristicSurvey2D <- metaMDS(dist_FloristicSurvey, k=2, trymax = 1000)
@@
     coord_cartesian(xlim = c(-1,1.5))+
-  theme_simple()+ guides(color=guide_legend("Garlic Mustard Coverage"))
+  theme_simple()+ guides(color=guide_legend("Garlic Mustard Coverage"))+
+  ggtitle("LDA of Floristic Composition \n in a Garlic Mustard Population")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_color_manual(values=c("green3"," blue3","orange3","red3"))+ scale_fill_manual(values=c("green3","blue3","orange3","red3"))
+ggsave(file="LDA_of_Floristic_Composition.epx", plot=LDA_of_Floristic_Composition, width=10, height=8)
 ```
@@
 ```{r}
-FloristicSurvey<-FloristicSurvey[,-56]
-FloristicSurvey.pca <- prcomp(FloristicSurvey[,4:(ncol(FloristicSurvey))],center = TRUE) 
+FloristicSurvey.pca <- prcomp(FloristicSurvey[,4:(ncol(FloristicSurvey)-1)],center = TRUE) 
 summary(FloristicSurvey.pca)
-fviz_eig(FloristicSurvey.pca,addlabels=TRUE,hjust = -0.3)+theme_simple()
-
+factoextra::fviz_eig(FloristicSurvey.pca,addlabels=TRUE,hjust = -0.3)+theme_simple()
+library(ggfortify)
+autoplot(FloristicSurvey.pca, data = FloristicSurvey, colour = "GM_Coverage_category", label.size = 3)+theme_simple()
 round(FloristicSurvey.pca$sdev^2/sum(FloristicSurvey.pca$sdev^2)*100,2)
@@
 ```
+
 ### Modeling (redundancy analysis)
@@
 var$Population <- as.factor(var$Population)
+var$GM_Coverage<-as.numeric(var$GM_Coverage)
+sp.comp<-as.matrix(sp.comp)
 

### 2018-03-19 CleanModels.Rmd
Commit work

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    highlight: tango
    theme: cerulean
    toc: yes
---

#Housekeeping

##Load packages

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)
library(mefa)
library(ggbiplot)
library(pvclust)
library(vegan)
library(ggbiplot)
library(factoextra)
library(glmmADMB)
library(car)
library(effects)
library(coefplot2)
library(bbmle)
library(gridExtra)
library(corrplot)
library(ade4)
library(lmtest)
```

##Load costum functions

```{r costum functions}
residfit <- function (model, col="black") {
  f<-fitted(model)
  r<-resid(model, type='pearson')
  plot(f, r, col=col, main='Residuals vs. Fitted')
  L1<-loess(r~f)
  fvec = seq(min(f),max(f),length.out=1000)
  lines(fvec,predict(L1,fvec),col='red')
}

#do the same for the Scale-Location plot
scaleloc <- function(model,col="black") {
  f <- fitted(model)
  r <- sqrt(abs(residuals(model, type='pearson'))) #transformed pearson residuals
  plot(f,r,col=col, main='Scale-Location Plot') 
  L1 <- loess(r~f)
  fvec = seq(min(f),max(f),length.out=1000)
  lines(fvec,predict(L1,fvec),col=2)
}
```

##Load data

### Load/ Modify data: Co-occurence

```{r Introduce co-occurence dataset, message=FALSE, warning=FALSE, echo=FALSE}
mdata <- read.csv("CSV/Assessing_Oct_20.csv",stringsAsFactors=F)
indiv <- mdata$CODE[!mdata$CODE==""]
tdata <- mdata[grep("[0-9]+",mdata$Cross),]
nrow(tdata)/length(indiv)

# This is not the same because some individuals just had the totals not the cooccurence data
## THE COMMENT IS NOT CLEAR, EXPLAIN...
indiv2 <- tdata$CODE[!tdata$CODE==""]
nrow(tdata)/length(indiv2)
indiv2 <- data.frame(indiv2)
indiv2 <- mefa:::rep.data.frame(indiv2,each=100)
fdata <- cbind(indiv2,tdata)
fdata <- fdata[,-c(2,3,4,9,14,17,18)]

# Cleaning up the occurence data
## CLEANING UP HOW?
fdata[is.na(fdata)] <- 0
fdata$Lesion<-rowSums(fdata[,2:4])
fdata[fdata$Lesion>1,]
fdata$Mycorrhiza<-rowSums(fdata[,6:8])
fdata[fdata$Mycorrhiza>1,]
fdata <- fdata[,-c(2:4,6:8)]

#### Checking data for problems ####

summary(fdata)
fdata$None.Path <- as.integer(fdata$None.Path)
fdata$None.Myc <- as.integer(fdata$None.Myc)
fdata[is.na(fdata)] <- 0

sherb <- fdata$Herbivory+fdata$None.Herb
fdata[sherb!=1,]
fdata[sherb!=1,"None.Herb"]<-1

# Are all the sums equal to 100 for herb? 
dframeHerb <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeHerb[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeHerb$counter[c] <- c
  dframeHerb$Indiv2[c] <- i
  dframeHerb$Sum[c] <- sum(subdata[,"Herbivory"]+subdata[,"None.Herb"])
  subdata <- NA
  c <- c + 1
}
dframeHerb[dframeHerb$Sum!=100,]

# Are all the sums equal to 100 for Mycorrhiza? 
dframeMyc <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeMyc[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeMyc$counter[c] <- c
  dframeMyc$Indiv2[c] <- i
  dframeMyc$Sum[c] <- sum(subdata[,"Mycorrhiza"]+subdata[,"None.Myc"])
  subdata <- NA
  c <- c + 1
}
dframeMyc[dframeMyc$Sum!=100,]

# Are all the sums equal to 100 for Lesions? 
dframeLesion <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeLesion[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeLesion$counter[c] <- c
  dframeLesion$Indiv2[c] <- i
  dframeLesion$Sum[c] <- sum(subdata[,"Lesion"]+subdata[,"None.Path"])
  subdata <- NA
  c <- c + 1
}
dframeLesion[dframeLesion$Sum!=100,]

# Separating "Individual" into: pop,location,species columns 
fdata$pop <- gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",fdata$indiv)
fdata$location <- gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",fdata$indiv)
fdata$species <- sub("^[0-9]+[I,O]([A-Z]+).*","\\1",fdata$indiv)
fdata$location <- as.factor(fdata$location)
fdata$species <- as.factor(fdata$species)
fdata$pop <- as.factor(fdata$pop)
fdata$indiv2 <- as.character(fdata$indiv2)
summary(fdata)
fdata %>% drop_na()->fdata

fdata$None.Myc <- as.factor(fdata$None.Myc)
fdata$Herbivory <- as.factor(fdata$Herbivory)
fdata$Mycorrhiza <- as.factor(fdata$Mycorrhiza)
fdata$Lesion <- as.factor(fdata$Lesion)
fdata$None.Herb <- as.factor(fdata$None.Herb)
fdata$None.Path <- as.factor(fdata$None.Path)
summary(fdata)
```

### Load/ Modify data: Totals

```{r Introduce total dataset, message=FALSE, warning=FALSE, echo=FALSE}
mdata<-read.csv("CSV/Assessing_Oct_20.csv",stringsAsFactors=F)
indiv<-mdata$CODE[!mdata$CODE==""]
tdata<-mdata[mdata$Slide=="TOTAL",]
length(indiv)
nrow(tdata)

ndata<-cbind(indiv,tdata)
ndata<-ndata[,-c(2,3,4,9,14,17:37)]
ndata$None.Path<-as.integer(ndata$None.Path)
ndata$Lesions<-as.integer(100-ndata$None.Path)
ndata$None.Myc<-as.integer(ndata$None.Myc)
ndata$Mycorrhiza<-as.integer(100-ndata$None.Myc)

# Checking data for problems
(problemsPath<-ndata[!rowSums(ndata[,c(2:5)])==100,])
(problemsHyph<-ndata[!rowSums(ndata[,c(6:9)])==100,])
(problemsHerb<-ndata[!rowSums(ndata[,c(10:11)])==100,])

# Separating "Individual" into: pop,location,species columns 
ndata$pop<-gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",ndata$indiv)
ndata$location<-gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",ndata$indiv)
ndata$species<-gsub("^[0-9]+[I,O]([A-Z]+).*","\\1",ndata$indiv)
ndata$location<-as.factor(ndata$location)
ndata$species<-as.factor(ndata$species)
ndata$pop<-as.factor(ndata$pop)

#### Totalling the scores####
binlesion<-cbind(ndata$None.Path,100-ndata$None.Path)
binmycorr<-cbind(ndata$None.Myc,100-ndata$None.Myc)
binherbivory<-cbind(ndata$None.Herb,100-ndata$None.Herb)
summary(ndata)
```

### Field survey data

```{r load field data}
FloristicSurvey <-read.csv("CSV/May_2017_FloristicSurvey_summer2016.csv", sep="\t")
PlantLength <- read.csv("CSV/May_2017_PlantLength_summer2016.csv", sep="\t")
Soil_characteristics <- read.csv("CSV/Soil_characteristics.txt", sep="\t")

#Restructuring
head(PlantLength)
str(PlantLength)
colnames(PlantLength)[1] <- "Population"
PlantLength$Population<-as.factor(PlantLength$Population)
PlantLength$Location<-as.factor(PlantLength$Location)

FloristicSurvey$Population<-as.factor(FloristicSurvey$Population) # Make the population a factor and not an interger
FloristicSurvey[is.na(FloristicSurvey)] <- 0
sum(row.has.na <- apply(FloristicSurvey, 1, function(x){any(is.na(x))}))
```

### Root size

```{r load root size data}
Root_size <-read.csv("CSV/Root_size.csv")
Root_size$pop<-gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",Root_size$indiv)
Root_size$location<-gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",Root_size$indiv)
Root_size$species<-gsub("^[0-9]+[I,O]([A-Z]+).*","\\1",Root_size$indiv)
Root_size$location<-as.factor(Root_size$location)
Root_size$species<-as.factor(Root_size$species)
Root_size$pop<-as.factor(Root_size$pop)
```

###Make a full dataset

```{r full data set}
Soil_characteristics$Location<-as.character(Soil_characteristics$Location)
for(i in 1:length(Soil_characteristics$Location))if(Soil_characteristics[i,2]=="in"){
   Soil_characteristics[i,2]<-"I"
}else{
  Soil_characteristics[i,2]<-"O"
}
Soil_characteristics$Location<-as.factor(Soil_characteristics$Location)  
names(Soil_characteristics)[1:2]<-c("pop","location")

fulldata <- merge(Soil_characteristics, ndata, by=c("pop","location"))
names(Root_size)[1]<-"indiv"
fulldata <- merge(fulldata, Root_size, by=c("indiv","location","pop","species"))
for(i in 1:length(fulldata$indiv)){
fulldata$mean_rootsize[i]<-(sum(fulldata[i,20:29])/length(fulldata[,20:29]))
}
fulldata<-fulldata[,-c(20:29)]

binlesionF<-cbind(fulldata$None.Path,100-fulldata$None.Path)
binmycorrF<-cbind(fulldata$None.Myc,100-fulldata$None.Myc)
binherbivoryF<-cbind(fulldata$None.Herb,100-fulldata$None.Herb)

fulldata$pop<-as.factor(fulldata$pop)
fulldata$Mycorrhiza<-100-fulldata$None.Myc
fulldata$Lesion<-100-fulldata$None.Path
```

#Variable descriptions

###Co-occurence

  * **indiv2:** The unique code given to a sample. In this dataset the unique sample code repeats 100 times for each cross where an observation was taken on the root sample.

  * **None.Path:** A binary representation of whether a sign of pathogen activity was recorded (0) or not (1).

  * **Lesion:** The counterpart to the previous variable (None.Path). A binary representation of whether a sign of pathogen activity was recorded (1) or not (0).

  * **None.Myc:** A binary representation of whether a sign of myccorhizal activity was recorded (0) or not (1).

  * **Mycorrhiza:** The counterpart to the previous variable (None.Myc). A binary representation of whether a sign of mycorrhizal activity was recorded (1) or not (0).

  * **None.Herb:** A binary representation of whether herbivory was recorded (0) or not (1).

  * **Herbivory:** The counterpart to the previous variable (None.Herb). A binary representation of whether Herbivoryn was recorded (1) or not (0).

  * **Population (pop):** The coding number representing the population at which the sample was collected.

  * **location:** A code representing the whether the sample was collected inside a Alliaria petiolata population (I) or whther it was collected at least 7 m outside of he furthest individual in the A. petiolata population (O).

  * **species:** The particular species to which the sample belongs.

  * **Cross:** The particular cross number where the data was recorded on the individual sample.

###Total scores

  * **indiv:** The unique code given to a sample.

  * **Decay:** The total number of crosses where decay was recorded an individual sample when doing a total of 100 crosses/ sample.

  * **Pathogen:** The total number of crosses where pathogen was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **Hyphae:** The total number of crosses where non-myccorhizal hyphae was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **None.Path:** The total number of crosses where no signs of pathogen activities were recorded on an individual sample when doing a total of 100 crosses/ sample. Note that the total of Decay, Pathogen, Hyphae, and None.Path must come to 100 per individual to account for all 100 crosses.

  * **Arbuscule:** The total number of crosses where an arbuscule was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **Vesicules:** The total number of crosses where a vesicule was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **M_Hyphae:** The total number of crosses where myccorhizal hyphae was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **None.Myc:** The total number of crosses where no signs of mycorrhizal activities were recorded on an individual sample when doing a total of 100 crosses/ sample. Note that the total of Arbuscules, Vesicules, M_Hyphae, and None.Myc must come to 100 per individual to account for all 100 crosses.

  * **Herbivory:** The total number of crosses where herbivory was recorded on an individual sample when doing a total of 100 crosses/ sample.

  * **None.Herb:** The total number of crosses where no signs of herbivory was recorded on an individual sample when doing a total of 100 crosses/ sample. Note that the total of Herbivory, and None.Herb must come to 100 per individual to account for all 100 crosses.

  * **Population (pop):** The coding number representing the population at which the sample was collected.

  * **location:** A code representing the whether the sample was collected inside a Alliaria petiolata population (I) or whther it was collected at least 7 m outside of he furthest individual in the A. petiolata population (O).

  * **species:** The particular species to which the sample belongs.

###Floristic Survey

###Soil Characteristics

###Root size

#Soil abiotic qualities and location

### Model selection

```{r model fittin soil}
var<-Soil_characteristics[,c(1,2)]
Y<-Soil_characteristics[,-c(1,2,5)]
var$pop<-as.factor(var$pop)
Location<-as.factor(var$location)
Y$Sample <-paste(var$pop,var$location) 
rownames(Y)<-Y$Sample
Y$Sample<-NULL

covar_cor = cor(Y)
corrplot.mixed(covar_cor, upper = "ellipse", lower = "number")
Nutrient_PCA = dudi.pca(df = Y[, c(3, 4)], scannf = FALSE, nf = 1)
Nutrient_PCA$co
Nutrient_PCA$eig/sum(Nutrient_PCA$eig)
Soil_characteristics$Nutrient_PC1 = Nutrient_PCA$li[,1]

dat<-data.frame(c(1:20))
dat[1]<-Soil_characteristics$location
colnames(dat)[1]<-"Location"
dat$Agg_stability.s<-scale(Soil_characteristics$Agg_stability)
dat$pH.s<-scale(Soil_characteristics$pH)
dat$Nutrient_PC1.s<-scale(Soil_characteristics$Nutrient_PC1)

GLM_soil <- glm(Location~Agg_stability.s*pH.s*Nutrient_PC1.s,
                    family=binomial(link='logit'),
                    data=dat)
```

###LRT

```{r LRT soil}
GLM_soil2 <- glm(Location~Agg_stability.s+pH.s+Nutrient_PC1.s+
                   Agg_stability.s:pH.s + Agg_stability.s:Nutrient_PC1.s+
                   Nutrient_PC1.s:pH.s,
                family=binomial(link='logit'),
                data=dat)
anova(GLM_soil,GLM_soil2)

GLM_soil3 <- glm(Location~Agg_stability.s+pH.s+Nutrient_PC1.s+
                   Agg_stability.s:pH.s + Agg_stability.s:Nutrient_PC1.s,
                 family=binomial(link='logit'),
                 data=dat)
anova(GLM_soil2,GLM_soil3)

GLM_soil4 <- glm(Location~Agg_stability.s+pH.s+Nutrient_PC1.s+
                   Agg_stability.s:pH.s,
                 family=binomial(link='logit'),
                 data=dat)
anova(GLM_soil3,GLM_soil4)

GLM_soil5 <- glm(Location~Agg_stability.s+pH.s+Nutrient_PC1.s,
                 family=binomial(link='logit'),
                 data=dat)
anova(GLM_soil4,GLM_soil5)

GLM_soil6 <- glm(Location~Agg_stability.s+pH.s,
                 family=binomial(link='logit'),
                 data=dat)
anova(GLM_soil5,GLM_soil6)

GLM_soil7 <- glm(Location~Agg_stability.s,
                 family=binomial(link='logit'),
                 data=dat)
anova(GLM_soil6,GLM_soil7)

GLM_soil8 <- glm(Location~1,
                 family=binomial(link='logit'),
                 data=dat)
anova(GLM_soil7,GLM_soil8)
```

###descriptive stats

```{r descriptive stats soil}
summary(GLM_soil)
confint(GLM_soil)

pr<-resid(GLM_soil, type='pearson')
n<-nrow(Soil_characteristics)
c<-length(coef(GLM_soil))
(Disp<-sum(pr^2)/(n-c))
```

#Garlic mustard on Mycorrhiza

###Model selection

```{r Model fit mycGM gauss}
hist(ndata$Lesions)
# In vs Out
ggplot(data=ndata,aes(x=location))+geom_histogram(stat="count")+facet_wrap(~pop)
ggplot(data=ndata,aes(x=location))+geom_histogram(stat="count")+facet_wrap(~species)
# Each Species
ggplot(data=ndata,aes(x=species))+geom_histogram(stat="count")+facet_wrap(~pop)
# Each Population
ggplot(data=ndata,aes(x=pop))+geom_histogram(stat="count")

ndata$Prop_Lesions<- ndata$Lesions/(ndata$Lesions+ndata$None.Path)
hist(ndata$Prop_Lesions)
shapiro.test(log(ndata$Prop_Lesions))
mod1.gauss<-lmer(Prop_Lesions~ species + location + species:location +
                       (1|pop),
                     data=ndata) 
mod1.gauss<-lm(Prop_Lesions~ species + location + species:location,data=ndata)
bc<-boxcox(mod1.gauss, lambda = seq(-2, 2, 0.1))
lambda <- bc$x[which.max(bc$y)]
ndata <- cbind(ndata, ((ndata$Prop_Lesions^lambda)-1)/lambda)
names(ndata)[length(ndata)] <- "Yprime"
shapiro.test(ndata$Yprime)
hist(ndata$Yprime)
scaleloc(mod1.gauss)
residfit(mod1.gauss)

mod1.gaussY<-glmmadmb(Yprime~ species + location + species:location +
                       (1|pop),
                     data=ndata, family="gaussian")
qqPlot(ndata$Yprime)

cooksd <- cooks.distance(mod1.gauss)
names(cooksd) <- 1:length(cooksd)
plot(cooksd, pch="*", cex=2, main="Influential Obs by Cooks distance")  # plot cook's distance
abline(h = 4*mean(cooksd, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>4*mean(cooksd, na.rm=T),names(cooksd),""), col="red")

ndataRM<-ndata[-c(66,73,97,130,133,135,136,176,172,185,204),]
qqPlot(ndataRM$Yprime)
shapiro.test(ndataRM$Yprime)

mod1.gaussYRM<-glmmadmb(Yprime~ species + location + species:location +
                       (1|pop),
                     data=ndataRM, family="gaussian")

bptest(mod1.gaussYRM)
hist(ndataRM$Yprime)
mod1.gaussYRM<-lmer(Yprime~ species + location + species:location +
                       (1|pop),
                     data=ndataRM)
scaleloc(mod1.gaussYRM)
residfit(mod1.gaussYRM)

ICtab(mod1.gaussY,mod1.poisson,mod1.nb,mod1.gaussYRM)
```
```{r Model fit mycGM beta}
descdist(ndata$Prop_Lesions,boot=1000)
summary(ndata$Prop_Lesions)
plot(density(ndata$Prop_Lesions))
mu <- mean(ndata$Prop_Lesions)
var <- var(ndata$Prop_Lesions)
estBetaParams <- function(mu, var) {
  alpha <- ((1 - mu) / var - 1 / mu) * mu ^ 2
  beta <- alpha * (1 / mu - 1)
  return(params = list(alpha = alpha, beta = beta))
}
estBetaParams(mu, var)

mod1.beta<-glmmTMB(Prop_Lesions~ species + location + species:location +
                       (1|pop), ziformula=,
                     data=ndata, family=list(family="beta",link="logit"))

```

```{r Model fit mycGM binom}
mod1.binom<-glmmadmb(binmycorr ~ species + location + species:location +
                       (1|pop),
                     data=ndata, family="binomial")

pr<-resid(mod1.binom, type='pearson')
(phimod1.binom <- sum(pr^2)/df.residual(mod1.binom))

scaleloc(mod1.binom)
residfit(mod1.binom)

```

```{r Model fit mycGM poisson}
mod1.poisson <-glmmadmb(Mycorrhiza ~ species + location + species:location +
                         (1|pop),
                       data=ndata, family="poisson")

pr<-resid(mod1.poisson, type='pearson')
(phi <- sum(pr^2)/df.residual(mod1.poisson))

scaleloc(mod1.poisson)
residfit(mod1.poisson)

ChiCrit<-qchisq(0.95, df.residual(mod1.poisson))
deviance(mod1.poisson)
ChiSq<-sum(pr^2)

ChiCrit>=ChiSq
```

```{r Model fit mycGM negBinom}
# http://data.princeton.edu/wws509/r/overdispersion.html

mod1.nb<-glmmadmb(Mycorrhiza ~ species + location + species:location +
                    (1|pop),
                  data=ndata,family="nbinom1")

-2*(logLik(mod1.poisson)-logLik(mod1.nb))

scaleloc(mod1.nb)
residfit(mod1.nb)

pr<-resid(mod1.nb, type='pearson')
ChiSq<-sum(pr^2)
ChiCrit>=ChiSq #still too big but much smaller...

mod1.nb1<-glmer.nb(Mycorrhiza ~ species + location + species:location +
                    (1|pop),
                  data=ndata, control=glmerControl(optimizer="bobyqa")) 
theta<-getME(mod1.nb1, "glmer.nb.theta")

xb <- predict(mod1.poisson)
g <- cut(xb, breaks=quantile(xb,seq(0,100,5)/100))
m <- tapply(ndata$Mycorrhiza, g, mean)
v <- tapply(ndata$Mycorrhiza, g, var)

plot(m, v, xlab="Mean", ylab="Variance",main="Mean-Variance Relationship")
x <- seq(42.16667,83.77778,0.3)
lines(x, x*phi, lty="dashed")
lines(x, x*(1+x/theta))

```

###LRT

```{r LRT mycGM}
mod1.1<-glmmadmb(Mycorrhiza ~ species + location + 
                    (1|pop),
                  data=ndata, family="nbinom1") 
# species:location?
anova(mod1.1, mod1.nb) #discard

mod1.2<-glmmadmb(Mycorrhiza ~ species + 
                    (1|pop),
                  data=ndata, family="nbinom1") 
# location?
anova(mod1.2, mod1.1) #discard????

mod1.3<-glmmadmb(Mycorrhiza ~ location + 
                    (1|pop),
                  data=ndata, family="nbinom1")

mod1.4<-glmmadmb(Mycorrhiza ~ 1 + 
                    (1|pop),
                  data=ndata, family="nbinom1")

anova(mod1.4 , mod1.3)
anova(mod1.4 , mod1.2)

options(na.action = "na.fail")
dredge(mod1.nb)
```

###Descriptive stats

```{r descriptive stats mycGM}
pr<-resid(mod1.1, type='pearson')
n<-nrow(ndata)
c<-length(coef(mod1.1))
(Disp<-sum(pr^2)/(n-c))

summary(mod1.1)
confint(mod1.1)

# no efffect on colonization... maybe the plantswere there before GM?
coefplot2(mod1.1)
```

#Garlic mustard on Lesion

###Model selection

```{r model sel lesionGM}
hist(ndata$Lesions)

mod2.binom<-glmmadmb(binlesion ~ species + location + species:location +
                       (1|pop),
                     data=ndata, family="binomial")

pr<-resid(mod2.binom, type='pearson')
n<-nrow(ndata)
c<-length(coef(mod2.binom))
(Dispmod2.binom<-sum(pr^2)/(n-c))
scaleloc(mod2.binom)
residfit(mod2.binom)

mod2.binom.ind<-glmmadmb(binlesion ~ species + location + species:location +
                       (1|pop)+ (1|indiv),
                     data=ndata, family="binomial")

pr<-resid(mod2.binom.ind, type='pearson')
n<-nrow(ndata)
c<-length(coef(mod2.binom.ind))
(Dispmod2.binom.ind<-sum(pr^2)/(n-c))
scaleloc(mod2.binom.ind)
residfit(mod2.binom.ind)

mod2.binom.sp<-glmmadmb(binlesion ~ species + location + species:location +
                 (1|pop) + (species|pop),
               data=ndata, family="binomial")

pr<-resid(mod2.binom.sp, type='pearson')
n<-nrow(ndata)
c<-length(coef(mod2.binom.sp))
(Disp.sp<-sum(pr^2)/(n-c))
scaleloc(mod2.binom.sp)
residfit(mod2.binom.sp)

mod2.poisson<-glmmadmb(Lesions ~ species + location + species:location +
                    (1|pop),
                  data=ndata, family="poisson")

pr<-resid(mod2.poisson, type='pearson')
n<-nrow(ndata)
c<-length(coef(mod2.poisson))
(Dispmod2.poisson<-sum(pr^2)/(n-c))
scaleloc(mod2.poisson)
residfit(mod2.poisson)

mod2.nb.sp<-glmmadmb(Lesions ~ species + location + species:location +
                  (species|pop) + (1|pop),
                  data=ndata, family="nbinom1")

pr<-resid(mod2.nb.sp, type='pearson')
n<-nrow(ndata)
c<-length(coef(mod2.nb.sp))
(Dispmod1.nb.sp<-sum(pr^2)/(n-c))
scaleloc(mod2.nb.sp)
residfit(mod2.nb.sp)

mod2.nb<-glmmadmb(Lesions ~ species + location + species:location +
                    (1|pop),
                  data=ndata, family="nbinom1")

pr<-resid(mod2.nb, type='pearson')
n<-nrow(ndata)
c<-length(coef(mod2.nb))
(Dispmod2.nb<-sum(pr^2)/(n-c))
scaleloc(mod2.nb)
residfit(mod2.nb)

ICtab(mod2.poisson,mod2.binom,mod2.binom.sp,mod2.nb.sp,mod2.nb)
```

###LRT

```{r LRT lesionGM}
mod2.1<-glmmadmb(Lesions ~ species + location +
                    (1|pop),
                  data=ndata, family="nbinom1") 
anova(mod2.1, mod2.nb)

mod2.2<-glmmadmb(Lesions ~ species +
                    (1|pop),
                  data=ndata, family="nbinom1")

mod2.3<-glmmadmb(Lesions ~ location +
                    (1|pop),
                  data=ndata, family="nbinom1")

mod2.4<-glmmadmb(Lesions ~ 1 +
                    (1|pop),
                  data=ndata, family="nbinom1") 
anova(mod2.4 , mod2.2)
anova(mod2.4 , mod2.3)

dredge( mod2.nb)
```

###Descriptive stats

```{r descriptive stats lesionGM}
pr<-resid(mod2.nb, type='pearson')
n<-nrow(ndata)
c<-length(coef(mod2.nb))
(Disp<-sum(pr^2)/(n-c))

summary(mod2.nb)
confint(mod2.nb)

coefplot2(mod2.nb)
```

# Myc and lesion Correlation Model

*NOTE: Yprime = corr coefficient of Myc and Lesion at every cross per indiv*

###Model selection

```{r}
# calculating the r
Root_size$mean_rootsize <- rowSums(Root_size[,2:11])/length(Root_size[,2:11])
names(Root_size)[1]<-"indiv2"

fdata_rs <- merge(fdata, Root_size, by=c("indiv2","location","pop","species"))
indivCODE <- as.character(unique(fdata_rs$indiv2))
dfcorr <-data.frame(indiv2=c(0),r=c(0))
for (i in 1:length(indivCODE)){
  dat1<-NULL
  dat1<-fdata_rs[fdata_rs$indiv2==indivCODE[i],]
  dfcorr[i,1] <- indivCODE[i]
  dfcorr[i,2] <- cor(as.numeric(dat1$Mycorrhiza),as.numeric(dat1$Lesion))
}
dfcorr %>% drop_na()->dfcorr

fdata_rs.corr <- merge(dfcorr, Root_size, by="indiv2")
shapiro.test(fdata_rs.corr$r)

fdata_rs.corr$r.t<-fdata_rs.corr$r+1
CorrLM<-lm(r.t~ species * location * mean_rootsize,data=fdata_rs.corr)

bc<-boxcox(CorrLM, lambda = seq(-2, 2, 0.1))
lambda <- bc$x[which.max(bc$y)]
fdata_rs.corr <- cbind(fdata_rs.corr, ((fdata_rs.corr$r.t^lambda)-1)/lambda)
names(fdata_rs.corr)[length(fdata_rs.corr)] <- "Yprime"
shapiro.test(fdata_rs.corr$Yprime)
hist(fdata_rs.corr$Yprime)

CorrLMERBC<-lmer(Yprime~ species + location + mean_rootsize + 
                   location:species +
                   (1|pop),
                 data=fdata_rs.corr)
pr<-resid(CorrLMERBC, type='pearson')
n<-nrow(fdata_rs.corr)
c<-length(coef(CorrLMERBC))
(Disp<-sum(pr^2)/(n-c))

plot(effect("location:mean_rootsize", CorrLMERBC))
plot(effect("mean_rootsize", CorrLMERBC))
```

####LRT

```{r LRT corrmod}
CorrLMERBC<-lmer(Yprime~ species + location + mean_rootsize + 
                   location:species +
                   (1|pop),
                 data=fdata_rs.corr)

CorrLMERBC1<-lmer(Yprime~ species + location + mean_rootsize+
                   (1|pop),
                 data=fdata_rs.corr)
anova(CorrLMERBC1, CorrLMERBC)

CorrLMERBC2<-lmer(Yprime~ species + location + 
                   (1|pop),
                 data=fdata_rs.corr)
anova(CorrLMERBC2, CorrLMERBC1)

CorrLMERBC3<-lmer(Yprime~ species +  
                    (1|pop),
                  data=fdata_rs.corr)
anova(CorrLMERBC3, CorrLMERBC2)

CorrLMERBC4<-lmer(Yprime~ 1+ 
                    (1|pop),
                  data=fdata_rs.corr)
anova(CorrLMERBC3, CorrLMERBC4)
```

###Descriptive stats

```{r descriptive stats cormod}
pr<-resid(CorrLMERBC, type='pearson')
n<-nrow(fdata_rs.corr)
c<-length(coef(CorrLMERBC))
(Disp<-sum(pr^2)/(n-c))

summary(CorrLMERBC)
confint(CorrLMERBC)
```

#Everything on lesion

###Model selection

```{r model selection fullmod}
var<-fulldata[,c(5,6,8,9,22,23,24)]
covar_cor = cor(var)
corrplot.mixed(covar_cor, upper = "ellipse", lower = "number")
Nutrient_PCA = dudi.pca(df = var[, c(3, 4)], scannf = FALSE, nf = 1)
Nutrient_PCA$co
Nutrient_PCA$eig/sum(Nutrient_PCA$eig)
fulldata$Nutrient_PC1 = Nutrient_PCA$li[,1]

mod10.nbinom <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "nbinom1")
mod10.nbinom.ind <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+(1 | indiv)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "nbinom1")

# mod10.poisson <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      # scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      # (1 | pop)+
                      # Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      # Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      # Mycorrhiza:scale(Agg_stability), 
                    # data = fulldata,family = "poisson") 
#fails
mod10.poisson.ind <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+(1 | indiv)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "poisson")

mod10.binom <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "binomial")
# mod10.binom.ind <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      # scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      # (1 | pop) + (1 | indiv)+
                      # Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      # Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      # Mycorrhiza:scale(Agg_stability), 
                    # data = fulldata,family = "binomial") 
#fail

ICtab(mod10.binom, mod10.poisson.ind, mod10.nbinom, mod10.nbinom.ind)
```

###LRT

*cant include location because when pop is a random factor locatin is correlated with all the other measurements! They were taken "in" and "out".*

```{r LRT fullmodel}
mod10.binom <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "binomial")

mod10.1 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH), 
                    data = fulldata,family = "binomial")
# Mycorrhiza:scale(Agg_stability)? 
anova(mod10.1, mod10.binom) # important

mod10.2 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species , 
                    data = fulldata,family = "binomial")
# Mycorrhiza:scale(pH)? 
anova(mod10.2, mod10.1) # important

mod10.3 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:scale(pH), 
                    data = fulldata,family = "binomial")
# Mycorrhiza:species? 
anova(mod10.3, mod10.1) # important

mod10.4 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1+
                      Mycorrhiza:species + Mycorrhiza:scale(pH), 
                    data = fulldata,family = "binomial")
# Mycorrhiza:scale(mean_rootsize)?
anova(mod10.4,mod10.1) #keep

mod10.1 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH), 
                    data = fulldata,family = "binomial")
# Mycorrhiza:Nutrient_PC1?
anova(mod10.3,mod10.4) #keep nutrient myc interaction

mod10.5 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH)+ scale(Agg_stability) + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "binomial")
# Nutrient_PC1?
anova(mod10.5, mod10.binom) #important

mod10.6 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      scale(pH) + Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "binomial")
# scale(Agg_stability)?
anova(mod10.6 ,mod10.binom) #NOPE

mod10.7 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
                      Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "binomial")
# scale(pH)?
anova(mod10.7,mod10.6) #NOPE

mod10.8 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) +
                      Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "binomial")
# Species?
anova(mod10.7,mod10.8) #keep

mod10.9 <- glmmadmb(binlesionF ~ Mycorrhiza + species + 
                      Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "binomial")
# scale(mean_rootsize)?
anova(mod10.9,mod10.7) #Keep

mod10.10 <- glmmadmb(binlesionF ~ scale(mean_rootsize) + species + 
                      Nutrient_PC1 + 
                      (1 | pop)+
                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
                      Mycorrhiza:scale(Agg_stability), 
                    data = fulldata,family = "binomial")

# Mycorrhiza?
anova(mod10.10,mod10.7) #keep
```

###Descriptive stats

```{r desctiptive stats fullmod}
pr<-resid(mod10.3, type='pearson')
n<-nrow(fulldata)
c<-length(coef(mod10.3))
(Disp<-sum(pr^2)/(n-c))

summary(mod10.7)
confint(mod10.7)
coefplot2(mod10.7)
```

### 2018-03-19 Katherine Analysis.Rmd
Commit work

@@
   * `pvclust` package version `r packageVersion("pvclust")`
+  * `effects` package version `r packageVersion("effects")`
+  * `coefplot2` package version `r packageVersion("coefplot2")`
+  * `bbmle` package version `r packageVersion("bbmle")`
+  * `gridExtra` package version `r packageVersion("gridExtra")`
 
@@
 library(car)
+library(effects)
+library(coefplot2)
+library(bbmle)
+library(gridExtra)
+library(corrplot)
+library(ade4)
 ```
@@
 }
+
+grid_arrange_shared_legend <-
+  function(...,
+           ncol = length(list(...)),
+           nrow = 1,
+           position = c("bottom", "right")) {
+
+    plots <- list(...)
+    position <- match.arg(position)
+    g <-
+      ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
+    legend <- g[[which(sapply(g, function(x)
+      x$name) == "guide-box")]]
+    lheight <- sum(legend$height)
+    lwidth <- sum(legend$width)
+    gl <- lapply(plots, function(x)
+      x + theme(legend.position = "none"))
+    gl <- c(gl, ncol = ncol, nrow = nrow)
+
+    combined <- switch(
+      position,
+      "bottom" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 1,
+        heights = grid::unit.c(unit(1, "npc") - lheight, lheight)
+      ),
+      "right" = arrangeGrob(
+        do.call(arrangeGrob, gl),
+        legend,
+        ncol = 2,
+        widths = grid::unit.c(unit(1, "npc") - lwidth, lwidth)
+      )
+    )
+
+    grid::grid.newpage()
+    grid::grid.draw(combined)
+
+    # return gtable invisibly
+    invisible(combined)
+
+  }
+
 ```
@@
   c(chisq = Pearson.chisq, ratio = prat, rdf = rdf, p = pval)
+}
+
+residfit <- function (model, col="black") {
+  f<-fitted(model)
+  r<-resid(model, type='pearson')
+  plot(f, r, col=col, main='Residuals vs. Fitted')
+  L1<-loess(r~f)
+  fvec = seq(min(f),max(f),length.out=1000)
+  lines(fvec,predict(L1,fvec),col='red')
+}
+
+#do the same for the Scale-Location plot
+scaleloc <- function(model,col="black") {
+  f <- fitted(model)
+  r <- sqrt(abs(residuals(model, type='pearson'))) #transformed pearson residuals
+  plot(f,r,col=col, main='Scale-Location Plot') 
+  L1 <- loess(r~f)
+  fvec = seq(min(f),max(f),length.out=1000)
+  lines(fvec,predict(L1,fvec),col=2)
 }
@@
 summary(fdata)
-
-#### Gather ####
+```
+```{R gather dataframe}
 length(unique(fdata$indiv2))
@@
 ndata$None.Path<-as.integer(ndata$None.Path)
+ndata$Lesions<-as.integer(100-ndata$None.Path)
 ndata$None.Myc<-as.integer(ndata$None.Myc)
+ndata$Mycorrhiza<-as.integer(100-ndata$None.Myc)
 
@@
 sum(row.has.na <- apply(FloristicSurvey, 1, function(x){any(is.na(x))}))
-
 ```
@@
 ## Floristic composition and GM presence
-
-### Linear discriminate analysis
-```{r}
-# Discriminant function analysis is used (general LDA format) because i have a cat. dependent and a binary independent. (it needs binary or continuous!)
-# you might have to bin covers because it only works with categorical, so 0-5% none, 6-40 low etc.
-FloristicSurvey$GM_Coverage_category<-cut(FloristicSurvey$GM_Coverage, c(-Inf,25,50,75,100), labels = c("None to Low","Medium", "High", "Overtaken"))
-table(FloristicSurvey$GM_Coverage_category)
-# [0-20] None
-# ]20-40] low
-# ]40-60] Medium 
-# ]60-80] high
-# ]80-100] Overtaken
-```
-
-```{r}
-#LDA
-FloristicSurveysmall<-data.frame(FloristicSurvey[,4:56])
-# Linear discriminant function analysis
-
-FloristicSurveysmall <- FloristicSurveysmall[,-c(42,45)] 
-FloristicSurveyLDA <- lda(GM_Coverage_category ~., data=FloristicSurveysmall)
-# Extract scaling vectors
-scalvec<-data.frame(FloristicSurveyLDA$scaling)
-# Extract predictions
-FloristicSurveyLDAval <- data.frame(predict(FloristicSurveyLDA)$x)
-
-# Plot results
-ggplot(data=FloristicSurveyLDAval,aes(x=LD1, y=LD2, group=FloristicSurveysmall$GM_Coverage_category))+
-  stat_ellipse(geom="polygon",aes(colour=FloristicSurveysmall$GM_Coverage_category),fill=NA,size=1.2,alpha=0.3)+
-  stat_ellipse(geom="polygon",aes(fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=1.2,alpha=0.3)+
-  geom_point(aes(shape=FloristicSurveysmall$GM_Coverage_category,fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=I(4),alpha=I(0.8))+
-  xlab("LD Axis 1")+ylab("LD Axis 2")+theme_simple() +
-  theme(legend.title=element_blank())
-
-#test significance of axis
-anova(lm(FloristicSurveyLDAval$LD1~FloristicSurveysmall$GM_Coverage_category))
-anova(lm(FloristicSurveyLDAval$LD2~FloristicSurveysmall$GM_Coverage_category))
-
-#LDA WITHOUT A. PETIOLATA
-FloristicSurveysmall<-data.frame(FloristicSurvey[,4:56])
-# Linear discriminant function analysis
-FloristicSurveysmall[10]<-NULL
-FloristicSurveysmall[c(41,44)] <- NULL 
-FloristicSurveyLDA<-lda(GM_Coverage_category ~ ., data=FloristicSurveysmall)
-# Extract scaling vectors
-scalvec<-data.frame(FloristicSurveyLDA$scaling)
-# Extract predictions
-FloristicSurveyLDAval <- data.frame(predict(FloristicSurveyLDA)$x)
-
-# Plot results
-LDA_of_Floristic_Composition<-ggplot(data=FloristicSurveyLDAval,aes(x=LD1,y=LD2,group=FloristicSurveysmall$GM_Coverage_category))+
-  stat_ellipse(geom="polygon",aes(colour=FloristicSurveysmall$GM_Coverage_category),fill=NA,size=1.2,alpha=0.3)+
-  stat_ellipse(geom="polygon",aes(fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=1.2,alpha=0.3)+
-  geom_point(aes(shape=FloristicSurveysmall$GM_Coverage_category,fill=FloristicSurveysmall$GM_Coverage_category,colour=FloristicSurveysmall$GM_Coverage_category),size=I(4),alpha=I(0.8))+
-  xlab("LD Axis 1")+ylab("LD Axis 2")+
-  ggtitle("LDA of Floristic Composition \n in a Garlic Mustard Population")+
-  theme_bw()+
-  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_color_manual(values=c("green3"," blue3","orange3","red3"))+ scale_fill_manual(values=c("green3","blue3","orange3","red3"))
-ggsave(file="LDA_of_Floristic_Composition.epx", plot=LDA_of_Floristic_Composition, width=10, height=8)
-
-#test significance of axis
-anova(lm(FloristicSurveyLDAval$LD1~FloristicSurveysmall$GM_Coverage_category))
-anova(lm(FloristicSurveyLDAval$LD2~FloristicSurveysmall$GM_Coverage_category))
-```
 
@@
 mult <- 1 #multiplier for the arrows and text for envfit below. You can change this and then rerun the plot command.
-ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
+NMDS_of_Floristic_Composition<-ggplot(data = FloristicSurvey.NMDS.data, aes(y = NMDS2, x = NMDS1))+ 
     geom_path(data = df_ell.FSurvey.GM_coverage, aes(x = NMDS1, y = NMDS2, group = df_ell.FSurvey.GM_coverage$GM_coverage, color=df_ell.FSurvey.GM_coverage$GM_coverage))+ 
@@
     scale_color_manual(values = c(14,5,19,2))+ 
-    coord_cartesian(xlim = c(-1,1.5))+
+    coord_cartesian(xlim = c(-.5,.5))+
   theme_simple()+ guides(color=guide_legend("Garlic Mustard Coverage"))+
-  ggtitle("LDA of Floristic Composition \n in a Garlic Mustard Population")+
+  ggtitle("NMDS of Floristic Composition \n in a Garlic Mustard Population")+
   theme_bw()+
-  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_color_manual(values=c("green3"," blue3","orange3","red3"))+ scale_fill_manual(values=c("green3","blue3","orange3","red3"))
-ggsave(file="LDA_of_Floristic_Composition.epx", plot=LDA_of_Floristic_Composition, width=10, height=8)
-```
-
-### PCA
-```{r}
-FloristicSurvey.pca <- prcomp(FloristicSurvey[,4:(ncol(FloristicSurvey)-1)],center = TRUE) 
-summary(FloristicSurvey.pca)
-factoextra::fviz_eig(FloristicSurvey.pca,addlabels=TRUE,hjust = -0.3)+theme_simple()
-library(ggfortify)
-autoplot(FloristicSurvey.pca, data = FloristicSurvey, colour = "GM_Coverage_category", label.size = 3)+theme_simple()
-round(FloristicSurvey.pca$sdev^2/sum(FloristicSurvey.pca$sdev^2)*100,2)
-# About 25% explained by my first 2 eigenvectors. 50% by the first 6.
-```
-
-### Modeling (redundancy analysis)
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_color_manual(values=c("green3"," blue3","orange3","red3"))
+NMDS_of_Floristic_Composition
+ggsave(file="NMDS_of_Floristic_Composition.eps", plot=NMDS_of_Floristic_Composition, width=10, height=8)
+```
+
+### RDA
 species comp ~ GMcov * pop + soil characteristics inside and outside as covariates? 
@@
 # Redundancy analysis
-sp.comp <- FloristicSurvey[,4:(length(FloristicSurvey))]
-var <- FloristicSurvey[,1:3]
+sp.comp <- FloristicSurvey[,4:(length(FloristicSurvey)-1)]
+var <- FloristicSurvey[,c(1:3,length(FloristicSurvey))]
 var$Quadrat <- as.character(var$Quadrat)
@@
 var$GM_Coverage<-as.numeric(var$GM_Coverage)
-sp.comp<-as.matrix(sp.comp)
-
-formulaRDA <- rda(sp.comp ~ GM_Coverage + Condition(Population) , data=var)
-
-formulaRDA <- rda(sp.comp ~ GM_Coverage , data=var)
+sp.comp.hell<-decostand(sp.comp,method="hellinger")
+
+formulaRDA <- rda(sp.comp.hell ~ GM_Coverage + Population , data=var)
+
 head(summary(formulaRDA))
 RsquareAdj(formulaRDA)
-plot(formulaRDA, scaling = 2)
+coef(formulaRDA)
+scor = scores(formulaRDA, display=c("sp", "cn", "bp"), scaling=2)
+
 anova.cca(formulaRDA,step=1000)
-anova.cca(formulaRDA,by="axis", step=1000)
-
-```
-
-*Note that I redid this with GM_coverage_catogory and i didnt find ANY significance!
+anova.cca(formulaRDA,by="terms", step=1000)
+
+# numeric centroids
+numeric_centroids <- data.frame(scor$centroids)
+numeric_centroids
+str(numeric_centroids)
+numeric_centroids$Population <- rownames(numeric_centroids)
+numeric_centroids
+
+# testing it out
+ggplot(numeric_centroids, aes(x = RDA1, y = RDA2))+
+  geom_text(aes(label = Population))+ # label tells geom_text which text you want to plot
+  ylim(-1,1)+ #NB note that this is a convenience wrapper and may cut data out of your plot
+  xlim(-1,1) #important if you are calculating stats in the plot - these will be excluded
+
+# species
+species_centroids <- data.frame(scor$species)
+species_centroids
+species_centroids$species_names <- rownames(species_centroids) # you can also put label = rownames() etc in the ggplot code. But sometimes you may want it in a column for later
+
+ggplot(numeric_centroids, aes(x = RDA1, y = RDA2))+
+  geom_text(aes(label = Population))+
+  geom_text(data = species_centroids, aes(label = species_names),
+            colour = "orange")+
+  ylim(-1,1)+
+  xlim(-1,1)
+
+# arrows
+continuous_arrows <- data.frame(scor$biplot)
+continuous_arrows
+continuous_arrows$manure_class <- rownames(continuous_arrows) #turning rownames into a variable
+continuous_arrows
+
+site_scores <- data.frame(scores(formulaRDA)$sites)
+site_scores$site_num <- var$Quadrat
+site_scores$coverage<-var$GM_Coverage_category
+
+RDA_plot <- ggplot(numeric_centroids, aes(x = RDA1, y = RDA2))+
+   geom_point(data = site_scores, aes(x = RDA1, y = RDA2,  color=coverage),
+             size = 3)+
+   coord_cartesian(x = c(-1, 1), y = c(-1,1.2))+
+   geom_segment(data = continuous_arrows,
+                aes(x = 0, xend = mult * RDA1,
+                    y = 0, yend = mult * RDA2),
+                arrow = arrow(length = unit(0.25, "cm")), colour = "grey") + #grid is required for arrow to work.
+   geom_text(data = continuous_arrows,
+             aes(x= (mult + mult/10) * RDA1, y = (mult + mult/10) * RDA2, 
+                 label = manure_class), 
+             size = 5,
+             hjust = 0.5)+
+   geom_text(aes(label = Population))+ theme_bw()
+RDA_plot
+ggsave(file="RDA_plot.eps", plot=RDA_plot, width=10, height=8)
+
+```
 
@@
 
-par(mfrow=c(2,2))
-ggplot(Soil_characteristics, aes(Location,Agg_stability,fill=Location))+ geom_boxplot() +
-  theme_simple()
-ggplot(Soil_characteristics, aes(Location,pH,fill=Location))+ geom_boxplot() +
-  theme_simple()
-ggplot(Soil_characteristics, aes(Location,C_percent,fill=Location))+ geom_boxplot() +
-  theme_simple()
-ggplot(Soil_characteristics, aes(Location,N_percent,fill=Location))+ geom_boxplot() +
-  theme_simple()
+Agg_stability_plot<-ggplot(Soil_characteristics, aes(Location,Agg_stability,fill=Location))+ geom_boxplot() +
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_fill_manual(values=c("red3","blue3"))
+
+ph_plot<-ggplot(Soil_characteristics, aes(Location,pH,fill=Location))+ geom_boxplot() +
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12)) + scale_fill_manual(values=c("red3","blue3"))
+
+C_percent_plot<-ggplot(Soil_characteristics, aes(Location,C_percent,fill=Location))+ geom_boxplot() +
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12)) + scale_fill_manual(values=c("red3","blue3"))
+
+N_percent_plot<-ggplot(Soil_characteristics, aes(Location,N_percent,fill=Location))+ geom_boxplot() +
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_fill_manual(values=c("red3","blue3"))
+
+edaphic_soil_qualities_plot<-grid_arrange_shared_legend(Agg_stability_plot, ph_plot,C_percent_plot, N_percent_plot)
+ggsave(file="edaphic_soil_qualities_plot.eps", plot=edaphic_soil_qualities_plot, width=10, height=8)
+
 Soil_characteristics$Population<-as.factor(Soil_characteristics$Population)
@@
 GLMER_soil <- glmer(Location~scale(Agg_stability)*scale(C_percent)*scale(N_percent)+(1|Population),family=binomial(link='logit'),data=Soil_characteristics)
+residfit(GLMER_soil)
+scaleloc(GLMER_soil)
+
+pr<-resid(GLMER_soil, type='pearson')
+n<-nrow(Soil_characteristics)
+c<-length(coef(GLMER_soil))
+(Disp<-sum(pr^2)/(n-c))
+
 summary(GLMER_soil)
@@
 # A model with nothing is best...
+```
+
+LDA differs from RDA and CCA in that the response variable is a grouping of the
+sites. This grouping may have been obtained by clustering the sites on the basis of
+a data set, or it may represent an ecological hypothesis. LDA tries to determine to what extent an independent set of quantitative variables can explain this grouping.
+```{r soil LDA}
+var<-Soil_characteristics[,c(1,2)]
+Y<-Soil_characteristics[,-c(1,2,5)]
+var$Population<-as.factor(var$Population)
+Location<-as.factor(var$Location)
+Y$Sample <-paste(var$Population,var$Location) 
+rownames(Y)<-Y$Sample
+Y$Sample<-NULL
+
+covar_cor = cor(Y)
+corrplot.mixed(covar_cor, upper = "ellipse", lower = "number")
+
+Nutrient_PCA<-dudi.pca(df = Y[, c(3, 4)], scannf = FALSE, nf = 1)
+Nutrient_PCA$co
+Nutrient_PCA$eig/sum(Nutrient_PCA$eig)
+Y$Nutrient_PC1 = Nutrient_PCA$li[,1]
+
+Y<-Y[,c(1,2,5)]
+
+Y.d1 <-dist(Y)
+Y.MHV<-betadisper(Y.d1,var$Location)
+permutest(Y.MHV) # no significant difference in dispersion between groups
+
+formulaLDA <- lda(var$Location ~ Agg_stability + Nutrient_PC1 + pH, data=Y)
+summary(formulaLDA)
+formulaLDA$means
+scalvec<-data.frame(formulaLDA$scaling)
+LDAval <- data.frame(predict(formulaLDA)$x)
+anova(lm(LDAval$LD1~var$Location))
+DF<-cbind(LDAval$LD1,data.frame(var$Location))
+colnames(DF)<-c("LDAval","Location")
+SoilLDAplot<-ggplot(DF, aes(LDAval, fill = Location)) + geom_density(alpha = 0.2)+
+  ggtitle("Linear Discriminant analysis of Soil characteristics \n in and out of A. petiolata invasion")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_fill_manual(values=c("red3","blue3"))
+SoilLDAplot
+ggsave(file="SoilLDAplot.pdf", plot=SoilLDAplot, width=10, height=8)
+
 ```
@@
 
-ggplot(fdat_ind,aes(species,Mycorrhiza,colour=loc))+geom_boxplot()+theme_simple()
-ggplot(fdat_ind,aes(pop,Mycorrhiza,colour=loc))+geom_boxplot()+theme_simple()
+Myc_location_species_plot <- ggplot(fdat_ind,aes(loc,Mycorrhiza, fill=loc))+geom_boxplot()+facet_wrap(~species)+
+  xlab("Plant Species")+ylab("Mycorrhizal \nColonization")+
+  ggtitle("Species Mycorrhizal Colonization \n in and out of Garlic Mustard")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 18))+scale_fill_manual(values=c("light blue","forest green"))
+Myc_location_species_plot
+ggsave(file="Myc_location_species_plot.pdf", plot=Myc_location_species_plot, width=10, height=8)
+
+Lesion_location_species_plot <- ggplot(fdat_ind,aes(loc,Lesion,fill=loc))+geom_boxplot()+facet_wrap(~species)+
+  xlab("Plant Species")+ylab("Lesion")+
+  ggtitle("Species Lesions \n in and out of Garlic Mustard")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 18))+scale_fill_manual(values=c("red3","blue3"))
+Lesion_location_species_plot
+ggsave(file="Lesion_location_species_plot.pdf", plot=Lesion_location_species_plot, width=10, height=8)
+
+Myc_location_population_plot<-ggplot(fdat_ind,aes(loc,Mycorrhiza,fill=loc))+geom_boxplot()+facet_wrap(~pop)+
+  xlab("Population")+ylab("Mycorrhizal \nColonization")+
+  ggtitle("Mycorrhizal Colonization \n in and out of Garlic Mustard Population")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 18))+scale_fill_manual(values=c("red3","blue3"))
+Myc_location_population_plot
+ggsave(file="Myc_location_population_plot.pdf", plot=Myc_location_population_plot, width=10, height=8)
 ```
@@
 
-ggplot(fdat_ind,aes(Mycorrhiza,Lesion))+facet_wrap(~species)+
-  geom_point(aes(col=loc))+theme_simple()+geom_smooth(method="lm")
+Myc_vs_Lesion<-ggplot(fdat_ind,aes(Mycorrhiza,Lesion))+facet_wrap(~species)+
+  geom_point(aes(col=loc))+theme_simple()+geom_smooth(method="lm",colour="black")+
+  xlab("Mycorrhizal \nColonization")+ylab("Lesion \nMeasurement")+
+  ggtitle("Effect of Mycorrhiza on Lesions \n in and out of Garlic Mustard per Species")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 18))+scale_color_manual(values=c("red3","blue3"))
+Myc_vs_Lesion
+ggsave(file="Myc_vs_Lesion.eps", plot=Myc_vs_Lesion, width=10, height=8)
 ```
@@
 
-ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path, color=location))+
+Myc_vs_Lesion_plot<-ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path, color=location))+
   geom_smooth(method = "lm")+
@@
   theme_simple()+
-  labs(x = "Mycorrhizal colonization", y="Lesions")
+  labs(x = "Mycorrhizal colonization", y="Lesions")+
+  xlab("Mycorrhizal \nColonization")+ylab("Lesion \nMeasurement")+
+  ggtitle("Effect of Mycorrhiza on Lesions \n in and out of Garlic Mustard")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 18))+scale_color_manual(values=c("red3","blue3"))
+Myc_vs_Lesion_plot
+ggsave(file="Myc_vs_Lesion_plot.eps", plot=Myc_vs_Lesion_plot, width=10, height=8)
 ```
@@
 
-```{r}
+```{r soil lesion~myc}
 Soil_characteristics$Location<-as.character(Soil_characteristics$Location)
@@
 fulldata <- merge(Soil_characteristics, ndata, by=c("pop","location"))
-# note i used the SCALED dataframe for the total histology
+names(Root_size)[1]<-"indiv"
 fulldata <- merge(fulldata, Root_size, by=c("indiv","location","pop","species"))
@@
 fulldata$pop<-as.factor(fulldata$pop)
+fulldata$Mycorrhiza<-100-fulldata$None.Myc
+fulldata$Lesion<-100-fulldata$None.Path
 # model myc_lesion 
-mod1 <- glmmadmb(binlesionF ~ scale(None.Myc)  * scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop), data = fulldata,family = "binomial")
+hist(fulldata$Lesion)
+shapiro.test(fulldata$Lesion)
+mod1 <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
+                    scale(pH) + scale(Agg_stability) + scale(N_percent) +
+                    scale(C_percent) + (1 | pop) +
+                          Mycorrhiza:N_percent + Mycorrhiza:scale(mean_rootsize) +
+                          Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                          Mycorrhiza:scale(Agg_stability)+Mycorrhiza:C_percent,
+                  data = fulldata,family = "poisson")
 summary(mod1)
-mod1.dredge <- dredge(mod1)
-mod1.dredgegood <- subset(mod1.dredge,mod1.dredge$delta<=7)
+residfit(mod1)
+scaleloc(mod1)
+
+pr<-resid(mod1, type='pearson')
+n<-nrow(fulldata)
+c<-length(coef(mod1))
+(Disp<-sum(pr^2)/(n-c))
+
+mod10 <- glmmadmb(Lesion ~  Mycorrhiza + scale(mean_rootsize) + species + 
+                    scale(pH) + scale(Agg_stability) + scale(N_percent) +
+                    scale(C_percent) + (1 | pop) +
+                          Mycorrhiza:N_percent + Mycorrhiza:scale(mean_rootsize) +
+                          Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                          Mycorrhiza:scale(Agg_stability)+Mycorrhiza:C_percent,
+                  data = fulldata,family = "nbinom1")
+
+mod11 <- glmmadmb(binlesionF ~ Mycorrhiza + scale(mean_rootsize) + species + 
+                    scale(pH) + scale(Agg_stability) + scale(N_percent) +
+                    scale(C_percent) + (1 | pop) +
+                          Mycorrhiza:N_percent + Mycorrhiza:scale(mean_rootsize) +
+                          Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                          Mycorrhiza:scale(Agg_stability)+Mycorrhiza:C_percent,
+                  data = fulldata,family = "binomial")
+
+ICtab(mod1, mod10, mod11, type='AICc')
+
+#ploting the residuals of mycorrhizal on lesions
+hist(fulldata$Mycorrhiza)
+mod1.2<-glm.nb(Mycorrhiza ~ scale(mean_rootsize) + species + 
+                    scale(pH) + scale(Agg_stability) + scale(N_percent) +
+                    scale(C_percent) +
+                          Mycorrhiza:N_percent + Mycorrhiza:scale(mean_rootsize) +
+                          Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                          Mycorrhiza:scale(Agg_stability)+Mycorrhiza:C_percent,
+               data = fulldata)
+residfit(mod1.2)
+scaleloc(mod1.2)
+
+pr<-resid(mod1.2, type='pearson')
+n<-nrow(fulldata)
+c<-length(coef(mod1.2))
+(Disp<-sum(pr^2)/(n-c))
+
+var<-fulldata[,c(5,6,8,9,20,21,22)]
+covar_cor = cor(var)
+corrplot.mixed(covar_cor, upper = "ellipse", lower = "number")
+
+Nutrient_PCA = dudi.pca(df = var[, c(3, 4)], scannf = FALSE, nf = 1)
+Nutrient_PCA$co
+Nutrient_PCA$eig/sum(Nutrient_PCA$eig)
+fulldata$Nutrient_PC1 = Nutrient_PCA$li[,1]
+
+mod10 <- glmmadmb(Lesion ~ Mycorrhiza + location + scale(mean_rootsize) + species + 
+                                   scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
+                                   (1 | pop)+
+                                   Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                                   Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                                   Mycorrhiza:scale(Agg_stability)+ Mycorrhiza:location, 
+                                 data = fulldata,family = "nbinom1")
+
+mod10.2 <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
+                                    scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
+                                    (1 | pop)+
+                                    Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                                    Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                                    Mycorrhiza:scale(Agg_stability)+ Mycorrhiza:location, 
+                                  data = fulldata,family = "nbinom1")
+
+mod10.3 <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
+                      scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
+                      (1 | pop)+
+                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                      Mycorrhiza:scale(Agg_stability), 
+                    data = fulldata,family = "nbinom1")
+
+mod10.4 <- glmmadmb(Lesion ~ scale(mean_rootsize) + species + 
+                          scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + 
+                          (1 | pop)+
+                          Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                          Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                          Mycorrhiza:scale(Agg_stability), 
+                        data = fulldata,family = "nbinom1")
+
+ICtab(mod10, mod10.2, mod10.3, mod10.4) # mycorrhiza or not should not be discounted. delta = 2.
+
+mod10.5 <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
+                      scale(Agg_stability) + Nutrient_PC1 + 
+                      (1 | pop)+
+                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                      Mycorrhiza:scale(Agg_stability), 
+                    data = fulldata,family = "nbinom1")
+
+ICtab(mod10.3,mod10.5)
+
+mod10.6 <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
+                      Nutrient_PC1 + 
+                      (1 | pop)+
+                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                      Mycorrhiza:scale(Agg_stability), 
+                    data = fulldata,family = "nbinom1")
+
+ICtab(mod10.6,mod10.5)
+
+mod10.7 <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
+                      Nutrient_PC1 + 
+                      (1 | pop)+
+                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                      Mycorrhiza:species + 
+                      Mycorrhiza:scale(Agg_stability), 
+                    data = fulldata,family = "nbinom1")
+
+ICtab(mod10.6,mod10.7)
+
+mod10.8 <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
+                      Nutrient_PC1 + 
+                      (1 | pop)+
+                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                      Mycorrhiza:species + Mycorrhiza:scale(pH),
+                    data = fulldata,family = "nbinom1")
+ICtab(mod10.6,mod10.8)
+
+mod10.9 <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species+
+                      (1 | pop)+
+                      Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                      Mycorrhiza:scale(Agg_stability), 
+                    data = fulldata,family = "nbinom1")
+ICtab(mod10.9,mod10.6)
+
+mod10.10 <- glmmadmb(Lesion ~ Mycorrhiza + scale(mean_rootsize) + species + 
+                      Nutrient_PC1 + 
+                      (1 | pop)+
+                      Mycorrhiza:scale(mean_rootsize) +
+                      Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                      Mycorrhiza:scale(Agg_stability), 
+                    data = fulldata,family = "nbinom1")
+
+ICtab(mod10.10,mod10.6)
+
+pr<-resid(mod10.6, type='pearson')
+n<-nrow(fulldata)
+c<-length(coef(mod10.6))
+(Disp<-sum(pr^2)/(n-c))
+
+summary(mod10.6)
+data.frame(coef(mod10.6))
+confint(mod10.6)
+
+pdf(file="regressioncoefficients_lesionvsMyc.pdf", width=10, height=8)
+coefplot2(mod10.6)
+dev.off()
+
+effect(mod = mod10.Colin, "Mycorrhiza")
+```
+```{r Model based figure myc VS lesion in soil}
+mod10.Colin.NM <- glmmadmb(Lesion ~ scale(mean_rootsize) + species + 
+                          scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + (1 | pop)+
+                          Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                          Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                          Mycorrhiza:scale(Agg_stability), 
+                        data = fulldata,family = "nbinom1")
+
+mod1.4 <- glmmadmb(Mycorrhiza ~ scale(mean_rootsize) + species + 
+                          scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + (1 | pop)+
+                          Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                          Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                          Mycorrhiza:scale(Agg_stability), 
+                        data = fulldata,family = "nbinom1")
+
+X1<-residuals(mod10.Colin.NM)
+X2<-residuals(mod1.4)
+df<-as.data.frame(cbind(X1,X2))
+PartialResidMycLesion<-ggplot(df, aes(X1,X2))+geom_smooth(method="lm")+geom_point()+
+  theme_simple()+
+  ggtitle("Added Variable plot of\nMycorrhiza effect on Lesion")+
+  labs(x="Residuals of Mycorrhiza", y="Residuals of Lesions")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))
+PartialResidMycLesion
+ggsave(file="PartialResidMycLesion.eps", plot=PartialResidMycLesion, width=10, height=8)
+
+```
+```{r Model based figure root size VS lesion in soil}
+hist(fulldata$mean_rootsize)
+lmod10.meanrs <- lm(mean_rootsize ~ Mycorrhiza + species + 
+                          scale(pH)+ scale(Agg_stability) + Nutrient_PC1,data = fulldata)
+plot(lmod10.meanrs)
+#athough its not "normal" the residuals and the heteroskedasticity is good so ill keep it
+
+mod10.noRS <- glmmadmb(Lesion ~ Mycorrhiza + species + 
+                          scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + (1 | pop)+
+                          Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                          Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                          Mycorrhiza:scale(Agg_stability), 
+                        data = fulldata,family = "nbinom1")
+
+mod10.meanrs <- lmer(mean_rootsize ~ Mycorrhiza + species + 
+                          scale(pH)+ scale(Agg_stability) + Nutrient_PC1 + (1 | pop)+
+                          Mycorrhiza:Nutrient_PC1 + Mycorrhiza:scale(mean_rootsize) +
+                          Mycorrhiza:species + Mycorrhiza:scale(pH) +
+                          Mycorrhiza:scale(Agg_stability), 
+                        data = fulldata)
+X1<-residuals(mod10.noRS)
+X2<-residuals(mod10.meanrs)
+df<-as.data.frame(cbind(X1,X2))
+PartialResidRootSizeLesion<-ggplot(df, aes(X1,X2))+geom_smooth(method="lm")+geom_point()+
+  theme_simple()+
+  ggtitle("Added Variable plot of\nRoot Size effect on Lesion")+
+  labs(x="Residuals of Root Size", y="Residuals of Lesions")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))
+PartialResidRootSizeLesion
+ggsave(file="PartialResidRootSizeLesion.eps", plot=PartialResidRootSizeLesion, width=10, height=8)
+
+```
+
+```{r soil myc}
 # model myc 
 mod2 <- glmmadmb(binmycorrF ~ scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop) , data = fulldata,family = "binomial")
-summary(mod2)
-mod2.dredge <- dredge(mod2)
-mod2.dredgegood <- subset(mod2.dredge,mod2.dredge$delta<=7)
+
+mod1.4<-glmmadmb(Mycorrhiza ~ scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop), data = fulldata,family="nbinom1")
+
+mod2.1<-glmmadmb(Mycorrhiza ~ scale(mean_rootsize) * species + scale(pH) + scale(Agg_stability) + scale(N_percent) + scale(C_percent) + (1 | pop), data = fulldata,family="poisson")
+
+ICtab(mod2, mod1.4, mod2.1, type='AICc')
+
+summary(mod1.4)
+
+var<-fulldata[,c(5,6,8,9,21)]
+covar_cor = cor(var)
+corrplot.mixed(covar_cor, upper = "ellipse", lower = "number")
+sparrow_PCA = dudi.pca(covariates)
+2
+
+mod1.4.dredge <- dredge(mod1.4)
+mod1.4.dredgegood <- subset(mod1.4.dredge,mod1.4.dredge$delta<=7)
+mod1.4.avg<-model.avg(mod1.4.dredgegood)
+summary(mod1.4.avg)
+
+```
+
+### Does root size influence how myc protect from lesion?
+```{r rootsize}
+Root_size$mean_rootsize <- rowSums(Root_size[,2:11])/length(Root_size[,2:11])
+names(Root_size)[1]<-"indiv2"
+
+fdata_rs <- merge(fdata, Root_size, by=c("indiv2","location","pop","species"))
+
+## Mycorrhiza model (NOTE: No loc*species because not all species present in all populations)
+base.Les<-glmmadmb(Lesion~ Mycorrhiza * species * location * mean_rootsize +(1|pop),data=fdata_rs,family = "binomial", extra.args="-ndi 30000")
+
+Les2<-glmmadmb(Lesion ~ Mycorrhiza * species * location * mean_rootsize +(1|pop)-Mycorrhiza:species:location:mean_rootsize,data=fdata_rs,family = "binomial", extra.args="-ndi 30000")
+
+anova(base.Les,Les2)
+
+Les3a<-glmmadmb(Lesion~Mycorrhiza * species * location * mean_rootsize +(1|pop) -species:mean_rootsize,data=fdata_rs,family = "binomial", extra.args="-ndi 30000")
+Les3b<-glmmadmb(Lesion~Mycorrhiza * species * location * mean_rootsize +(1|pop) -species:mean_rootsize:location,data=fdata_rs,family = "binomial", extra.args="-ndi 30000")
+Les3c<-glmmadmb(Lesion~Mycorrhiza * species * location * mean_rootsize +(1|pop) -Mycorrhiza:mean_rootsize,data=fdata_rs,family = "binomial", extra.args="-ndi 30000")
+anova(base.Les,Les3a) # TEST species*rootsize 
+anova(base.Les,Les3b) # TEST Myc*location*rootsize 
+anova(base.Les,Les3c) # TEST Myc*rootsize
+```
+
+Correlation model
+
+```{r}
+# calculating the r
+indivCODE <- as.character(unique(fdata_rs$indiv2))
+dfcorr <-data.frame(indiv2=c(0),r=c(0))
+for (i in 1:length(indivCODE)){
+  dat1<-NULL
+  dat1<-fdata_rs[fdata_rs$indiv2==indivCODE[i],]
+  dfcorr[i,1] <- indivCODE[i]
+  dfcorr[i,2] <- cor(as.numeric(dat1$Mycorrhiza),as.numeric(dat1$Lesion))
+}
+dfcorr %>% drop_na()->dfcorr
+
+fdata_rs.corr <- merge(dfcorr, Root_size, by="indiv2")
+shapiro.test(fdata_rs.corr$r)
+
+fdata_rs.corr$r.t<-fdata_rs.corr$r+1
+CorrLM<-lm(r.t~ species * location * mean_rootsize,data=fdata_rs.corr)
+
+bc<-boxcox(CorrLM, lambda = seq(-2, 2, 0.1))
+lambda <- bc$x[which.max(bc$y)]
+fdata_rs.corr <- cbind(fdata_rs.corr, ((fdata_rs.corr$r.t^lambda)-1)/lambda)
+names(fdata_rs.corr)[length(fdata_rs.corr)] <- "Yprime"
+shapiro.test(fdata_rs.corr$Yprime)
+hist(fdata_rs.corr$Yprime)
+
+CorrLMERBC<-lmer(Yprime~ species + location + mean_rootsize + 
+                   location:species +
+                   (1|pop),
+                 data=fdata_rs.corr)
+pr<-resid(CorrLMERBC, type='pearson')
+n<-nrow(fdata_rs.corr)
+c<-length(coef(CorrLMERBC))
+(Disp<-sum(pr^2)/(n-c))
+
+plot(effect("location:mean_rootsize", CorrLMERBC))
+plot(effect("mean_rootsize", CorrLMERBC))
+
+summary(CorrLMERBC)
+CorrLMER.dredge<-dredge(CorrLMERBC)
+r.squaredGLMM(CorrLMERBC)
 ```

### 2018-03-19 Older/MScFigures.Rmd
Commit work

--- 2018-01-29 MScFigures.Rmd
@@
 output:
-  html_document:
-    df_print: paged
-    toc: yes
   html_notebook:
@@
 ```{r Introduce co-occurence dataset, message=FALSE, warning=FALSE}
-mdata <- read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
+mdata <- read.csv("CSV/Assessing_Oct_20.csv",stringsAsFactors=F)
 indiv <- mdata$CODE[!mdata$CODE==""]
@@
 ```{r Introduce total dataset, message=FALSE, warning=FALSE}
-mdata<-read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
+mdata<-read.csv("CSV/Assessing_Oct_20.csv",stringsAsFactors=F)
 indiv<-mdata$CODE[!mdata$CODE==""]

### 2018-03-19 Older/Variables.Rmd
Commit work

--- 2018-01-27 MScFigures.Rmd
@@
 ---
-title: "MSc Statistical overview"
-output:
-  html_document:
-    df_print: paged
-    toc: yes
-  html_notebook:
-    highlight: tango
-    theme: cerulean
-    toc: yes
-  word_document:
-    toc: yes
+title: "Variables"
+author: "Robert I. Colautti"
+date: "January 27, 2018"
+output: html_document
 ---
-# Housekeeping
-### Preamble
 
-By Katherine Duchesneau
+# Datasets
 
-We are working with the roots Lesion and Mycorrhiza dataset for now.
+  * Assessing_Oct_20.csv (mdata) --> Root transect data
+  * fdata --> mdata with errors corrected
+  * fdata_gather --> repeated measures version of fdata
 
-### R details
-
-This section contains all the necessary details about the R version and package version used to run this Notebook.
-
-  * File creation date: `r Sys.Date()`
-  * `r R.version.string`
-  * `tidyverse` package version: `r packageVersion("tidyverse")`
-  * `lme4` package version `r packageVersion("lme4")`
-  * `MASS` package version `r packageVersion("MASS")`
-  * `MuMIn` package version `r packageVersion("MuMIn")`
-  * `emmeans` package version `r packageVersion("emmeans")`
-  * `boot` package version `r packageVersion("boot")`
-  * `brms` package version `r packageVersion("brms")`
-  * `loo` package version `r packageVersion("loo")`
-  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`
-  * `mefa` package version `r packageVersion("mefa")`
-  * `library(devtools)` and `install_github("vqv/ggbiplot")` package version `r packageVersion("ggbiplot")`
-  * also requires [rtools](https://cran.r-project.org/bin/windows/Rtools/)
-
-### Load Packages and Functions
-
-```{r Load_packages and functions, message=FALSE, warning=FALSE}
-library(tidyverse)
-library(lme4)
-library(MASS)
-library(MuMIn)
-library(emmeans)
-library(boot)
-library(brms)
-library(loo)
-library(fitdistrplus)
-library(mefa)
-library(ggbiplot)
-
-# theme_simple() a homemade function from the Colautti lab (2017) to standardize figures
-theme_simple <- function (base_size = 16, base_family = "") {
-  theme_classic(base_size = base_size, base_family = base_family) %+replace%
-    theme(
-      axis.text = element_text(colour = "black"),
-      axis.title.x = element_text(size=18),
-      axis.text.x = element_text(size=16, face= "italic"),
-      axis.title.y = element_text(size=18, angle=90), 
-      axis.text.y = element_text(size=16),
-      axis.ticks = element_blank(),
-      panel.background = element_rect(fill="white"),
-      panel.border = element_blank(),
-      plot.title=element_text(face="bold", size=24)
-      #      legend.position="none"
-    )
-}
-
-overdisp_fun <- function(model) {
-  ## number of variance parameters in an n-by-n variance-covariance matrix
-  vpars <- function(m) {
-    nrow(m) * (nrow(m) + 1)/2
-  }
-  # The next two lines calculate the residual degrees of freedom
-  model.df <- sum(sapply(VarCorr(model), vpars)) + length(fixef(model))
-  rdf <- nrow(model.frame(model)) - model.df
-  # extracts the Pearson residuals
-  rp <- residuals(model, type = "pearson")
-  Pearson.chisq <- sum(rp^2)
-  prat <- Pearson.chisq/rdf
-  # Generates a p-value. If less than 0.05, the data are overdispersed.
-  pval <- pchisq(Pearson.chisq, df = rdf, lower.tail = FALSE)
-  c(chisq = Pearson.chisq, ratio = prat, rdf = rdf, p = pval)
-}
-```
-
-# Introducing the Data
-
-### Load/ Modify data: Co-occurence
-```{r Introduce co-occurence dataset, message=FALSE, warning=FALSE}
-mdata <- read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
-indiv <- mdata$CODE[!mdata$CODE==""]
-tdata <- mdata[grep("[0-9]+",mdata$Cross),]
-nrow(tdata)/length(indiv)
-# This is not the same because some individuals just had the totals not the cooccurence data
-indiv2 <- tdata$CODE[!tdata$CODE==""]
-nrow(tdata)/length(indiv2)
-indiv2 <- data.frame(indiv2)
-indiv2 <- mefa:::rep.data.frame(indiv2,each=100)
-fdata <- cbind(indiv2,tdata)
-fdata <- fdata[,-c(2,3,4,9,14,17,18)]
-
-# Cleaning up the occurence data
-fdata[is.na(fdata)] <- 0
-fdata$Lesion<-rowSums(fdata[,2:4])
-fdata[fdata$Lesion>1,]
-fdata$Mycorrhiza<-rowSums(fdata[,6:8])
-fdata[fdata$Mycorrhiza>1,]
-fdata <- fdata[,-c(2:4,6:8)]
-
-#### Checking data for problems ####
-
-summary(fdata)
-fdata$None.Path <- as.integer(fdata$None.Path)
-fdata$None.Myc <- as.integer(fdata$None.Myc)
-fdata[is.na(fdata)] <- 0
-
-sherb <- fdata$Herbivory+fdata$None.Herb
-fdata[sherb!=1,]
-fdata[sherb!=1,"None.Herb"]<-1
-
-# Are all the sums equal to 100 for herb? 
-dframeHerb <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
-c <- 1
-for (i in unique(fdata$indiv2)){
-  dframeHerb[c,] <- NA
-  subdata <- fdata[fdata$indiv2==i,]
-  dframeHerb$counter[c] <- c
-  dframeHerb$Indiv2[c] <- i
-  dframeHerb$Sum[c] <- sum(subdata[,"Herbivory"]+subdata[,"None.Herb"])
-  subdata <- NA
-  c <- c + 1
-}
-dframeHerb[dframeHerb$Sum!=100,]
-
-# Are all the sums equal to 100 for Mycorrhiza? 
-dframeMyc <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
-c <- 1
-for (i in unique(fdata$indiv2)){
-  dframeMyc[c,] <- NA
-  subdata <- fdata[fdata$indiv2==i,]
-  dframeMyc$counter[c] <- c
-  dframeMyc$Indiv2[c] <- i
-  dframeMyc$Sum[c] <- sum(subdata[,"Mycorrhiza"]+subdata[,"None.Myc"])
-  subdata <- NA
-  c <- c + 1
-}
-dframeMyc[dframeMyc$Sum!=100,]
-
-# Are all the sums equal to 100 for Lesions? 
-dframeLesion <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
-c <- 1
-for (i in unique(fdata$indiv2)){
-  dframeLesion[c,] <- NA
-  subdata <- fdata[fdata$indiv2==i,]
-  dframeLesion$counter[c] <- c
-  dframeLesion$Indiv2[c] <- i
-  dframeLesion$Sum[c] <- sum(subdata[,"Lesion"]+subdata[,"None.Path"])
-  subdata <- NA
-  c <- c + 1
-}
-dframeLesion[dframeLesion$Sum!=100,]
-
-# Separating "Individual" into: pop,location,species columns 
-fdata$pop <- gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",fdata$indiv)
-fdata$location <- gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",fdata$indiv)
-fdata$species <- sub("^[0-9]+[I,O]([A-Z]+).*","\\1",fdata$indiv)
-fdata$location <- as.factor(fdata$location)
-fdata$species <- as.factor(fdata$species)
-fdata$pop <- as.factor(fdata$pop)
-fdata$indiv2 <- as.character(fdata$indiv2)
-summary(fdata)
-fdata %>% drop_na()->fdata
-
-fdata$None.Myc <- as.factor(fdata$None.Myc)
-fdata$Herbivory <- as.factor(fdata$Herbivory)
-fdata$Mycorrhiza <- as.factor(fdata$Mycorrhiza)
-fdata$Lesion <- as.factor(fdata$Lesion)
-fdata$None.Herb <- as.factor(fdata$None.Herb)
-fdata$None.Path <- as.factor(fdata$None.Path)
-summary(fdata)
-
-#### Gather ####
-length(unique(fdata$indiv2))
-Cross<- data.frame(c(rep(1:100, times=225)))
-fdatac <- cbind(fdata,Cross)
-colnames(fdatac)[11]<-"cross"
-fdatac %>% gather(Trait, Value, c(4,6,7)) -> fdata_gather # The warning is an inconsequential bug from tidyverse (https://github.com/tidyverse/tidyr/issues/386)
-fdata_gather$Value<-as.numeric(fdata_gather$Value)
-fdata_gather$Trait<-as.factor(fdata_gather$Trait)
-fdata_gather <- fdata_gather[,-c(2:4)]
-```
-
-### Load/ Modify data: Totals
-```{r Introduce total dataset, message=FALSE, warning=FALSE}
-mdata<-read.csv("Assessing_Oct_20.csv",stringsAsFactors=F)
-indiv<-mdata$CODE[!mdata$CODE==""]
-tdata<-mdata[mdata$Slide=="TOTAL",]
-length(indiv)
-nrow(tdata)
-
-ndata<-cbind(indiv,tdata)
-ndata<-ndata[,-c(2,3,4,9,14,17:37)]
-ndata$None.Path<-as.integer(ndata$None.Path)
-ndata$None.Myc<-as.integer(ndata$None.Myc)
-
-# Checking data for problems
-problemsPath<-ndata[!rowSums(ndata[,c(2:5)])==100,]
-problemsHyph<-ndata[!rowSums(ndata[,c(6:9)])==100,]
-problemsHerb<-ndata[!rowSums(ndata[,c(10:11)])==100,]
-
-# Separating "Individual" into: pop,location,species columns 
-ndata$pop<-gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",ndata$indiv)
-ndata$location<-gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",ndata$indiv)
-ndata$species<-gsub("^[0-9]+[I,O]([A-Z]+).*","\\1",ndata$indiv)
-ndata$location<-as.factor(ndata$location)
-ndata$species<-as.factor(ndata$species)
-ndata$pop<-as.factor(ndata$pop)
-
-#### Totalling the scores####
-binlesion<-cbind(ndata$None.Path,100-ndata$None.Path)
-binmycorr<-cbind(ndata$None.Myc,100-ndata$None.Myc)
-binherbivory<-cbind(ndata$None.Herb,100-ndata$None.Herb)
-summary(ndata)
-
-# scale data (only need to scale the numerical variables!)
-numcols <- grep("^None.",names(ndata))
-ndatas <- ndata
-ndatas[,numcols] <- scale(ndatas[,numcols])
-```
-
-### Variable descriptions
+# Variable descriptions
 
@@
   * **species:** The particular species to which the sample belongs.
-
-# Reviewing the hypothesis
-
-## Histology data Hypothesis
-### Hypothesis 1
-
-Mycorrhizal colonization protects roots from lesions and herbivory.
-```{r echo=FALSE}
-y<-data.frame(c(rnorm(50, mean=5, sd=8),rnorm(50, mean=50, sd=8)))
-colnames(y)<-c("y")
-y$y<-sort(y$y, decreasing = T)
-x<-data.frame(c(rnorm(50, mean=5, sd=8),rnorm(50, mean=50, sd=8)))
-colnames(x)<-c("x")
-x$x<-sort(x$x, decreasing = F)
-df <- cbind(x,y)
-colnames(df)<-c("x","y")
-
-ggplot(df, aes(x,y))+geom_smooth(method="lm", se=F)+geom_point()+
-  theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
-  theme(axis.text.x = element_blank(),axis.text.y = element_blank())
-```
-
-### Hypothesis 2
-
-A. petiolata invasion reduces mycorrhizal colonization and increases pathogen colonization and herbivory
-```{r echo=FALSE}
-InOut<- data.frame(c(rep("I", times=50),rep("O", times=50)))
-colnames(InOut)<-c("Location")
-df <- cbind(df,InOut)
-
-ggplot(df, aes(x,y, colour=Location))+geom_smooth(method="lm", se=F)+geom_jitter()+
-  theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
-  theme(axis.text.x = element_blank(),axis.text.y = element_blank())
-```
-### Hypothesis 3
-
-Efficiency of mycorrhizal protection is reduced in the presence of A. petiolata
-```{r echo=FALSE}
-y<-data.frame(c(rnorm(50, mean=5, sd=8),rep(40, times=10),rep(41, times=10),rep(42, times=10),rep(40.5, times=10),rep(39, times=10)))
-colnames(y)<-c("y")
-y$y<-sort(y$y, decreasing = T)
-x<-data.frame(c(rnorm(50, mean=5, sd=8),rnorm(50, mean=50, sd=8)))
-colnames(x)<-c("x")
-x$x<-sort(x$x, decreasing = F)
-df <- cbind(x,y)
-colnames(df)<-c("x","y")
-
-InOut<- data.frame(c(rep("I", times=50),rep("O", times=50)))
-colnames(InOut)<-c("Location")
-df <- cbind(df,InOut)
-
-ggplot(df, aes(x,y, colour=Location))+geom_smooth(method="lm", se=F)+geom_jitter()+
-  theme_simple()+labs(x="Mycorrhizal Colonization (%)", y="Lesions (%)")+
-  theme(axis.text.x = element_blank(),axis.text.y = element_blank())
-```
-
-## Molecular data Hypothesis
-
-### Hypothesis 1
-
-A. petiolata invasion changes the diversity of mycorrhizal and other fungal species present in the soil.
-
-I will find that the molecular data from the soil extraction supports this claim by having a reduced biodiversity and abundance of mycorrhiza in samples taken inside A. petiolata populations.
-
-### Hypothesis 2
-
-There will be a negative correlation between mycorrhizal and fungal pathogen diversity.
-
-# Histology data Analysis
-
-## Hypothesis 1: Lesion ~ Mycorriza
-
-###Co-occurence data
-
-```{r Co-occurence model using corr}
-# calculating the r
-indivCODE <- unique(fdata$indiv2)
-dfcorr <-data.frame(indivCODE=c(0),r=c(0))
-for (i in 1:length(indivCODE)){
-  dat1<-NULL
-  dat1<-filter(fdata, fdata$indiv2==indivCODE[i])
-  dfcorr[i,1] <- indivCODE[i]
-  dfcorr[i,2] <- cor(as.numeric(dat1$Mycorrhiza),as.numeric(dat1$Lesion))
-}
-dfcorr %>% drop_na()->dfcorr
-
-#Normal?
-car::qqp(dfcorr$r, "norm")
-shapiro.test(dfcorr$r)
-hist(dfcorr$r)
-# Cannot be normal because it is only between -1 and 1 and our mean is at 0.
-descdist(dfcorr$r, discrete = FALSE, boot = 500)
-
-# weibull when transformed to be positive?
-dfcorr$r.t <- dfcorr$r+1
-fit.weibull <- fitdist(dfcorr$r.t, "weibull")
-car::qqp(dfcorr$r.t, "weibull", shape = fit.weibull$estimate[[1]])
-
-dfcorr$pop <- gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",dfcorr$indivCODE)
-dfcorr$location <- gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",dfcorr$indivCODE)
-dfcorr$species <- sub("^[0-9]+[I,O]([A-Z]+).*","\\1",dfcorr$indivCODE)
-dfcorr$location <- as.factor(dfcorr$location)
-dfcorr$species <- as.factor(dfcorr$species)
-dfcorr$pop <- as.factor(dfcorr$pop)
-
-meanR<-mean(dfcorr$r)
-SEMR<-sd(dfcorr$r)/sqrt(length(dfcorr$r))
-UCI<- meanR+SEMR*1.96
-LCI<- meanR-SEMR*1.96
-mean(filter(dfcorr, dfcorr$location=="I")$r)
-mean(filter(dfcorr, dfcorr$location=="O")$r)
-
-baysian_corrGLMM <- brm(r.t ~ location * species + (1|pop), data=dfcorr, family = weibull(link="log"), control = list(adapt_delta = 0.9))
-baysian_corrGLMM2 <- brm(r.t ~ location + species + (1|pop), data=dfcorr, family = weibull(link="log"), control = list(adapt_delta = 0.9))
-baysian_corrGLMM3 <- brm(r.t ~ location + (1|pop), data=dfcorr, family = weibull(link="log"), control = list(adapt_delta = 0.9))
-baysian_corrGLMM_NULL <- brm(r.t ~ 1 + (1|pop), data=dfcorr, family = weibull(link="log"), control = list(adapt_delta = 0.9))
-
-waic.BCG_1<-waic(baysian_corrGLMM)
-waic.BCG_2<-waic(baysian_corrGLMM2)
-waic.BCG_3<-waic(baysian_corrGLMM3)
-waic.BCG_NULL<-waic(baysian_corrGLMM_NULL)
-compare(waic.BCG_1,waic.BCG_2) #positive means second is better
-compare(waic.BCG_2,waic.BCG_3) #negative means first is better
-compare(waic.BCG_2,waic.BCG_NULL) #negative means first is better
-summary(baysian_corrGLMM2)
-bayes_R2(baysian_corrGLMM2)
-
-ggplot(dfcorr, aes(y=r,x=location))+geom_boxplot()+theme_simple()
-ggplot(dfcorr, aes(y=r,x=species))+geom_boxplot()+theme_simple()
-
-```
-
-Co-occurence with gather: what is the difference? 
-Here I want to see that the traits are associating differently at every cross for each indiv
-
-````{r Co-occurence model GATHER}
-
-baysianGLMERmyc_lesion_GTHR <- brm(Value ~ Trait * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-summary(baysianGLMERmyc_lesion_GTHR)
-bayes_R2(baysianGLMERmyc_lesion_GTHR)
-
-baysianGLMERmyc_lesion_GTHR_1 <- brm(Value ~ Trait * location * species + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-baysianGLMERmyc_lesion_GTHR_2 <- brm(Value ~ Trait + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-baysianGLMERmyc_lesion_GTHR_NULL <- brm(Value ~ 1 + (1|pop) + (1|indiv2/cross), data = fdata_gather, family = bernoulli,control = list(adapt_delta = 0.95))
-
-model.sel(baysianGLMERmyc_lesion_GTHR,baysianGLMERmyc_lesion_GTHR_1,baysianGLMERmyc_lesion_GTHR_2,baysianGLMERmyc_lesion_GTHR_NULL) #not sure if this function will work with brm model, if not ill just have to do a waic and then a compare like the previous...
-should test with a smaller model
-```
-**SUMMARY:**
-
-What is significant with the correlation~location*sp model?
-
-What does it change when we gather the model? What am I really testing?
-Does it really test what I want it to test?
-
-What is significant when we gather? Is this model even any good?
-
-###Totals data
-
-```{r Totals model}
-
-# model 
-GLMMmyc_lesion <- glmer(binlesion ~ None.Myc * species + (1 | pop) , data = ndatas,family = binomial(link = "logit"))
-summary(GLMMmyc_lesion)
-
-options(na.action="na.fail")
-dredge(GLMMmyc_lesion)
-r.squaredGLMM(GLMMmyc_lesion)
-# will need to change this ASAP
-
-ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path))+
-  stat_summary(fun.y=mean, geom="point")+
-  geom_smooth(method = "lm")+
-  geom_point()+
-  theme_simple()+
-  facet_wrap("species")+
-  labs(x = "Mycorrhizal colonization", y="Lesions")
-```
-**SUMMARY:**
-
-Is the totals the same as the corr data?
-
-if not what has change?
-what does it mean biologically: Same/less path=mycorrhiza defend NotSame/less path=mycorrhizal defence is not related to colonization.
-if theres not an effect then maybe it has more to do with the species composition than the actual mycorrhizal colonization, Thats why we will test pathogen colonization alone (without myc = H2)
-
-## Hypothesis 2: Mycorrhiza & Lesion ~ invasion
-
-### Does location impact the effect of myc on lesion?
-
-```{r location interaction with mycorrhiza and lesion}
-GLMMmyc_lesion_loc <- glmer(binlesion ~ None.Myc * location * species + (1 | pop), data = ndatas, family = binomial(link = "logit"))
-summary(GLMMmyc_lesion_loc)
-
-emm<-emmeans(GLMMmyc_lesion_loc, list(~None.Myc| species | location, ~None.Myc| location), type = "response" )
-summary(emm)
-
-ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path))+
-  geom_smooth(method = "lm")+
-  geom_point(aes(color=location))+
-  theme_simple()+
-  facet_wrap("species")+
-  labs(x = "Mycorrhizal colonization", y="Lesions")
-
-pca <- prcomp(ndata[,c(5,9)])
-location <- ndata[,13]
-library(ggbiplot)
-g <- ggbiplot(pca, obs.scale = 1, var.scale = 1, 
-                groups = location, ellipse = TRUE, 
-                circle = TRUE)
-g <- g + scale_color_discrete(name = '')
-g <- g + theme(legend.direction = 'horizontal', 
-                 legend.position = 'top')
-print(g)
-```
-
-### Does location impact lesion alone?
-
-```{r location on lesion}
-glmerLESION_disp <- glmer (binlesion ~ location * species + (1|pop) + (1|indiv), data = ndatas, family = binomial(link="logit"))
-summary(glmerLESION_disp)
-options(na.action="na.fail")
-dredge(glmerLESION_disp)
-r.squaredGLMM(glmerLESION_disp)
-
-ggplot(aes(x = location, y = 100-None.Path, color=location), data=ndata)+
-  geom_boxplot()+
-  geom_jitter(width=0.1)+
-  facet_wrap("species")+
-  theme_simple()
-```
-
-### Does location impact mycorrhiza alone?
-
-```{r location on mycorrhiza}
-glmerMYC_disp <- glmer (binmycorr ~ location * species + (1|pop) + (1|indiv), data = ndata, family = binomial(link="logit"))
-summary(glmerMYC_disp)
-options(na.action="na.fail")
-dredge(glmerMYC_disp)
-r.squaredGLMM(glmerMYC_disp)
-
-ggplot(aes(x = location, y = 100-None.Myc, color=location), data=ndata)+
-  geom_boxplot()+
-  geom_jitter(width=0.1)+
-  facet_wrap("species")+
-  theme_simple()
-
-```
-
-## Hypothesis 3: Lesion ~ Mycorriza * invasion
-
-```{r Hypothesis 3}
-
-ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path, color=location))+
-  geom_smooth(method = "lm")+
-  geom_point()+
-  theme_simple()+
-  facet_wrap("species")+
-  labs(x = "Mycorrhizal colonization", y="Lesions")
-
-ggplot(data = ndata,aes(x = 1-None.Myc, y = 100-None.Path, color=location))+
-  geom_smooth(method = "lm")+
-  geom_point()+
-  theme_simple()+
-  labs(x = "Mycorrhizal colonization", y="Lesions")
-```
-
-# Molecular data Analysis
-
-## Hypothesis 1: Mycorrhiza_div ~ invasion
-
-## Hypothesis 2: Mycorrhiza_div ~ Pathoge_div

### 2018-03-19 AlgebraProblem/Rob_Code.R

@@ -1,0 +1,42 @@
+library(ggplot2)
+
+
+Icor<-function(p1,p2,a){
+  # Conditional probabilities
+  ## A through B can be estimated from the data
+  ## Use these equations to try to solve for p1, p2 & a
+  ## For example, B-C or C-B will isolate p1 and p2 only
+  A<-p1*p2*(1-2*a)
+  B<-p1*(1-p2)+p1*p2*a
+  C<-(1-p1)*p2+p1*p2*a
+  D<-(1-p1)*(1-p2)
+  
+  # Equations for calculating (co)variances and correlation coefficient  
+  V1<-(A+B)*(1-(A+B))
+  V2<-(A+C)*(1-(A+C))
+  COV12<-A-(A+B)*(A+C)
+  
+  COR12<-COV12/(sqrt(V1)*sqrt(V2))
+  
+  # Insert equations for A through B here
+  ## For example, if you wanted to solve for p1 & p2 only
+  ## Combine A through B to isolate each of these terms
+  a<-((C-2*p2)/((B-C+p2)*p2))+1 # Insert equation for estimating alpha (a)
+  p1<-B-C+p2 # Insert equation for p1
+  p2<-C-B+p1# insert equation for p2
+  
+  return(cbind(a,p1,p2))
+}
+
+# Test your model
+SimDat<-data.frame(P1=runif(5000),P2=runif(5000),a=runif(5000))
+Parm<-Icor(p1=SimDat$P1,p2=SimDat$P2,a=SimDat$a)
+
+
+#Each of these 3 plots will be a 1:1 line if your calculations are correct"
+## Test p1
+qplot(SimDat$P1,Parm[,2])
+## Test p2
+qplot(SimDat$P2,Parm[,3])
+## Test alpha
+qplot(SimDat$P2,Parm[,1])

### 2018-03-19 BareBonesModels.R

@@ -1,0 +1,385 @@
+#### *Soil abiotic qualities and location*####
+var<-Soil_characteristics[,c(1,2)]
+Y<-Soil_characteristics[,-c(1,2,5)]
+var$Population<-as.factor(var$Population)
+Location<-as.factor(var$Location)
+Y$Sample <-paste(var$Population,var$Location) 
+rownames(Y)<-Y$Sample
+Y$Sample<-NULL
+
+covar_cor = cor(Y)
+corrplot.mixed(covar_cor, upper = "ellipse", lower = "number")
+Nutrient_PCA = dudi.pca(df = Y[, c(3, 4)], scannf = FALSE, nf = 1)
+Nutrient_PCA$co
+Nutrient_PCA$eig/sum(Nutrient_PCA$eig)
+Soil_characteristics$Nutrient_PC1 = Nutrient_PCA$li[,1]
+
+dat<-data.frame(c(1:20))
+dat[1]<-Soil_characteristics$Location
+colnames(dat)[1]<-"Location"
+dat$Agg_stability.s<-scale(Soil_characteristics$Agg_stability)
+dat$pH.s<-scale(Soil_characteristics$pH)
+dat$Nutrient_PC1.s<-scale(Soil_characteristics$Nutrient_PC1)
+
+GLM_soil <- glm(Location~Agg_stability.s*pH.s*Nutrient_PC1.s,
+                    family=binomial(link='logit'),
+                    data=dat)
+
+ ---------------------------------------------
+#LRT
+
+GLM_soil2 <- glm(Location~Agg_stability.s+pH.s+Nutrient_PC1.s+
+                   Agg_stability.s:pH.s + Agg_stability.s:Nutrient_PC1.s+
+                   Nutrient_PC1.s:pH.s,
+                family=binomial(link='logit'),
+                data=dat)
+anova(GLM_soil,GLM_soil2)
+
+GLM_soil3 <- glm(Location~Agg_stability.s+pH.s+Nutrient_PC1.s+
+                   Agg_stability.s:pH.s + Agg_stability.s:Nutrient_PC1.s,
+                 family=binomial(link='logit'),
+                 data=dat)
+anova(GLM_soil2,GLM_soil3)
+
+
+GLM_soil4 <- glm(Location~Agg_stability.s+pH.s+Nutrient_PC1.s+
+                   Agg_stability.s:pH.s,
+                 family=binomial(link='logit'),
+                 data=dat)
[…]

### 2018-03-19 Extrafigures.R

@@ -1,0 +1,87 @@
+#### Soil abiotic qualities and location####
+
+formulaLDA <- lda(var$Location ~ Agg_stability + Nutrient_PC1 + pH, data=Y)
+summary(formulaLDA)
+formulaLDA$means
+scalvec<-data.frame(formulaLDA$scaling)
+LDAval <- data.frame(predict(formulaLDA)$x)
+anova(lm(LDAval$LD1~var$Location))
+DF<-cbind(LDAval$LD1,data.frame(var$Location))
+colnames(DF)<-c("LDAval","Location")
+SoilLDAplot<-ggplot(DF, aes(LDAval, fill = Location)) + geom_density(alpha = 0.2)+
+  ggtitle("Linear Discriminant analysis of Soil characteristics \n in and out of A. petiolata invasion")+
+  theme_bw()+
+  theme(legend.title=element_blank(),plot.title = element_text(hjust = 0.5,face="bold", size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"),axis.title.x = element_text(size=18),axis.title.y = element_text(size=18),axis.text.y = element_text(size=10),panel.border = element_rect(colour = "black"),strip.background = element_rect(colour = "black",fill="white"),strip.text.x = element_text(size = 12))+scale_fill_manual(values=c("red3","blue3"))
+SoilLDAplot
+ggsave(file="SoilLDAplot.eps", plot=SoilLDAplot, width=10, height=8)
+
+#### Garlic mustard on Mycorrhiza####
+
+modX<-glmmadmb(Mycorrhiza ~ species + species:location +
+                 (1|pop)+ (1|indiv),
+               data=ndata, family="nbinom1") 
+
+modY<-glmmadmb(location ~ species + species:location +
+                 (1|pop)+ (1|indiv),
+               data=ndata, family="binomial") 
+
+X1<-as.factor(round(residuals(modY),5))
+X2<-residuals(modX)
+df<-as.data.frame(cbind(X2,data.frame(ndata$location)))
+colnames(df)<-c("X2","X1")
+AVplotMycINOUT<-ggplot(df, aes(X1,X2, group=X1,fill=X1)) + geom_boxplot()+
+  ggtitle("Added Variable plot of\nMycorrhiza inside and outside of invasion")+
+  labs(x="Location", y="Residuals of Mycorrhiza")+
+  theme_bw()+
[…]

### 2018-03-21 AlgebraProblem/CorrAndCovFunction.Rmd

---
title: "Functions relating to the Colonization model"
output: 
  html_notebook: 
    highlight: tango
    theme: cerulean
    toc: yes
---
#Load packages

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
```
# Model

According to the data simulation function:

A = p1 p2 a
B = p1 (1-p2 a)
C = (1-p1) p2
D = (1-p1) (1-p2)

Alpha reduces the colonization of pathogen ONLY when mycorrhiza is present. The interaction also ONLY has an effect on the pathogen colonization, not the mycorrhizal colonization.

The nice thing about this model is that it inhibits the pathogen at every point that there is a mycorrhiza.

The problem with this model is that the proportion of area colonized with mycorrhiza does not have an effect on how the pathogens will colonize the non-mycorrhizal points. If the effect is systemic, this will be something we see.

# Data Simulation

```{r Data simulation}
GMsim<-function(NXsec=100,NPlants=1000,Pm=0.5,Pp=0.2,Pc=0.5){
  c<-0
  Root<-data.frame(ind=rep(NA,NPlants*NXsec),c1=rep(NA,NPlants*NXsec),c2=rep(NA,NPlants*NXsec)) # Data for saving output
  for(i in 1:NPlants){
    tempMyc<-sample(1:0,NXsec,replace=T,prob=c(Pm,1-Pm)) # Generate Myc colonization
    tempPath<-rep(NA,NXsec) # Empty vector of pathogen infection

    # Simulate root cross-sections. 
    if(length(tempMyc[tempMyc==0])>0){
      tempPath[tempMyc==0]<-sample(1:0,length(tempPath[tempMyc==0]),replace=T,prob=c(Pp,1-Pp))  
    }
    if(length(tempPath[tempMyc==1])>0){
      tempPath[tempMyc==1]<-sample(1:0,length(tempPath[tempMyc==1]),replace=T,prob=c(Pp*Pc,1-Pp*Pc))
    }

    # Add the simulated co-occurence to the simulated data
    Root[(c+1):(c+NXsec),1]<-rep(i,NXsec)
    Root[(c+1):(c+NXsec),2]<-tempMyc
    Root[(c+1):(c+NXsec),3]<-tempPath

    #counter
    c<-c+NXsec

    # Clear temporary vectors to avoid errors in future iterations
    tempMyc<-tempPath<-NA
  }
  return(Root) ## Don't forget to return this to the user!
}

Toy<-GMsim()
```

# Function for Var/covar and correlation

data -- the dataset with rows representing each cross-section and the following columns:

ind -- the column with the labels for individuals; there should be > 1 location per individual

c1 -- the column of presence/absence (1:0) for Mycorrhiza

c2 -- the column of presence/absence (1:0) for Pathogen

```{r Var/covar and  corr coeff Function }
Bcor<-function(x=NA,ind=ind,c1=c1,c2=c2){
  # Check if user wants covariance matrix or correlation coefficient

  # Calculate the frequency of each possible outcome
A<- length((dplyr::filter(x, c1 == 1 & c2 == 1))$ind)
B<- length((dplyr::filter(x, c1 == 1 & c2 == 0))$ind)
C<- length((dplyr::filter(x, c1 == 0 & c2 == 1))$ind)
D<- length((dplyr::filter(x, c1 == 0 & c2 == 0))$ind)

  # Calculate variances, covariance and correlation
infoDF <- data.frame(VARIANCE1=NA,VARIANCE2=NA,COVARIANCE=NA,CORRELATION=NA)
infoDF$VARIANCE1[1] <- (A+B)*(1-(A+B))
infoDF$VARIANCE2[1] <- (A+C)*(1-(A+C))
infoDF$COVARIANCE[1]<- A-(A+B)*(A+C)
infoDF$CORRELATION[1] <- infoDF$COVARIANCE[1]/(sqrt(infoDF$VARIANCE1[1]*infoDF$VARIANCE2[1]))

    return(print(infoDF))
}
```

## Test

```{r}
Toy<-GMsim(Pm=0.6,Pp=0.2,Pc=0.3)
Bcor(x = Toy)

```

# Function for p1, p2 and a

```{r p1 p2 a Function }

Icor <- function(x=NA,ind=ind,c1=c1,c2=c2){
  # Conditional probabilities
  ## A through B can be estimated from the data
  ## Use these equations to try to solve for p1, p2 & a
  ## For example, B-C or C-B will isolate p1 and p2 only
A<- length((dplyr::filter(x, c1 == 1 & c2 == 1))$ind)
B<- length((dplyr::filter(x, c1 == 1 & c2 == 0))$ind)
C<- length((dplyr::filter(x, c1 == 0 & c2 == 1))$ind)
D<- length((dplyr::filter(x, c1 == 0 & c2 == 0))$ind)

  # Calculate p1,p2 and a
  # note that there are two versions of p1 and p2 because of the quadratic equation
  # choose the one that has a positive value.

infoDF <- data.frame(MycP=NA,PathP=NA, alpha=NA)

  infoDF$MycP[1]<- 1-((C+D)/sum(A,B,C,D))
  infoDF$PathP[1]<- (C/sum(A,B,C,D))/(1-p1)
  infoDF$alpha[1]<- (A/sum(A,B,C,D))/(p1*p2)

  return(print(infoDF))
}

```

## Test

```{r}
Toy<-GMsim(Pm=0.6,Pp=0.2,Pc=0.3)
Icor(x = Toy)
```

#Our data
##Load data
```{r Introduce co-occurence dataset, message=FALSE, warning=FALSE, echo=FALSE}
mdata <- read.csv("./Assessing_Oct_20.csv",stringsAsFactors=F)
indiv <- mdata$CODE[!mdata$CODE==""]
tdata <- mdata[grep("[0-9]+",mdata$Cross),]
nrow(tdata)/length(indiv)

# This is not the same because some individuals just had the totals not the cooccurence data
## THE COMMENT IS NOT CLEAR, EXPLAIN...
indiv2 <- tdata$CODE[!tdata$CODE==""]
nrow(tdata)/length(indiv2)
indiv2 <- data.frame(indiv2)
indiv2 <- mefa:::rep.data.frame(indiv2,each=100)
fdata <- cbind(indiv2,tdata)
fdata <- fdata[,-c(2,3,4,9,14,17,18)]

# Cleaning up the occurence data
## CLEANING UP HOW?
fdata[is.na(fdata)] <- 0
fdata$Lesion<-rowSums(fdata[,2:4])
fdata[fdata$Lesion>1,]
fdata$Mycorrhiza<-rowSums(fdata[,6:8])
fdata[fdata$Mycorrhiza>1,]
fdata <- fdata[,-c(2:4,6:8)]

#### Checking data for problems ####

summary(fdata)
fdata$None.Path <- as.integer(fdata$None.Path)
fdata$None.Myc <- as.integer(fdata$None.Myc)
fdata[is.na(fdata)] <- 0

sherb <- fdata$Herbivory+fdata$None.Herb
fdata[sherb!=1,]
fdata[sherb!=1,"None.Herb"]<-1

# Are all the sums equal to 100 for herb? 
dframeHerb <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeHerb[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeHerb$counter[c] <- c
  dframeHerb$Indiv2[c] <- i
  dframeHerb$Sum[c] <- sum(subdata[,"Herbivory"]+subdata[,"None.Herb"])
  subdata <- NA
  c <- c + 1
}
dframeHerb[dframeHerb$Sum!=100,]

# Are all the sums equal to 100 for Mycorrhiza? 
dframeMyc <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeMyc[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeMyc$counter[c] <- c
  dframeMyc$Indiv2[c] <- i
  dframeMyc$Sum[c] <- sum(subdata[,"Mycorrhiza"]+subdata[,"None.Myc"])
  subdata <- NA
  c <- c + 1
}
dframeMyc[dframeMyc$Sum!=100,]

# Are all the sums equal to 100 for Lesions? 
dframeLesion <- data.frame(counter=NA, Indiv2=NA,Sum=NA)
c <- 1
for (i in unique(fdata$indiv2)){
  dframeLesion[c,] <- NA
  subdata <- fdata[fdata$indiv2==i,]
  dframeLesion$counter[c] <- c
  dframeLesion$Indiv2[c] <- i
  dframeLesion$Sum[c] <- sum(subdata[,"Lesion"]+subdata[,"None.Path"])
  subdata <- NA
  c <- c + 1
}
dframeLesion[dframeLesion$Sum!=100,]

# Separating "Individual" into: pop,location,species columns 
fdata$pop <- gsub("^([0-9]+)[I,O][A-Z]+.*","\\1",fdata$indiv)
fdata$location <- gsub("^[0-9]+([I,O])[A-Z]+.*","\\1",fdata$indiv)
fdata$species <- sub("^[0-9]+[I,O]([A-Z]+).*","\\1",fdata$indiv)
fdata$location <- as.factor(fdata$location)
fdata$species <- as.factor(fdata$species)
fdata$pop <- as.factor(fdata$pop)
fdata$indiv2 <- as.character(fdata$indiv2)
summary(fdata)
fdata %>% drop_na()->fdata

fdata$None.Myc <- as.factor(fdata$None.Myc)
fdata$Herbivory <- as.factor(fdata$Herbivory)
fdata$Mycorrhiza <- as.factor(fdata$Mycorrhiza)
fdata$Lesion <- as.factor(fdata$Lesion)
fdata$None.Herb <- as.factor(fdata$None.Herb)
fdata$None.Path <- as.factor(fdata$None.Path)
summary(fdata)
```

```{r Species specific}
levels(fdata$species)
dataAH <-filter(fdata,species== "AH")[,c(1,6,7,8,9)]
colnames(dataAH)<-c("ind","c1","c2","pop","location")
Bcor(dataAH)
Icor(dataAH)

dataCL <-filter(fdata,species== "CL")[,c(1,6,7,8,9)]
colnames(dataCL)<-c("ind","c1","c2","pop","location")
Bcor(dataCL)
Icor(dataCL)

dataGA <-filter(fdata,species== "GA")[,c(1,6,7,8,9)]
colnames(dataGA)<-c("ind","c1","c2","pop","location")
Bcor(dataGA)
Icor(dataGA)

dataGR <-filter(fdata,species== "GR")[,c(1,6,7,8,9)]
colnames(dataGR)<-c("ind","c1","c2","pop","location")
Bcor(dataGR)
Icor(dataGR)

dataMR <-filter(fdata,species== "MR")[,c(1,6,7,8,9)]
colnames(dataMR)<-c("ind","c1","c2","pop","location")
Bcor(dataMR)
Icor(dataMR)

dataSC <-filter(fdata,species== "SC")[,c(1,6,7,8,9)]
colnames(dataSC)<-c("ind","c1","c2","pop","location")
Bcor(dataSC)
Icor(dataSC)
```

```{r Location specific}
dataInside <-filter(fdata,location== "I")[,c(1,6,7,8,10)]
colnames(dataInside)<-c("ind","c1","c2","pop","species")
Bcor(dataInside)
Icor(dataInside)

dataOutside <-filter(fdata,location== "O")[,c(1,6,7,8,10)]
colnames(dataOutside)<-c("ind","c1","c2","pop","species")
Bcor(dataOutside)
Icor(dataOutside)
```

```{r Species and location specific}

dataAHIn <-filter(fdata,species== "AH" & location== "I")[,c(1,6,7,8)]
colnames(dataAHIn)<-c("ind","c1","c2","pop")
Bcor(dataAHIn)
Icor(dataAHIn)

dataAHOut <-filter(fdata,species== "AH" & location== "O")[,c(1,6,7,8)]
colnames(dataAHOut)<-c("ind","c1","c2","pop")
Bcor(dataAHOut)
Icor(dataAHOut)

dataCLIn <-filter(fdata,species== "CL" & location== "I")[,c(1,6,7,8)]
colnames(dataCLIn)<-c("ind","c1","c2","pop")
Bcor(dataCLIn)
Icor(dataCLIn)

dataCLOut <-filter(fdata,species== "CL" & location== "O")[,c(1,6,7,8)]
colnames(dataCLOut)<-c("ind","c1","c2","pop")
Bcor(dataCLOut)
Icor(dataCLOut)

dataGAIn <-filter(fdata,species== "GA"& location== "I")[,c(1,6,7,8)]
colnames(dataGAIn)<-c("ind","c1","c2","pop")
Bcor(dataGAIn)
Icor(dataGAIn)

dataGAOut <-filter(fdata,species== "GA"& location== "O")[,c(1,6,7,8)]
colnames(dataGAOut)<-c("ind","c1","c2","pop")
Bcor(dataGAOut)
Icor(dataGAOut)

dataGRIn <-filter(fdata,species== "GR" & location== "I")[,c(1,6,7,8)]
colnames(dataGRIn)<-c("ind","c1","c2","pop")
Bcor(dataGRIn)
Icor(dataGRIn)

dataGROut <-filter(fdata,species== "GR" & location== "O")[,c(1,6,7,8)]
colnames(dataGROu)<-c("ind","c1","c2","pop")
Bcor(dataGROu)
Icor(dataGROu)

dataMRIn <-filter(fdata,species== "MR" & location== "I")[,c(1,6,7,8)]
colnames(dataMRIn)<-c("ind","c1","c2","pop")
Bcor(dataMRIn)
Icor(dataMRIn)

dataMROut <-filter(fdata,species== "MR" & location== "O")[,c(1,6,7,8)]
colnames(dataMROut)<-c("ind","c1","c2","pop")
Bcor(dataMROut)
Icor(dataMROut)

dataSC <-filter(fdata,species== "SC")[,c(1,6,7,8)]
colnames(dataSC)<-c("ind","c1","c2","pop")
Bcor(dataSC)
Icor(dataSC)
```

### 2018-03-21 AlgebraProblem/CorrAndCovFunction.Rmd
Saved

@@
 dataGROut <-filter(fdata,species== "GR" & location== "O")[,c(1,6,7,8)]
-colnames(dataGROu)<-c("ind","c1","c2","pop")
-Bcor(dataGROu)
-Icor(dataGROu)
+colnames(dataGROut)<-c("ind","c1","c2","pop")
+Bcor(dataGROut)
+Icor(dataGROut)
 
@@
 
-dataSC <-filter(fdata,species== "SC")[,c(1,6,7,8)]
-colnames(dataSC)<-c("ind","c1","c2","pop")
-Bcor(dataSC)
-Icor(dataSC)
+dataSCIn <-filter(fdata,species== "SC" & location== "I")[,c(1,6,7,8)]
+colnames(dataSCIn)<-c("ind","c1","c2","pop")
+Bcor(dataSCIn)
+Icor(dataSCIn)
+
+dataSCOut <-filter(fdata,species== "SC" & location== "O")[,c(1,6,7,8)]
+colnames(dataSCOut)<-c("ind","c1","c2","pop")
+Bcor(dataSCOut)
+Icor(dataSCOut)
+
 ```
